---
title: "Tutira + Cyclone Gabrielle 2026"
format: html
editor: visual
---

# Libraries

```{r, message = FALSE}
library(sf)
library(ggplot2)
library(osmdata)
library(rnaturalearth)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(scales)
library(ggpubr)
library(rLakeAnalyzer) 
library(LakeMetabolizer)
library(purrr)
library(stringr)
library(cowplot)
library(zoo)
library(slider)
library(ggridges)
library(mgcv)
library(stats)
library(RColorBrewer)
library(rlang)
library(patchwork)
library(png)
library(grid)
library(gridExtra)
library(ggforce)
library(ggtext)
```

# Data

```{r}
#Download Profiling Data from zenodo
url <- "https://zenodo.org/records/19582360/files/Tutira_201807-202601_profiles.csv?download=1"

download.file(url, destfile = "Tutira_Pro.csv", mode = "wb")

Tutira_Pro <- read.csv("Tutira_Pro.csv")

#Add in 00:00 time when necessary
Tutira_Pro1<- Tutira_Pro
Tutira_Pro1$DateTime <- ifelse(
  grepl("^\\d{4}-\\d{2}-\\d{2}$", Tutira_Pro1$DateTime),  # if only date, no time
  paste0(Tutira_Pro1$DateTime, " 00:00:00"),              # add time
  Tutira_Pro1$DateTime                                     # leave as-is
)
#format dates
Tutira_Pro1$Date <- format(as.Date(Tutira_Pro1$DateTime, '%Y-%m-%d', tz= "UTC"), format = '%Y-%m-%d')
Tutira_Pro1$Date <- as.Date(Tutira_Pro1$Date)
Tutira_Pro1$Time <- format(as.POSIXct(Tutira_Pro1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:%M')
Tutira_Pro1$Hour <- format(as.POSIXct(Tutira_Pro1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:00')
Tutira_Pro1$DateTime <- as.POSIXct(Tutira_Pro1$DateTime, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
Tutira_Pro1$Month <- months(Tutira_Pro1$Date)
Tutira_Pro1$Year <- format(as.POSIXct(Tutira_Pro1$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_Pro1$Datetime <- as.POSIXct(paste(Tutira_Pro1$Date, Tutira_Pro1$Hour),format='%Y-%m-%d %H:%M', tz='UTC')
Tutira_Pro1$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_Pro1$Date), "%m-%d")))
Tutira_Pro1$MDT <- as.POSIXct(paste0("2000-", format(as.POSIXct(Tutira_Pro1$DateTime), "%m-%d %H:%M")),format = "%Y-%m-%d %H:%M",tz = "UTC")

#make sure data ends in 2025
Tutira_Pro1 <- Tutira_Pro1 %>%
  filter(Year != 2026)

#Download Profiling Data from zenodo
url <- "https://zenodo.org/records/19582360/files/Tutira_201807-202601_meteorology.csv?download=1"

download.file(url, destfile = "Tutira_Met.csv", mode = "wb")

Tutira_Met <- read.csv("Tutira_Met.csv")

#Add in 00:00 time when necessary
Tutira_Met1<- Tutira_Met
Tutira_Met1$DateTime <- ifelse(
  grepl("^\\d{4}-\\d{2}-\\d{2}$", Tutira_Met1$DateTime),  # if only date, no time
  paste0(Tutira_Met1$DateTime, " 00:00:00"),              # add time
  Tutira_Met1$DateTime                                     # leave as-is
)
#format dates
Tutira_Met1$Date <- format(as.Date(Tutira_Met1$DateTime, '%Y-%m-%d', tz= "UTC"), format = '%Y-%m-%d')
Tutira_Met1$Date <- as.Date(Tutira_Met1$Date)
Tutira_Met1$Time <- format(as.POSIXct(Tutira_Met1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:%M')
Tutira_Met1$Hour <- format(as.POSIXct(Tutira_Met1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:00')
Tutira_Met1$DateTime <- as.POSIXct(Tutira_Met1$DateTime, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
Tutira_Met1$Month <- months(Tutira_Met1$Date)
Tutira_Met1$Year <- format(as.POSIXct(Tutira_Met1$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_Met1$datetime <- as.POSIXct(paste(Tutira_Met1$Date, Tutira_Met1$Hour),format='%Y-%m-%d %H:%M',tz = 'UTC')
Tutira_Met1$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_Met1$Date), "%m-%d")))
Tutira_Met1$MDT <- as.POSIXct(paste0("2000-", format(as.POSIXct(Tutira_Met1$DateTime), "%m-%d %H:%M")),format = "%Y-%m-%d %H:%M",tz = "UTC")

#convert wind speed from knots to m/s
Tutira_Met2 <- Tutira_Met1%>%
  mutate(WndSpd = WndSpd/1.944) %>%#converts from knots to m/s
  filter(Year != 2026)
```

## Profiles

```{r}
#averaging depths at meter intervals
Tutira_Pro2 <- Tutira_Pro1%>%
  mutate(Depth = case_when(
    DptSns <= 0.5 ~ 0,
    DptSns > 0.5 & DptSns <=1.5 ~ 1,
    DptSns > 1.5 & DptSns <=2.5 ~ 2,
    DptSns > 2.5 & DptSns <=3.5 ~ 3,
    DptSns > 3.5 & DptSns <=4.5 ~ 4,
    DptSns > 4.5 & DptSns <=5.5 ~ 5,
    DptSns > 5.5 & DptSns <=6.5 ~ 6,
    DptSns > 6.5 & DptSns <=7.5 ~ 7,
    DptSns > 7.5 & DptSns <=8.5 ~ 8,
    DptSns > 8.5 & DptSns <=9.5 ~ 9,
    DptSns > 9.5 & DptSns <=10.5 ~ 10,
    DptSns > 10.5 & DptSns <=11.5 ~ 11,
    DptSns > 11.5 & DptSns <=12.5 ~ 12,
    DptSns > 12.5 & DptSns <=13.5 ~ 13,
    DptSns > 13.5 & DptSns <=14.5 ~ 14,
    DptSns > 14.5 & DptSns <=15.5 ~ 15,
    DptSns > 15.5 & DptSns <=16.5 ~ 16,
    DptSns > 16.5 & DptSns <=17.5 ~ 17,
    DptSns > 17.5 & DptSns <=18.5 ~ 18,
    DptSns > 18.5 & DptSns <=19.5 ~ 19,
    DptSns > 19.5 & DptSns <=20.5 ~ 20,
    DptSns > 20.5 & DptSns <=21.5 ~ 21,
    DptSns > 21.5 & DptSns <=22.5 ~ 22,
    DptSns > 22.5 & DptSns <=23.5 ~ 23,
    DptSns > 23.5 & DptSns <=24.5 ~ 24,
    DptSns > 24.5 & DptSns <=25.5 ~ 25,
    DptSns > 25.5 & DptSns <=26.5 ~ 26,
    DptSns > 26.5 & DptSns <=27.5 ~ 27,
    DptSns > 27.5 & DptSns <=28.5 ~ 28,
    DptSns > 28.5 & DptSns <=29.5 ~ 29,
    DptSns > 29.5 & DptSns <=30.5 ~ 30,
    DptSns > 30.5 & DptSns <=31.5 ~ 31,
    DptSns > 31.5 & DptSns <=32.5 ~ 32,
    DptSns > 32.5 & DptSns <=33.5 ~ 33,
    DptSns > 33.5 & DptSns <=34.5 ~ 34,
    DptSns > 34.5 & DptSns <=35.5 ~ 35,
    DptSns > 35.5 & DptSns <=36.5 ~ 36,
    DptSns > 36.5 & DptSns <=37.5 ~ 37,
    DptSns > 37.5 & DptSns <=38.5 ~ 38,
    DptSns > 38.5 & DptSns <=39.5 ~ 39,
    DptSns > 39.5 & DptSns <=40.5 ~ 40
  ))%>%
  group_by(DateTime,Date,Hour,MD,Month,Year,Depth, DptSns)%>%
  #group_by(Datetime, Date, Hour, MD, MDT, Month, Year, Depth)%>%
  dplyr::summarise_at(vars('TmpWtr':'TmpDif'),mean,na.rm=TRUE)%>%
  ungroup()

#creating profiles for new depths
ok_profiles <- Tutira_Pro2 %>% 
  #filter(!is.na(DateTime))%>%
  arrange(DateTime)%>%
  dplyr::select(DateTime, DptSns, Depth, TmpWtr)

#creates a profile id
ok_profiles <- ok_profiles%>%
    mutate(
    new_profile_flag = Depth < lag(Depth, default = first(Depth)),  # TRUE at cast start
    profile_id       = cumsum(new_profile_flag) + 1                
  )

#selects first datetime for each profile
profile_times <- ok_profiles %>% 
  arrange(profile_id, DateTime) %>%          # make sure rows are in order
  group_by(profile_id) %>%                   
  dplyr::summarise(DateTime = first(DateTime),      # or DateTime = min(DateTime)
            .groups = "drop")                
```

## Interpolation - 60 days

```{r}
#combines profile id to original dataset and updates the Datetime, then fills out data so there are no gaps between dates or depths
Tutira_interp <- Tutira_Pro2 %>%
  left_join(ok_profiles, by = c('DateTime', 'Depth', 'TmpWtr', 'DptSns')) %>%
  dplyr::select(profile_id, Depth, TmpWtr:FlPhyc) %>%
  group_by(profile_id, Depth)%>%
  dplyr::summarise_at(vars('TmpWtr':'FlPhyc'),mean,na.rm=TRUE)%>%
  ungroup()%>%
  complete(profile_id, Depth = 1:38) %>%
  arrange(profile_id, Depth)%>%
  left_join(profile_times, by = 'profile_id')%>%
  mutate(DateTime = lubridate::round_date(DateTime, unit = "hour")) %>%
  distinct(DateTime, Depth, .keep_all = TRUE) %>%
  group_by(Depth) %>%
  complete(DateTime = seq(min(DateTime), max(DateTime), by = "1 hour")) %>%
  arrange(Depth, DateTime)%>%
  ungroup() %>%
  # Preserve original profile_id
  mutate(profile_orig = profile_id) %>%
  # Fill downward
  group_by(Depth) %>%
  tidyr::fill(profile_orig, .direction = "down") %>%
  # Add 0.5 only to rows that were originally NA
  mutate(profile_id = ifelse(is.na(profile_id), profile_orig + 0.5, profile_orig)) %>%
  ungroup() %>%
  dplyr::select(-profile_orig)

#finding out missing number of observations
Tutira_interp_daily <- Tutira_interp %>%
  mutate(Date = format(as.Date(DateTime, '%Y-%m-%d', tz= "UTC"), format = '%Y-%m-%d'),
  Date = as.Date(Date)) %>%
  group_by(Date, Depth) %>%
  dplyr::summarise_at(vars('TmpWtr':'FlPhyc'),mean,na.rm=TRUE)%>%
  ungroup()
  
total_values_all  <- prod(dim(Tutira_interp_daily))
missing_values_all <- sum(is.na(Tutira_interp_daily))

percent_missing_all <- (missing_values_all / total_values_all) * 100
percent_missing_all

#for each individual variable
Tutira_missing_var <- Tutira_interp_daily %>%
  dplyr::select(TmpWtr:FlPhyc) %>%
  summarise(across(everything(),
                   list(
                     Missing_n = ~ sum(is.na(.)),
                     Percent_Missing = ~ mean(is.na(.)) * 100
                   )))

# Define the variables to interpolate
vars_to_interp <- c("TmpWtr","DOconc","DOpsat","pH","Cond","SpCond","TurbRT","FlChlr","FlPhyc")

#Hourly interpolation for 60 days
#safe_hour_interp <- function(x, datetime, max_gap_hours = 168) { #7 days
#safe_hour_interp <- function(x, datetime, max_gap_hours = 336) { #14 days
#safe_hour_interp <- function(x, datetime, max_gap_hours = 744) { #31 days
safe_hour_interp <- function(x, datetime, max_gap_hours = 1440) { #60 days
  if (sum(!is.na(x)) < 2) return(x)
  
  # Interpolate
  interp <- zoo::na.approx(x, x = as.numeric(datetime), na.rm = FALSE, rule = 2)
  
  # Mask sequences exceeding max_gap
  na_idx <- which(is.na(x))
  if (length(na_idx) > 0) {
    r <- rle(is.na(x))
    idx <- 1
    mask <- rep(FALSE, length(x))
    for (i in seq_along(r$lengths)) {
      if (r$values[i] & r$lengths[i] > max_gap_hours) {
        mask[idx:(idx + r$lengths[i]-1)] <- TRUE
      }
      idx <- idx + r$lengths[i]
    }
    interp[mask] <- NA
  }
  return(interp)
}

Tutira_hourly <- Tutira_interp %>%
  group_by(Depth) %>%
  arrange(DateTime) %>%
  # Ensure full hourly sequence per depth
  complete(DateTime = seq(min(DateTime), max(DateTime), by = "1 hour")) %>%
  mutate(across(all_of(vars_to_interp), 
                ~ safe_hour_interp(.x, DateTime),
                .names = "{.col}_hourInterp")) %>%
  ungroup()

# Depth-wise interpolation 
safe_depth_interp <- function(x, depth) {
  if (sum(!is.na(x)) < 2) return(x)  # must have at least 2 values
  # Interpolate across all depths, allow extrapolation
  zoo::na.approx(x, x = depth, na.rm = FALSE, rule = 2)
}

Tutira_interp_depth <- Tutira_hourly %>%
  group_by(profile_id) %>%
  arrange(Depth) %>%
  mutate(across(ends_with("_hourInterp"), 
                ~ safe_depth_interp(.x, Depth),
                .names = "{.col}_depthInterp")) %>%
  ungroup()

Tutira_interp2 <- Tutira_interp_depth%>%
  dplyr::select(DateTime, profile_id, Depth, ends_with("_hourInterp_depthInterp")) %>%
  rename_with(
    ~ gsub("_hourInterp_depthInterp$", "", .x),
    ends_with("_hourInterp_depthInterp")
  )

Tutira_interp2$Date <- format(as.Date(Tutira_interp2$DateTime, '%Y-%m-%d', tz= "UTC"), format = '%Y-%m-%d')
Tutira_interp2$Date <- as.Date(Tutira_interp2$Date)
Tutira_interp2$Time <- format(as.POSIXct(Tutira_interp2$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:%M')
Tutira_interp2$Hour <- format(as.POSIXct(Tutira_interp2$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:00')
Tutira_interp2$DateTime <- as.POSIXct(Tutira_interp2$DateTime, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
Tutira_interp2$Month <- months(Tutira_interp2$Date)
Tutira_interp2$Year <- format(as.POSIXct(Tutira_interp2$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_interp2$datetime <- as.POSIXct(paste(Tutira_interp2$Date, Tutira_interp2$Hour),format='%Y-%m-%d %H:%M', tz = 'UTC')
Tutira_interp2$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_interp2$Date), "%m-%d")))
Tutira_interp2$MDT <- as.POSIXct(paste0("2000-", format(as.POSIXct(Tutira_interp2$datetime), "%m-%d %H:%M")),format = "%Y-%m-%d %H:%M",tz = "UTC")

#removing weird chlorophyll values
Tutira_interp2 <- Tutira_interp2 %>%
  mutate(FlChlr = case_when(
    ((datetime >= as.POSIXct("2020-02-07 15:00:00") &
    datetime <= as.POSIXct("2020-02-13 13:00:00")) |
    (datetime >= as.POSIXct("2020-02-13 15:00:00") &
    datetime <= as.POSIXct("2020-02-27 08:00:00"))) &
    Depth == 1 ~ NA_real_,
    TRUE ~ FlChlr
  ))

#adding in max algal peak depth
Tutira_AlgalPeak <- Tutira_interp2 %>% 
  group_by(datetime) %>% 
  mutate( 
    Depth_max_FlChlr = if (all(is.na(FlChlr))) NA_real_ else Depth[which.max(FlChlr)], 
    Depth_max_FlPhyc = if (all(is.na(FlPhyc))) NA_real_ else Depth[which.max(FlPhyc)] ) %>% 
  ungroup()

#adding in hypoxic depth
Tutira_Anoxic <- Tutira_interp2 %>%
  group_by(datetime) %>%
  mutate(
    Anoxic_Depth = case_when(
      all(is.na(DOconc)) ~ NA_real_,                             # no DO values
      any(!is.na(DOconc) & DOconc <= 2) ~ min(Depth[DOconc <= 2], na.rm = TRUE),  # first anoxic depth
      TRUE ~ 38                                                   # DO exists but none ≤ 2
    )
  ) %>%
  ungroup()

#temperature profiles
Tutira_ProfileWide <- Tutira_interp2 %>% 
  dplyr::select(datetime, Depth, TmpWtr)%>%
  pivot_wider(
    names_from   = Depth,
    names_prefix = "wtr_",      # adds “wtr_”
    names_sort   = TRUE,        # numeric sort (because Depth is numeric)
    values_from  = TmpWtr
  )%>%
  drop_na()
```

## rlakeanalyzer

```{r}
#changing format of temperature file
ok_wide_iso <- Tutira_ProfileWide %>%
  mutate(datetime = format(datetime, "%Y-%m-%dT%H:%M:%SZ"))

#Convert to character matrix for full control
char_mat <- apply(ok_wide_iso, 2, as.character)

#Build tab-separated lines manually
header <- paste(colnames(ok_wide_iso), collapse = "\t")
rows <- apply(char_mat, 1, function(x) paste(x, collapse = "\t"))
txt_lines <- c(header, rows)

#Feed to load.ts() via in-memory text connection
con <- textConnection(txt_lines, "r")
Tutira.wtr <- load.ts(con)
close(con)

Tutira.wtr$datetime <- as.POSIXct(
  format(Tutira_ProfileWide$datetime, "%Y-%m-%dT%H:%M:%SZ"),
  format = "%Y-%m-%dT%H:%M:%SZ",
  tz = "UTC"
)

str(Tutira.wtr)
#Find other parameters in rLakeAnalyzer
t.d_Tutira = ts.thermo.depth(Tutira.wtr) # pulls out calculated thermocline depth

#replaces NA values with bottom depth of lake
t.d_Tutira_replace <- t.d_Tutira%>%
  mutate(across(
    where(is.numeric),               
    ~ replace(.x, is.nan(.x), 38)    
  ))

#upload bathy data
#Download Profiling Data from zenodo
url <- "https://zenodo.org/records/19582360/files/Tutira_bathy.txt?download=1"

download.file(url, destfile = "Tutira_bathy.txt", mode = "wb")

Tutira_bathy <- "Tutira_bathy.txt"

#change to correct format for rlakeanalyzer
Tutira.bth = load.bathy(Tutira_bathy)
#calculate schmidt stability
S.S_Tutira = ts.schmidt.stability(Tutira.wtr,Tutira.bth, na.rm = FALSE)

#formating wind data
Tutira_Wnd <- Tutira_Met2%>%
  dplyr::select(c(datetime, WndSpd))%>%
  group_by(datetime)%>%
  dplyr::summarise_at(vars('WndSpd'),mean,na.rm=TRUE)%>%
  ungroup()%>%
  rename(wnd_1.0 = WndSpd)%>%
  drop_na()

Tutira_wnd_1 <- Tutira_Wnd %>%
  mutate(datetime = format(datetime, "%Y-%m-%dT%H:%M:%SZ"))

#Convert to character matrix for full control
char_mat <- apply(Tutira_wnd_1, 2, as.character)

#Build tab-separated lines manually
header <- paste(colnames(Tutira_wnd_1), collapse = "\t")
rows <- apply(char_mat, 1, function(x) paste(x, collapse = "\t"))
txt_lines <- c(header, rows)

#Feed to load.ts() via in-memory text connection
con <- textConnection(txt_lines, "r")
Tutira.wnd <- load.ts(con)
close(con)

Tutira.wnd$datetime <- as.POSIXct(
  format(Tutira_Wnd$datetime, "%Y-%m-%dT%H:%M:%SZ"),
  format = "%Y-%m-%dT%H:%M:%SZ",
  tz = "UTC"
)
#calculate lake number
Tutira_LN <- ts.lake.number(Tutira.wtr,Tutira.wnd,2,Tutira.bth,seasonal=TRUE)

#Metalimion depths
Tutira_MD <- ts.meta.depths(Tutira.wtr, slope = 0.1)
Tutira_MD <- Tutira_MD%>%
  rename(Meta_Top = top)%>%
  rename(Meta_Bottom = bottom)

#Brunt-Vaisala frequency
Tutira_BF <- ts.buoyancy.freq(Tutira.wtr)
Tutira_BF <- Tutira_BF%>%
  rename(Buoyancy = n2)

force_timezone <- function(df, tz = "UTC") {
  # Convert to character to preserve displayed clock time
  df$datetime <- as.POSIXct(format(df$datetime, "%Y-%m-%d %H:%M:%S"), tz = tz)
  return(df)
}

datasets <- list(Tutira_AlgalPeak, Tutira_Anoxic, t.d_Tutira_replace, S.S_Tutira, Tutira_LN, Tutira_MD, Tutira_BF)
datasets <- lapply(datasets, force_timezone, tz = "UTC")

Tutira_AlgalPeak      <- datasets[[1]]
Tutira_Anoxic <- datasets[[2]]
t.d_Tutira_replace <- datasets[[3]]
S.S_Tutira         <- datasets[[4]]
Tutira_LN          <- datasets[[5]]
Tutira_MD          <- datasets[[6]]
Tutira_BF          <- datasets[[7]]

Tutira_data3 <- Tutira_AlgalPeak%>%
  #mutate(datetime = as.POSIXct(datetime, tz = "UTC"))%>%
  left_join(
    Tutira_Anoxic %>% dplyr::select(datetime, Depth, Anoxic_Depth),
    by = c("datetime", "Depth"), relationship = "many-to-many"
  )%>%
  left_join(t.d_Tutira_replace, by = 'datetime', relationship = "many-to-one")%>%
  left_join(S.S_Tutira, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_LN, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_MD, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_BF, by = 'datetime', relationship = "many-to-one")

#replacing na values with 0
Tutira_LN1 <- Tutira_LN%>%
  mutate(lake.number = coalesce(lake.number, 0))

Tutira_BF1 <- Tutira_BF%>%
  mutate(Buoyancy = coalesce(Buoyancy, 0))

Tutira_MD1 <- Tutira_MD%>%
  mutate(Meta_Top = coalesce(Meta_Top, 0), Meta_Bottom = coalesce(Meta_Bottom, 38))

datasets <- list(Tutira_AlgalPeak, Tutira_Anoxic, t.d_Tutira_replace, S.S_Tutira, Tutira_LN1, Tutira_MD1, Tutira_BF1)
datasets <- lapply(datasets, force_timezone, tz = "UTC")

Tutira_AlgalPeak      <- datasets[[1]]
Tutira_Anoxic <- datasets[[2]]
t.d_Tutira_replace <- datasets[[3]]
S.S_Tutira         <- datasets[[4]]
Tutira_LN1          <- datasets[[5]]
Tutira_MD1          <- datasets[[6]]
Tutira_BF1          <- datasets[[7]]

Tutira_data3_replace <- Tutira_AlgalPeak %>%
  left_join(
    Tutira_Anoxic %>% dplyr::select(datetime, Depth, Anoxic_Depth),
    by = c("datetime", "Depth"), relationship = "many-to-many"
  )%>%
  left_join(t.d_Tutira_replace, by = 'datetime', relationship = "many-to-one")%>%
  left_join(S.S_Tutira, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_LN1, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_MD1, by = 'datetime', relationship = "many-to-one")%>%
  left_join(Tutira_BF1, by = 'datetime', relationship = "many-to-one")
```

## Storm identification

```{r}
#determining dates of cyclone Gabrielle
Tutira_storm <- Tutira_Met2 %>%
  arrange(DateTime) %>%
  mutate(
    # thresholds
    PrBaro_10th = quantile(PrBaro, 0.10, na.rm = TRUE),
    WS_85th    = quantile(WndSpd, 0.85, na.rm = TRUE),
    Rain_P  = PpRain > 0,
    # event flags
    PrBaro_event = PrBaro <= PrBaro_10th,
    WS_event     = WndSpd >= WS_85th,
    Rain_event   = Rain_P == TRUE,
    All_event    = PrBaro_event & WS_event & Rain_event,   # ALL must be true
    All_event_end    = PrBaro_event & WS_event
    #All_event    = PrBaro_event & Rain_event   # ALL must be true
  )%>%
  filter(Year == 2023, Month == "February") %>%
  mutate(
    first_during_time = min(DateTime[All_event], na.rm = TRUE),
        last_during_time = {
      r <- rle(All_event_end)
      # Find indices where a run of TRUE is at least length 4 (20 minutes)
      idx <- which(r$values & r$lengths >= 4)
      if (length(idx) == 0) {
        NA  # no qualifying run
      } else {
        # cumulative lengths to find the ending position of the run
        cum_lengths <- cumsum(r$lengths)
        # end index of last qualifying run
        end_idx <- cum_lengths[idx[length(idx)]]
        DateTime[end_idx]
      }
    }
  )

#combines Storm timing with Profile
Tutira_Cyclone_Pro <- Tutira_data3_replace %>%
  mutate(
    first_during_time = Tutira_storm$first_during_time[1],
    last_during_time  = Tutira_storm$last_during_time[1]
  )%>%
  distinct(datetime, Depth, .keep_all = TRUE) #data has multiple rows with same information (idk why)
```

## Mean +- 95% Confidence Interval - non normal

### Structural

```{r}
# -----------------------------
# 1. Create daily dataset
# -----------------------------
Tutira_Cyclone_Pro_Day <- Tutira_Cyclone_Pro%>%
  group_by(Date, Month, Year, MD, Depth, first_during_time, last_during_time)%>%
  dplyr::summarise(across(TmpWtr:FlPhyc, ~ mean(.x, na.rm = TRUE))) %>%
  ungroup()

# -----------------------------
# 2. Create full hourly time grid
# -----------------------------
full_hours <- seq(
  as.POSIXct("2018-01-01", tz = "UTC"),
  as.POSIXct("2025-12-31", tz = "UTC"),
  by = "1 day"
)

# -----------------------------
# 3. Fill dataset for all depths × hours
# -----------------------------
Tutira_filled_Depth <- expand_grid(
  Depth = unique(Tutira_Cyclone_Pro_Day$Depth),
  Date = full_hours
) %>%
  left_join(Tutira_Cyclone_Pro_Day, by = c("Depth", "Date")) %>%
  arrange(Depth, Date) %>%
  mutate(
    Date     = as.Date(Date),
    Month    = month(Date, label = TRUE),
    Year     = year(Date),
    DOY      = yday(Date),
    MD       = as.Date(paste0("2000-", month(Date), "-", day(Date)))
  )

# -----------------------------
# 4. Define target variables
# -----------------------------
set.seed(123)  # for reproducibility

# 1️⃣ Pivot longer to make variables in one column
# Long data 
Tutira_long <- Tutira_filled_Depth %>%
  pivot_longer(
    cols = c(TmpWtr, DOconc, DOpsat, pH, Cond, SpCond, TurbRT, FlChlr, FlPhyc),
    names_to = "Variable",
    values_to = "Value"
  )

# Bootstrap function 
bootstrap_ci <- function(x, nboot = 1000, conf = 0.95) {
  x <- na.omit(x)
  if (length(x) < 2) {
    # return consistent structure with NAs
    return(tibble(mean = mean(x), lower = NA_real_, upper = NA_real_))
  }
  boot_means <- replicate(nboot, mean(sample(x, replace = TRUE)))
  alpha <- (1 - conf) / 2
  ci <- quantile(boot_means, probs = c(alpha, 1 - alpha))
  tibble(mean = mean(x), lower = ci[1], upper = ci[2])
}

# Apply bootstrap summarizing by depth × variable
Tutira_boot_summary <- Tutira_long %>%
  group_by(DOY, Depth, Variable) %>%
  dplyr::summarise(
    n = sum(!is.na(Value)),
    ci = list(bootstrap_ci(Value, nboot = 1000)),
    .groups = "drop"
  ) %>%
  unnest_wider(ci) %>%  # expands mean/lower/upper into separate columns
  dplyr::select(DOY, Depth, Variable, n, mean, lower, upper)

Tutira_boot_long <- Tutira_boot_summary%>%
  dplyr::select(-n)%>%
  pivot_wider(
    names_from = Variable,
    values_from = c(mean, lower, upper),
    names_glue = "{Variable}_{.value}"
  )
  
# -----------------------------
# 5. Join with main data and compute residuals/percent differences
# -----------------------------
Tutira_full_Depth <- Tutira_filled_Depth %>%
  left_join(Tutira_boot_long, by = c("Depth", "DOY"))


#making first and last storm times be present throughout entire dataset
Tutira_full_Depth <- Tutira_full_Depth %>%
  mutate(
    first_during_time = coalesce(first_during_time, first(na.omit(first_during_time))),
    last_during_time  = coalesce(last_during_time,  first(na.omit(last_during_time)))
  )
```

### Functional

```{r}
# -----------------------------
# 1. Create daily dataset
# -----------------------------
Tutira_Cyclone_Pro_ND <- Tutira_Cyclone_Pro %>%
  group_by(Date, Month, Year, MD, first_during_time, last_during_time) %>%
  dplyr::summarise(across(Depth_max_FlChlr:Buoyancy, ~ mean(.x, na.rm = TRUE))) %>%
  ungroup()

# -----------------------------
# 2. Create full hourly time grid
# -----------------------------
full_hours <- seq(
  as.POSIXct("2018-01-01", tz = "UTC"),
  as.POSIXct("2025-12-31", tz = "UTC"),
  by = "1 day"
)

# -----------------------------
# 3. Fill dataset for all depths × hours
# -----------------------------
Tutira_filled_ND <- expand_grid(
  Date = full_hours
) %>%
  left_join(Tutira_Cyclone_Pro_ND, by = c("Date")) %>%
  arrange(Date) %>%
  mutate(
    Date     = as.Date(Date),
    Month    = month(Date, label = TRUE),
    Year     = year(Date),
    DOY      = yday(Date),
    MD       = as.Date(paste0("2000-", month(Date), "-", day(Date)))
  )

# -----------------------------
# 4. Define target variables
# -----------------------------
set.seed(123)  # for reproducibility

# 1️⃣ Pivot longer to make variables in one column
# Long data (yours)
Tutira_long_ND <- Tutira_filled_ND %>%
  pivot_longer(
    cols = c(Depth_max_FlChlr, Depth_max_FlPhyc, Anoxic_Depth, thermo.depth, schmidt.stability, lake.number, Meta_Top, Meta_Bottom, Buoyancy),
    names_to = "Variable",
    values_to = "Value"
  )

# Bootstrap function
bootstrap_ci <- function(x, nboot = 1000, conf = 0.95) {
  x <- na.omit(x)
  if (length(x) < 2) {
    # return consistent structure with NAs
    return(tibble(mean = mean(x), lower = NA_real_, upper = NA_real_))
  }
  boot_means <- replicate(nboot, mean(sample(x, replace = TRUE)))
  alpha <- (1 - conf) / 2
  ci <- quantile(boot_means, probs = c(alpha, 1 - alpha))
  tibble(mean = mean(x), lower = ci[1], upper = ci[2])
}

# Apply bootstrap summarizing by depth × variable
Tutira_boot_summary_ND <- Tutira_long_ND %>%
  group_by(DOY, Variable) %>%
  dplyr::summarise(
    n = sum(!is.na(Value)),
    ci = list(bootstrap_ci(Value, nboot = 1000)),
    .groups = "drop"
  ) %>%
  unnest_wider(ci) %>%  # expands mean/lower/upper into separate columns
  dplyr::select(DOY, Variable, n, mean, lower, upper)

Tutira_boot_long_ND <- Tutira_boot_summary_ND%>%
  dplyr::select(-n)%>%
  pivot_wider(
    names_from = Variable,
    values_from = c(mean, lower, upper),
    names_glue = "{Variable}_{.value}"
  )
  
# -----------------------------
# 5. Join with main data and compute residuals/percent differences
# -----------------------------
Tutira_full_ND <- Tutira_filled_ND %>%
  left_join(Tutira_boot_long_ND, by = "DOY")


#making first and last storm times be present throughout entire dataset
Tutira_full_ND <- Tutira_full_ND %>%
  mutate(
    first_during_time = coalesce(first_during_time, first(na.omit(first_during_time))),
    last_during_time  = coalesce(last_during_time,  first(na.omit(last_during_time)))
  )
```

## Recovery

### Structural

```{r}
# Rename
Tutira_MeanCI_Daily_Recovery_Depths <- Tutira_full_Depth

# Target variables
vars <- c("TmpWtr", "DOconc", "DOpsat", "pH",
          "Cond", "SpCond", "TurbRT", "FlChlr", "FlPhyc")

# Filter to post-storm period
start_time <- min(as.Date(Tutira_MeanCI_Daily_Recovery_Depths$last_during_time), na.rm = TRUE)

df_check <- Tutira_MeanCI_Daily_Recovery_Depths %>%
  filter(Date >= start_time)

# Get max thermo.depth value from the non-depth dataset
max_thermo <- max(Tutira_full_ND$thermo.depth, na.rm = TRUE)

# Create recovered columns based on 95% CI, with thermo rule applied
for (v in vars) {
  recovered <- df_check[[v]] >= df_check[[paste0(v, "_lower")]] &
               df_check[[v]] <= df_check[[paste0(v, "_upper")]]

  # Apply thermo.depth rule:
  # For all dates when the lake's thermocline is at its max, mark as not recovered
  if (!is.na(max_thermo)) {
    # Find the dates in the non-depth dataset when thermo.depth == max_thermo
    max_thermo_dates <- Tutira_full_ND %>%
      filter(thermo.depth == max_thermo) %>%
      pull(Date) %>%
      unique()

    recovered[df_check$Date %in% max_thermo_dates] <- FALSE
  }

  df_check[[paste0("recovered_", v)]] <- recovered
}

# Rolling 2-day check
daily_recovery <- df_check %>%
  group_by(Depth) %>%
  arrange(Date, .by_group = TRUE) %>%
  mutate(
    across(
      starts_with("recovered_"),
      ~ rollapply(.x, width = 2, FUN = all, fill = NA, align = "right"),
      .names = "{.col}_2days"
    )
  ) %>%
  ungroup()

# First recovery date per Depth × Variable
first_recovery <- daily_recovery %>%
  pivot_longer(
    cols = ends_with("_2days"),
    names_to = "variable",
    values_to = "recovered"
  ) %>%
  group_by(variable, Depth) %>%
  filter(recovered == TRUE) %>%
  dplyr::summarise(
    recovery_date = min(Date, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(variable = sub("_2days$", "", variable), variable = sub("^recovered_", "", variable))%>%
  pivot_wider(names_from = variable, values_from = recovery_date, names_prefix = "first_recovery_")

# Join back to main dataset
Tutira_MeanCI_Daily_Recovery_Depths <- Tutira_MeanCI_Daily_Recovery_Depths %>%
  left_join(first_recovery, by = "Depth")
```

### Functional

```{r}
# -----------------------------
# 1. Create DOY
# -----------------------------
Tutira_MeanCI_Daily_Recovery_ND <- Tutira_full_ND%>%
  mutate(DOY = yday(Date))
  
# -----------------------------
# 2. Define target variables
# -----------------------------
vars <- c("Depth_max_FlChlr", "Depth_max_FlPhyc", "Anoxic_Depth", "thermo.depth",
          "schmidt.stability", "lake.number", "Meta_Top", "Meta_Bottom", "Buoyancy")

# ----------------------------
# 3. Post-storm recovery check by Depth
# ----------------------------

start_time <- min(as.Date(Tutira_MeanCI_Daily_Recovery_ND$last_during_time), na.rm = TRUE)
start_time <- as.Date(start_time)

# Step 1: create recovered_* columns dynamically
df_check <- Tutira_MeanCI_Daily_Recovery_ND %>%
  filter(Date >= start_time)

# Find the max thermo.depth for comparison
max_thermo <- max(Tutira_full_ND$thermo.depth, na.rm = TRUE)

for (v in vars) {
  # Standard recovery condition
  recovered <- df_check[[v]] >= df_check[[paste0(v, "_lower")]] &
               df_check[[v]] <= df_check[[paste0(v, "_upper")]]

  # Special rule: if variable is thermo.depth and it's at its max, mark as not recovered
  if (v == "thermo.depth") {
    recovered[df_check$thermo.depth == max_thermo] <- FALSE
  }

  # Store back in df
  df_check[[paste0("recovered_", v)]] <- recovered
}
  
daily_recovery <- df_check %>%
  arrange(Date, .by_group = TRUE) %>%
  mutate(
    across(
      starts_with("recovered_"),
      ~ rollapply(.x, width = 2, FUN = all, fill = NA, align = "right"),
      .names = "{.col}_2days"
    )
  ) %>%
  mutate(
    across(
      starts_with("recovered_"),
      ~ if_else(thermo.depth == max_thermo, FALSE, .x)
    )
  ) %>%
  ungroup()
  
first_recovery <- daily_recovery %>%
  pivot_longer(
    cols = ends_with("_2days"),
    names_to = "variable",
    values_to = "recovered"
  ) %>%
  group_by(variable) %>%
  filter(recovered == TRUE) %>%
  dplyr::summarise(
    recovery_date = min(Date, na.rm = TRUE),
    .groups = "drop"
  )

first_recovery_clean <- first_recovery %>%
  mutate(variable = sub("_2days$", "", variable), variable = sub("^recovered_", "", variable) )%>%
  pivot_wider(names_from = variable, values_from = recovery_date, names_prefix = "first_recovery_")

# Join back to main dataset
Tutira_MeanCI_Daily_Recovery_ND <- bind_cols(Tutira_MeanCI_Daily_Recovery_ND, first_recovery_clean)
```

## Resilience and Resistance

### Structural

```{r}
#rename
Tutira_D_WT <- Tutira_MeanCI_Daily_Recovery_Depths

vars <- c("TmpWtr", "DOconc", "DOpsat", "pH", "FlChlr", "FlPhyc", "Cond", "SpCond", "TurbRT")

#resistance (RS)
#pulls out maximum disturbance values per depth
Tutira_D_WT_during <- Tutira_D_WT %>%
  filter(Date >= first_during_time & Date <= last_during_time) %>%
  pivot_longer(cols = all_of(vars), names_to = "Variable", values_to = "Value") %>%
  pivot_longer(cols = ends_with("_mean"), names_to = "MeanVar", values_to = "MeanValue") %>%
  filter(substr(MeanVar, 1, nchar(MeanVar) - 5) == Variable) %>%
  pivot_longer(cols = starts_with("first_recovery_"), names_to = "RecoveryVar", values_to = "first_recovery", names_prefix = "first_recovery_")%>%
  filter(RecoveryVar == Variable)%>%
  group_by(Depth, Variable) %>%
  slice_max(order_by = abs(Value - MeanValue), n = 1)%>%
  mutate(
    P0 = Value,
    C0 = MeanValue,
    t0 = Date,
    D0 = P0 - C0,
    RTB = as.numeric(first_recovery - t0)
  ) %>%
  ungroup() %>%
  dplyr::select(Depth, Variable, P0, C0, t0, D0, RTB, first_recovery)

#calculates RS
Tutira_D_WT_RS <- Tutira_D_WT_during%>%
  group_by(Depth, Variable)%>%
  mutate(RS = 1-((2*abs(D0))/(abs(D0) + C0)))

#calculates magnitude for each time point then average
Tutira_D_WT_RL <- bind_rows(
  lapply(vars, function(var) {
    # dynamically get the first recovery time column for this variable
    recovery_col <- paste0("first_recovery_", var)
    recovery_time <- Tutira_D_WT[[recovery_col]][1]  # assuming same for all depths

    # select relevant columns
    Tutira_D_WT %>%
      dplyr::select(Depth, Date, all_of(var), all_of(paste0(var, "_mean"))) %>%
      rename(Value = all_of(var),
             MeanValue = all_of(paste0(var, "_mean"))) %>%
      filter(Date >= recovery_time - hours(72) &
             Date <= recovery_time + hours(72)) %>%
      group_by(Depth) %>%
      mutate(Di = Value - MeanValue) %>%   # deviation at each timestamp
      summarise(
        Px = mean(Value, na.rm = TRUE),       # mean observed
        Cx = mean(MeanValue, na.rm = TRUE),   # mean baseline
        Dx = mean(abs(Di), na.rm = TRUE),     # mean magnitude of deviation
        tx = mean(Date)                        # midpoint of window
      ) %>%
      ungroup() %>%
      mutate(Variable = var)
  })
)

#merges datasets
Tutira_D_WT_RSRL <- Tutira_D_WT_RS%>%
  left_join(Tutira_D_WT_RL %>% dplyr::select(c(Depth, Variable, Px, Cx, tx, Dx)), by = c("Depth", "Variable"))

#calculates resilience (RL)
Tutira_D_WT_RLRS <- Tutira_D_WT_RSRL%>%
  group_by(Depth, Variable)%>%
  mutate(RL = (((2*abs(D0))/(abs(Dx) + abs(D0)))-1),
         RR = ifelse(RTB > 0, (abs(D0) - abs(Dx)) / RTB, NA_real_))

#merges datasets with RS and RL
Tutira_D_WT_p1 <- Tutira_D_WT%>%
  left_join(Tutira_D_WT_RLRS, by = "Depth")
```

### Functional

```{r}
#rename
Tutira_ND_WT <- Tutira_MeanCI_Daily_Recovery_ND

#define variables
vars <- c("Depth_max_FlChlr", "Depth_max_FlPhyc", "Anoxic_Depth", "thermo.depth",
          "schmidt.stability", "lake.number", "Meta_Top", "Meta_Bottom", "Buoyancy")

#resistance (RS)
#pulls out maximum disturbance values per depth
Tutira_ND_WT_during <- Tutira_ND_WT %>%
  filter(Date >= first_during_time & Date <= last_during_time) %>%
  pivot_longer(cols = all_of(vars), names_to = "Variable", values_to = "Value") %>%
  pivot_longer(cols = ends_with("_mean"), names_to = "MeanVar", values_to = "MeanValue") %>%
  filter(substr(MeanVar, 1, nchar(MeanVar) - 5) == Variable) %>%
  pivot_longer(cols = starts_with("first_recovery_"), names_to = "RecoveryVar", values_to = "first_recovery", names_prefix = "first_recovery_")%>%
  filter(RecoveryVar == Variable)%>%
  group_by(Variable) %>%
  slice_max(order_by = abs(Value - MeanValue), n = 1)%>%
  mutate(
    P0 = Value,
    C0 = MeanValue,
    t0 = Date,
    D0 = P0 - C0,
    RTB = as.numeric(first_recovery - t0)
  ) %>%
  ungroup() %>%
  dplyr::select(Variable, P0, C0, t0, D0, RTB, first_recovery)

#calculates RS
Tutira_ND_WT_RS <- Tutira_ND_WT_during%>%
  group_by(Variable)%>%
  mutate(RS = 1-((2*abs(D0))/(abs(D0) + C0)))

#calculates magnitude for each time point then average
Tutira_ND_WT_RL <- bind_rows(
  lapply(vars, function(var) {
    # dynamically get the first recovery time column for this variable
    recovery_col <- paste0("first_recovery_", var)
    recovery_time <- Tutira_ND_WT[[recovery_col]][1]  # assuming same for all depths

    # select relevant columns
    Tutira_ND_WT %>%
      dplyr::select(Date, all_of(var), all_of(paste0(var, "_mean"))) %>%
      rename(Value = all_of(var),
             MeanValue = all_of(paste0(var, "_mean"))) %>%
      filter(Date >= recovery_time - hours(72) &
             Date <= recovery_time + hours(72)) %>%
      mutate(Di = Value - MeanValue) %>%   # deviation at each timestamp
      dplyr::summarise(
        Px = mean(Value, na.rm = TRUE),       # mean observed
        Cx = mean(MeanValue, na.rm = TRUE),   # mean baseline
        Dx = mean(abs(Di), na.rm = TRUE),     # mean magnitude of deviation
        tx = mean(Date)                        # midpoint of window
      ) %>%
      ungroup() %>%
      mutate(Variable = var)
  })
)

#merges datasets
Tutira_ND_WT_RSRL <- Tutira_ND_WT_RS%>%
  left_join(Tutira_ND_WT_RL %>% dplyr::select(c(Variable, Px, Cx, tx, Dx)), by = c("Variable"))

#calculates Resilience (RL)
Tutira_ND_WT_RLRS <- Tutira_ND_WT_RSRL%>%
  group_by(Variable)%>%
  mutate(RL = ((2*abs(D0))/(abs(Dx) + abs(D0)))-1,
         RR = ifelse(RTB > 0, (abs(D0) - abs(Dx)) / RTB, NA_real_))

#merges datasets with RS and RL
Tutira_ND_WT_p1 <- Tutira_ND_WT%>%
  merge(Tutira_ND_WT_RLRS)
```

## Rate of Resilience

### Structural

```{r}
#define variables
vars <- c("TmpWtr", "DOconc", "DOpsat", "pH", "FlChlr", "FlPhyc", "Cond", "SpCond", "TurbRT")

# daily rate of resilience for each variable and depth
Tutira_D_WT_RR_daily <- bind_rows(
  lapply(vars, function(var) {
    
    recovery_col <- paste0("first_recovery_", var)

    # extract recovery times per depth (a tibble)
    depth_recovery <- Tutira_D_WT %>% 
      dplyr::select(Depth, !!recovery_col) %>%
      distinct() %>%
      rename(recovery_time = !!recovery_col)

    # Merge observed + baseline for this variable
    df <- Tutira_D_WT %>%
      dplyr::select(Depth, Date, all_of(var), all_of(paste0(var, "_mean"))) %>%
      rename(Value = all_of(var),
             MeanValue = all_of(paste0(var, "_mean"))) %>%
      mutate(
        Variable = var,
        Dd = Value - MeanValue
      ) %>%
      left_join(depth_recovery, by = "Depth")

    # Add t0 and D0
    df <- df %>%
      left_join(
        Tutira_D_WT_during %>% 
          dplyr::select(Depth, Variable, t0, D0),
        by = c("Depth", "Variable")
      )

    # RL for each day
    df %>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )
  })
)

Tutira_D_WT_RR_daily$Year <- format(as.POSIXct(Tutira_D_WT_RR_daily$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
```

### Functional

```{r}
vars <- c("Depth_max_FlChlr", "Depth_max_FlPhyc", "Anoxic_Depth", "thermo.depth",
          "schmidt.stability", "lake.number", "Meta_Top", "Meta_Bottom", "Buoyancy")

# daily rate of resilience for each non-depth variable
Tutira_ND_WT_RR_daily <- bind_rows(
  lapply(vars, function(var) {
    
    # recovery time for this variable (only 1 value)
    recovery_col <- paste0("first_recovery_", var)
    recovery_time <- Tutira_ND_WT[[recovery_col]][1]

    # t0 and D0 from the 'during' disturbance period
    t0_D0 <- Tutira_ND_WT_during %>% 
      filter(Variable == var) %>%
      distinct(Variable, t0, D0)

    # observed + baseline series
    df <- Tutira_ND_WT %>%
      dplyr::select(Date, all_of(var), all_of(paste0(var, "_mean"))) %>%
      rename(
        Value = all_of(var),
        MeanValue = all_of(paste0(var, "_mean"))
      ) %>%
      mutate(
        Variable = var,
        recovery_time = recovery_time,   # add here instead of select()
        Dd = Value - MeanValue        # daily deviation
      ) %>%
      left_join(t0_D0, by = "Variable") %>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )

    df
  })
)

Tutira_ND_WT_RR_daily$Year <- format(as.POSIXct(Tutira_ND_WT_RR_daily$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
```

# Graphing

## Figure 2

-   Conceptual Figure

```{r}
concept_ts <- data.frame(
  time = 1:27,
  value = c(
    rep(1, 5),          # baseline
    1.6, 1.8, 1.95, 2.0, 1.98,     # storm impact
    1.8, 1.5,           # early recovery
    1.3, 1.15, 1.05, 1.03,   # recovery
    rep(1, 4),           # recovered
    1.03, 1.15, 1.30, 1.27, 1.15, 1.05, 1
  )
)

storm_start <- 5
storm_end   <- 10
recovery_end <- 16
recovery_end_2 <- 27
baseline <- 1
ci_width  <- 0.1  # half-width of 95% CI
x_arrow <- 9
y_start <- 1.05
y_end   <- 1.9
y_mid   <- (y_start + y_end) / 2  # middle point

#center points of boxes
mid_x_S<- storm_start + (storm_end - storm_start) / 2
mid_x_R <- storm_end + (recovery_end - storm_end) / 2
mid_x_R2 <- recovery_end + (recovery_end_2 - recovery_end) / 2
mid_x_RL <- storm_end + (recovery_end_2 - storm_end) / 2

conceptual <- ggplot(concept_ts, aes(time, value)) +

  # Storm period shading
  annotate(
    "rect",
    xmin = storm_start,
    xmax = storm_end,
    ymin = -Inf,
    ymax = Inf,
    fill = '#66C2C7',
    alpha = 0.2
  ) +
  
  # Recovery shading
  annotate(
    "rect",
    xmin = storm_end,
    xmax = recovery_end,
    ymin = -Inf,
    ymax = Inf,
    fill = '#196F3D',
    alpha = 0.2
  ) +
  
  #Long-term Recovery
  annotate(
    "rect",
    xmin = recovery_end,
    xmax = recovery_end_2,
    ymin = -Inf,
    ymax = Inf,
    fill = '#003B19',
    alpha = 0.2
  ) +
  
   # 95% CI ribbon
  geom_ribbon(
    aes(ymin = baseline - ci_width, ymax = baseline + ci_width),
    fill = '#BDC3C7',
    alpha = 0.5
  ) +

  # Baseline
  geom_hline(
    yintercept = 1,
    linetype = "dashed",
    color = "black"
  ) +

  # System response line
  geom_line(linewidth = 1, color = "#7B9E4C") +
  #geom_point(size = 2) +

  # Resistance arrow
  # annotate(
  #   "segment",
  #   x = 9, xend = 9,
  #   y = 1, yend = 1.95,
  #   arrow = arrow(length = unit(0.2, "cm"))
  # ) +
  annotate(
    "segment",
    x = x_arrow, xend = x_arrow,
    yend = y_start + 0.02, y = y_mid - 0.1,  # leave small gap for text
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  # Second half of arrow
  annotate(
    "segment",
    x = x_arrow, xend = x_arrow,
    y = y_mid + 0.1, yend = y_end,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  # Text in the middle
  annotate(
    "text",
    x = x_arrow,
    y = y_mid,
    label =  "D[0]",
    parse = TRUE,
    fontface = "bold",
    vjust = 0.5, size = 3.5
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.8,
    label = "Resistance",
    color = '#842A11'
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.55,
    label = "D[0] == V[0] - B[0]",
    parse = TRUE,
    color = '#842A11'
  ) +
  geom_point(aes(x = 9, y = 2), color = "black", size = 2)+
  # Dashed rectangle around point + arrow + text
annotate(
  "rect",
  xmin = 8.5, xmax = 9.5,   # horizontal span
  ymin = 0.65, ymax = 2.4,   # vertical span
  color = "#842A11",           # border color
  linetype = "dashed",       # dashed border
  fill = NA,                 # no fill
  linewidth = 0.7
)+
  annotate(
    "text",
    x = 9,
    y = 0.8,
    label =  "B[0]",
    parse = TRUE, size = 3.5
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.2,
    label =  "V[0]",
    parse = TRUE, size = 3.5
  ) +

  # Recovery arrow
  # annotate(
  #   "segment",
  #   x = storm_end,
  #   xend = recovery_end,
  #   y = 0.9,
  #   yend = 0.9,
  #   arrow = arrow(length = unit(0.2, "cm"))
  # ) +
  annotate(
    "text",
    x = mid_x_R,
    y = 3.2,
    label = "Recovery \nPeriod",
    fontface = "bold"
  ) +
  annotate(
    "text",
    x = mid_x_R2,
    y = 3.2,
    label = "Long - Term\nRecovery Period",
    fontface = "bold"
  ) +
  geom_point(aes(x = 16, y = 1.03), color = "#674A84", size = 3)+
  annotate(
    "text",
    x = 16,
    y = 1.8,
    label = "Initial\nRecovery",
    color = '#674A84'
  ) +

  # Labels
  annotate(
    "text",
    x = mid_x_S,
    #y = max(concept_ts$value) + 0.1,
    y = 3.2,
    label = "Storm\nPeriod",
    fontface = "bold"
  ) +
  #resilience
  #points
  geom_point(aes(x = 10, y = 1.98), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 11, y = 1.8), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 12, y = 1.5), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 13, y = 1.3), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 14, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 15, y = 1.05), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 16, y = 1.03), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 17, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 18, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 19, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 20, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 21, y = 1.03), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 22, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 23, y = 1.30), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 24, y = 1.27), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 25, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 26, y = 1.05), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 27, y = 1), shape = 1, size = 2, color = '#594F3B') +
  #baseline labels
  annotate("text", x = 10, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  # annotate("text", x = 11, y = 0.95, label =  "C[2]", parse = TRUE) +
  # annotate("text", x = 12, y = 0.95, label =  "C[3]", parse = TRUE) +
  # annotate("text", x = 13, y = 0.95, label =  "C[4]", parse = TRUE) +
  # annotate("text", x = 14, y = 0.95, label =  "C[5]", parse = TRUE) +
  # annotate("text", x = 15, y = 0.95, label =  "C[6]", parse = TRUE) +
  annotate("text", x = 16, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate("text", x = 27, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  #actual value labels
  annotate("text", x = 10, y = 2.16, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  # annotate("text", x = 11, y = 1.86, label =  "P[2]", parse = TRUE, hjust = 0.3) +
  # annotate("text", x = 12, y = 1.56, label =  "P[3]", parse = TRUE, hjust = 0) +
  # annotate("text", x = 13, y = 1.36, label =  "P[4]", parse = TRUE, hjust = 0.2) +
  # annotate("text", x = 14, y = 1.21, label =  "P[5]", parse = TRUE, hjust = 0.5) +
  # annotate("text", x = 15, y = 1.11, label =  "P[6]", parse = TRUE) +
  annotate("text", x = 16, y = 1.23, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate("text", x = 27, y = 1.2, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate(
    "text",
    x = mid_x_RL,
    y = 2.8,
    label = "Resilience",
   # hjust = 0,
    color = '#D57124'
  ) +
  annotate(
    "text",
    x = mid_x_RL,
    y = 2.55,
    label = "D[t] == V[t] - B[t]",
    #hjust = 0,
    parse = TRUE,
    color = '#D57124'
  ) +
  geom_point(aes(x = 9, y = 2), color = "black", size = 3)+
  # Dashed rectangle around point + arrow + text
annotate(
  "rect",
  xmin = 9.5, xmax = 27.8,   # horizontal span
  ymin = 0.65, ymax = 2.4,   # vertical span
  color = '#D57124',           # border color
  linetype = "dashed",       # dashed border
  fill = NA,                 # no fill
  linewidth = 0.7            # optional border thickness
)+
  
  labs(
    x = "Day",
    y = "Lake Value"
  ) +
  scale_x_continuous(breaks = c(0,2,4,6,8,10,12,14,16,18,20,22,24,26))+
  scale_y_continuous(limits = c(0.5, 3.5), breaks = c(1, 2, 3))+

  theme_pubr() +
  theme(
    panel.grid = element_blank()
  )
conceptual

# ggsave(
#   filename = "Draft Paper Graphs/Conceptual_new.png",
#   plot = conceptual,
#   width = 6, #14
#   height = 3, #7
#   dpi = 300
# )
```

## Figure 3

-   storm identification

```{r}
# pull start/end into simple scalars
Tutira_first_time <- Tutira_storm$first_during_time
Tutira_last_time  <- Tutira_storm$last_during_time

#barometric pressure
BP <- ggplot(data = Tutira_storm, aes(x = datetime, y = PrBaro))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  #geom_line(color = "#7B9E4C")+
  geom_line(color = "black")+
  ylab('Barometric Pressure\n(hPa)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  #geom_hline(yintercept = unique(Tutira_storm$PrBaro_10th), linetype = 'solid', color = 'black') +
  #scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  scale_x_datetime(breaks = "1 week", labels = NULL) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
BP

#wind speed
WS<-ggplot(data = Tutira_storm, aes(x = datetime, y = WndSpd))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  geom_line(color = "black")+
  ylab('Wind Speed\n(m/s)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  #geom_hline(yintercept = unique(Tutira_storm$WS_90th), linetype = 'solid', color = 'black') +
  #scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  scale_x_datetime(breaks = "1 week", labels = NULL) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
WS

#rainfall
R<-ggplot(data = Tutira_storm, aes(x = datetime, y = PpRain))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  geom_col(color = "black") +
  ylab('Precipitation\n(mm)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
R

Tutira_Cyclone_patch <-
  (BP / WS / R) +
  plot_layout(heights = c(1, 1, 1)) &
  theme(
    plot.margin = margin(0, 0, 0, 0),
    panel.spacing = unit(0, "lines")
  )&
  plot_annotation(
     tag_levels = "A")#&
  # theme(
  #   plot.tag.position = c(0.13, 0.95)#,
  #   #plot.tag = element_text(face = "bold")
  # )
Tutira_Cyclone_patch

#saving
# ggsave(
#   filename = "Draft Paper Graphs/Tutira_Cyclone_Gabrielle.png",
#   plot = Tutira_Cyclone_patch,
#   width = 5, #14
#   height = 6, #7
#   dpi = 300
# )
```

## Figure 4

-   Heatmaps

```{r}
# -------------------------------
# Function to create load.ts objects
# -------------------------------
make_wtr_object <- function(data, var, prefix) {
  df <- data %>%
    filter(datetime >= '2022-07-01 00:00:00' &
           datetime <= '2023-07-31 23:00:00') %>%
    select(datetime, Depth, all_of(var)) %>%
    pivot_wider(
      names_from = Depth,
      names_prefix = prefix,
      names_sort = TRUE,
      values_from = all_of(var)
    ) %>%
    drop_na()

  df_fmt <- df %>%
    mutate(datetime = format(datetime, "%Y-%m-%dT%H:%M:%SZ"))

  char_mat <- apply(df_fmt, 2, as.character)
  header <- paste(colnames(df_fmt), collapse = "\t")
  rows <- apply(char_mat, 1, function(x) paste(x, collapse = "\t"))
  txt_lines <- c(header, rows)

  con <- textConnection(txt_lines, "r")
  out <- load.ts(con)
  close(con)

  out$datetime <- as.POSIXct(
    format(df$datetime, "%Y-%m-%dT%H:%M:%SZ"),
    format = "%Y-%m-%dT%H:%M:%SZ",
    tz = "UTC"
  )

  return(out)
}

# -------------------------------
# Create load.ts objects
# -------------------------------
Tutira.wtr  <- make_wtr_object(Tutira_interp2, "TmpWtr", "wtr_")
Tutira.DO   <- make_wtr_object(Tutira_interp2, "DOconc", "DO_")
Tutira.C    <- make_wtr_object(Tutira_interp2, "FlChlr", "C_")
Tutira.Phy  <- make_wtr_object(Tutira_interp2, "FlPhyc", "Phy_")
Tutira.Turb <- make_wtr_object(Tutira_interp2, "TurbRT", "Turb_")

# -------------------------------
# Function to save heatmaps with bigger text
# -------------------------------
save_heatmap <- function(obj, filename, title = NULL) {
  png(filename, width = 2400, height = 1200, res = 300)
  
  # Increase text sizes
  par(mar = c(4, 5, 3, 5),      # margins (bottom, left, top, right)
      cex.axis = 1.5,           # tick labels
      cex.lab  = 1.5,           # x/y axis labels
      cex.main = 1.5,             # main title
      col.main = '#452D7A')     # title color
  
  wtr.heat.map(obj, main = "")
  
  if (!is.null(title)) {
    # Split title so parentheses go on new line
    title_split <- gsub(" \\(", "\n(", title)
    
    title(main = title_split, adj = 0,
          col.main = '#452D7A', cex.main = 1.5)
  }
  
  dev.off()
}

# -------------------------------
# Save each heatmap
# -------------------------------
save_heatmap(Tutira.wtr,  "Graphs/heatmaps_temp.png", "Water Temperature (°C)")
save_heatmap(Tutira.DO,   "Graphs/heatmaps_do.png", "Dissolved Oxygen (mg/L)")
save_heatmap(Tutira.C,    "Graphs/heatmaps_chl.png", "Chlorophyll-a (RFU)")
save_heatmap(Tutira.Phy,  "Graphs/heatmaps_phyco.png", "Phycocyanin (RFU)")
save_heatmap(Tutira.Turb, "Graphs/heatmaps_turb.png", "Turbidity (NTU)")

#upload heatmaps
img1 <- rasterGrob(readPNG("Graphs/heatmaps_temp.png"))
img2 <- rasterGrob(readPNG("Graphs/heatmaps_do.png"))
img3 <- rasterGrob(readPNG("Graphs/heatmaps_chl.png"))
img4 <- rasterGrob(readPNG("Graphs/heatmaps_phyco.png"))
img5 <- rasterGrob(readPNG("Graphs/heatmaps_turb.png"))

#new
blank <- rectGrob(gp = gpar(col = NA, fill = NA))

# Layout matrix
layout_mat <- rbind(
  c(1, 2),
  c(3, 4),
  c(5, 6)
)

# Create the arranged grob
combined <- arrangeGrob(
  img1, blank,
  img2, img5,
  img3, img4,
  layout_matrix = layout_mat,
  widths = c(1, 1),
  heights = c(1, 1, 1)
)

# Labels corresponding to the non-blank images
labels <- c("A", "B", "C", "D", "E")

# Open PNG device
png("Graphs/combined_heatmaps_labeled.png", width = 3600, height = 2600, res = 300)

# Draw the combined grob
grid.draw(combined)

# Add labels manually using npc coordinates
label_positions <- list(
  c(0.03, 0.97),  # img1
  c(0.03, 0.64),  # img2
  c(0.53, 0.64),  # img5
  c(0.03, 0.30),  # img3
  c(0.53, 0.30)   # img4
)

for(i in seq_along(labels)) {
  grid.text(labels[i],
            x = unit(label_positions[[i]][1], "npc"),
            y = unit(label_positions[[i]][2], "npc"),
            gp = gpar(fontsize = 14, fontface = "bold"))
}
```

## Figure 5

-   Structural Resistance

```{r}
#colors depending on physical, chemical, or biological
# variable levels
var_levels <- c(
  "TmpWtr", "Cond", "DOconc", "pH", "TurbRT",
  "FlChlr", "FlPhyc"
)
# Define variable types
var_type <- c(
  "TmpWtr" = "Physical",
  "DOconc" = "Chemical",
  "DOpsat" = "Chemical",
  "pH"     = "Chemical",
  "FlChlr" = "Biological",
  "FlPhyc" = "Biological",
  "Cond"   = "Chemical",
  "SpCond" = "Chemical",
  "TurbRT" = "Chemical"
)

# Combine with labels for axis text
var_labels <- c(
  "TmpWtr" = "Water\ntemperature\n(°C)",
  "DOconc" = "Dissolved\noxygen\n(mg/L)",
  "DOpsat" = "Dissolved\noxygen\n(%)",
  "pH"     = "pH",
  "FlChlr" = "Chlorophyll-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)",
  "Cond"   = "Conductivity\n(µS/cm)",
  "SpCond" = "Specific conductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)"
)

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)

#graphing - boxplot with one color
RS_Box <- Tutira_D_WT_p1%>%
  filter(!Variable %in% c("SpCond", "DOpsat", 'Cond','pH'))%>%
  mutate(
    Type = factor(var_type[as.character(Variable)], levels = c("Physical", "Chemical", "Biological")),
    Variable = factor(
      Variable,
      levels = var_levels,
      labels = var_labels[var_levels])
  )%>%
  ggplot(aes(x = Variable, y = RS, fill = Type))+
  geom_boxplot()+
  scale_fill_manual(values = type_colors)+
  scale_y_continuous(limits = c(-1, 1))+
  labs(y = "Resistance", x = NULL, fill = "")+
  theme_pubr()+
  theme(axis.text.x = element_text(color = '#452D7A'))
RS_Box

# ggsave(
#   filename = "Draft Paper Graphs/RS_S_Box_colors_updated_colors.png",
#   plot = RS_Box,
#   width = 8, #14
#   height = 4, #7
#   dpi = 300
# )
```

## Figure 6

-   Structural recovery heatmap with depth

```{r}
# ---- DEPTH-BASED ----
recovery_vars_depth <- grep("^first_recovery_", colnames(Tutira_D_WT_p1), value = TRUE)

#calculating days for each recovery
depth_df <- Tutira_D_WT_p1 %>%
  dplyr::select(Depth, last_during_time, all_of(recovery_vars_depth)) %>%
  pivot_longer(
    cols = all_of(recovery_vars_depth),
    names_to = "variable",
    values_to = "recovery_date"
  ) %>%
  mutate(
    recovery_delay = as.numeric(difftime(recovery_date, last_during_time, units = "days")),
    variable = gsub("first_recovery_", "", variable),
    Depth = as.numeric(as.character(Depth)),
    Type = "Structural",  # fixed assignment
    Property = case_when(
      variable == 'TmpWtr' ~ "Physical",
      variable %in% c('Cond', 'DOconc', 'DOpsat', 'pH', 'SpCond', 'TurbRT') ~ "Chemical",
      variable %in% c('FlChlr', 'FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    )
  ) %>%
  dplyr::select(variable, Depth, recovery_delay, Type, Property)%>%
  group_by(variable, Depth, Type, Property)%>%
  dplyr::summarise_at('recovery_delay', mean, na.rm=TRUE)%>%
  ungroup

#graphing
variable_order <- c(
  # Physical
  "TmpWtr",
  # Chemical
  "Cond", "DOconc", "DOpsat", "pH", "SpCond", "TurbRT", 
  # Biological
  "FlChlr", "FlPhyc"
)

depth_df <- depth_df %>%
  mutate(Property = factor(Property, levels = c("Physical", "Chemical", "Biological")))
filtered_vars <- unique(depth_df$variable[!depth_df$variable %in% c('SpCond', 'pH', 'DOpsat', 'Cond')])

var_labels <- c(
  # Physical
  "TmpWtr" = "Water\nTemperature\n(°C)",
  #chemical
  #"Cond" = "Conductivity\n(µS/cm)",
  "DOconc" = "Dissolved\nOxygen\n(mg/L)",
  #"DOpsat" = "Oxygen\nSaturation\n(%)",
  #"pH" = "pH",
  #"SpCond" = "Specific\nConductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)",
  # Biological
  "FlChlr" = "Chl-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)"
)

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)

depth_df <- depth_df %>%
  mutate(
    Property_colored = paste0(
      "<span style='color:",
      type_colors[Property],
      "'>",
      Property,
      "</span>"
    )
  )
ordered_levels <- paste0(
  "<span style='color:",
  type_colors[c("Physical","Chemical","Biological")],
  "'>",
  c("Physical","Chemical","Biological"),
  "</span>"
)

depth_df <- depth_df %>%
  mutate(Property_colored = factor(Property_colored,
                                   levels = ordered_levels))

depth_df <- depth_df %>%
  mutate(variable = factor(variable, levels = names(var_labels), labels = var_labels[names(var_labels)]))

RC<- ggplot(depth_df%>% filter(Type == 'Structural', variable != 'NA'), aes(x = variable, y = Depth, fill = recovery_delay)) +
  geom_tile(color = "white") +
  #scale_fill_viridis_c(option = "B", na.value = "grey80", limits = c(0, 364)) +
  scale_fill_gradientn(
  colors = c("#66C2C7", "#7B9E4C", "#196F3D"),  # green → blue → green
  #colors = c('#A6262D', '#A626A6', '#4E2294'),
  na.value = "grey80",
  limits = c(0, 366)
)+
  #scale_x_discrete(labels = variable_order) +
  scale_y_reverse(breaks = seq(37, 1, by = -2)) +
  #scale_x_discrete(labels = var_labels) + 
  labs(x = NULL, y = "Depth (m)", fill = "Days till Recovered") +
  facet_wrap(~Property_colored, scales = "free_x", space = "free_x") +
  theme_pubr()+ 
  theme(
  #   #axis.text.x = element_markdown(size = 9, angle = 45, hjust = 1, lineheight = 1.1),
     panel.grid = element_blank(),
     axis.text.x = element_text(color = '#452D7A'),
     strip.text = element_markdown())
  #   axis.ticks.length = unit(0.2, "cm"),
  #   axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x  = element_text(size = 8),
  #   axis.text.y  = element_text(size = 8),
  #   legend.text   = element_text(size = 8),
  #   legend.title  = element_text(size = 8),
  #   strip.text    = element_text(size = 8)
  # )
RC

#save
# ggsave(
#   filename = "Draft Paper Graphs/facet_heatmap_newcolors.png",
#   plot = RC,
#   width = 5, #14
#   height = 6, #7
#   dpi = 300
# )
```

## Figure 7

-   Recovery and resilience for surface structural and functional variables

```{r}
#find longest recovery time - thermocline depth
TD_rec_time   <- min(as.Date(Tutira_ND_WT_p1$first_recovery_thermo.depth), na.rm = TRUE) #2023-09-12
Temp_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_TmpWtr[Tutira_D_WT_p1$Depth == 1]), na.rm = TRUE) #2023-04-21
#Turb_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_TurbRT[Tutira_D_WT_p1$Depth == 1]), na.rm = TRUE)
DO_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_DOconc[Tutira_D_WT_p1$Depth == 1]), na.rm = TRUE) #2023-03-21
chl_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_FlChlr[Tutira_D_WT_p1$Depth == 1]), na.rm = TRUE) #2023-02-17
Hyp_rec_time <- min(as.Date(Tutira_ND_WT_p1$first_recovery_Anoxic_Depth), na.rm = TRUE) #2023-02-22
DC_rec_time <- min(as.Date(Tutira_ND_WT_p1$first_recovery_Depth_max_FlChlr), na.rm = TRUE) #2023-08-29

#picking out storm periods
start_time <- min(as.Date(Tutira_ND_WT_p1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_ND_WT_p1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp <- Tutira_D_WT_p1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_temp <- 10 #min(df_Temp$TmpWtr, na.rm = TRUE)
y_max_temp <- max(df_Temp$TmpWtr, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R <- ggplot(df_Temp, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'TmpWtr', Depth == 1, Date < Temp_rec_time, Date > end_time), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(10, y_max_temp),
  breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = c(0.7,0.8), axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R

############################################ surface Dissolved Oxygen ########################################

df_DO <- Tutira_D_WT_p1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_DO <- 4 #min(df_DO$DOconc, na.rm = TRUE) 
y_max_DO <- max(df_DO$DOconc, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R <- ggplot(df_DO, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'DOconc', Depth == 1, Date < DO_rec_time, Date > end_time), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R

############################################ surface Chlorophyll-a ########################################

df_chl <- Tutira_D_WT_p1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl$FlChlr, na.rm = TRUE) 
y_max_chl <- 3.4 #max(df_chl$FlChlr, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R <- ggplot(df_chl, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'FlChlr', Depth == 1, Date < chl_rec_time, Date > end_time), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R

############################################ Thermocline Depth ########################################

#for secondary axis
# ranges
y1_min <- min(Tutira_ND_WT_p1$thermo.depth, na.rm = TRUE)
y1_max <- max(Tutira_ND_WT_p1$thermo.depth, na.rm = TRUE)

y2_min <- -1
y2_max <- 1

# scale RL_Daily to thermo.depth range
scale_fun_TD <- function(x) {
  y1_max - (x - y2_min) / (y2_max - y2_min) * (y1_max - y1_min)
}

inv_scale_fun_TD <- function(x) {
  y2_min + (y1_max - x) / (y1_max - y1_min) * (y2_max - y2_min)
}

#limiting time on graph
df_TD <- Tutira_ND_WT_p1 %>%
  filter(Date >= x_min & Date <= x_max)

#setting y limits
y_min_TD <- min(df_TD$thermo.depth, na.rm = TRUE)
y_max_TD <- max(df_TD$thermo.depth, na.rm = TRUE)

#creating boxes for storm and recovery
storm_window_TD <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_TD, ymax = y_max_TD)
recovery_window_TD <- data.frame(xmin = end_time, xmax = TD_rec_time, ymin = y_min_TD, ymax = y_max_TD)

#graph
TD_R <- ggplot(df_TD, aes(x = Date, y = thermo.depth)) +
  geom_rect(data = storm_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  #geom_rect(data = recovery_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            #inherit.aes = FALSE, fill = '#27AE15', alpha = 0.2) +
  geom_rect(data = recovery_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = thermo.depth_lower, ymax = thermo.depth_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = thermo.depth_mean), colour = 'black', size = 1) +
  geom_line(color = '#7B9E4C', size = 1) +
  geom_line(data = Tutira_ND_WT_RR_daily%>% filter(Variable == 'thermo.depth', Date < TD_rec_time, Date > end_time), aes(x = Date, y = scale_fun_TD(RL_daily)), color = '#FF7B9C', size = 1, linetype = 'dashed')+
  geom_vline(xintercept = c(start_time, end_time, TD_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  #scale_y_reverse(name = 'Thermocline Depth\n(m)', sec.axis = sec_axis(~inv_scale_fun(.), name = "RL Daily")) +
  scale_y_reverse(
  name = 'Thermocline Depth\n(m)',
  limits = c(39, 0),
  sec.axis = sec_axis(
    ~inv_scale_fun_TD(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  labs(x = NULL) +
  theme_pubr()+
  theme(axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
  # theme(axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x   = element_text(size = 8),
  #   axis.text.y   = element_text(size = 8))

TD_R

############################################ Hypoxic Depth ########################################

df_Hyp <- Tutira_ND_WT_p1 %>%
  filter(Date >= x_min & Date <= x_max)

y_min_Hyp <- min(df_Hyp$Anoxic_Depth, na.rm = TRUE) 
y_max_Hyp <- max(df_Hyp$Anoxic_Depth, na.rm = TRUE)

scale_fun_Hyp <- function(x) {
  y_max_Hyp - (x - y2_min) / (y2_max - y2_min) * (y_max_Hyp - y_min_Hyp)
}

inv_scale_fun_Hyp <- function(x) {
  y2_min + (y_max_Hyp - x) / (y_max_Hyp - y_min_Hyp) * (y2_max - y2_min)
}

storm_window_Hyp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_Hyp, ymax = y_max_Hyp)
recovery_window_Hyp <- data.frame(xmin = end_time, xmax = Hyp_rec_time, ymin = y_min_Hyp, ymax = y_max_Hyp)

Hyp_R <- ggplot(df_Hyp, aes(x = Date, y = Anoxic_Depth)) +
  geom_rect(data = storm_window_Hyp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_Hyp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = Anoxic_Depth_lower, ymax = Anoxic_Depth_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = Anoxic_Depth_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = Anoxic_Depth, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Hyp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_ND_WT_RR_daily%>% filter(Variable == 'Anoxic_Depth', Date < Hyp_rec_time, Date > end_time), aes(x = Date, y = scale_fun_Hyp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_reverse(
  name = 'Hypoxic Depth\n(m)',
  limits = c(39, y_min_Hyp),
  sec.axis = sec_axis(
    ~inv_scale_fun_Hyp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Hypoxic Depth\n(m)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
         axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
Hyp_R

############################################ Depth of maximum Chlorophyll-a ########################################

df_DC <- Tutira_ND_WT_p1 %>%
  filter(Date >= x_min & Date <= x_max)

y_min_DC <- min(df_DC$Depth_max_FlChlr, na.rm = TRUE) 
y_max_DC <- max(df_DC$Depth_max_FlChlr, na.rm = TRUE)

scale_fun_DC <- function(x) {
  y_max_DC - (x - y2_min) / (y2_max - y2_min) * (y_max_DC - y_min_DC)
}

inv_scale_fun_DC <- function(x) {
  y2_min + (y_max_DC - x) / (y_max_DC - y_min_DC) * (y2_max - y2_min)
}

storm_window_DC <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DC, ymax = y_max_DC)
recovery_window_DC <- data.frame(xmin = end_time, xmax = DC_rec_time, ymin = y_min_DC, ymax = y_max_DC)

DC_R <- ggplot(df_DC, aes(x = Date, y = Depth_max_FlChlr)) +
  geom_rect(data = storm_window_DC, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DC, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = Depth_max_FlChlr_lower, ymax = Depth_max_FlChlr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = Depth_max_FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = Depth_max_FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DC_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_ND_WT_RR_daily%>% filter(Variable == 'Depth_max_FlChlr', Date < DC_rec_time, Date > end_time), aes(x = Date, y = scale_fun_DC(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_reverse(
  name = 'Depth of Maximum\nChlorophyll-a (m)',
  limits = c(y_max_DC, y_min_DC),
  sec.axis = sec_axis(
    ~inv_scale_fun_DC(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Depth of Maximum\nChlorophyll-a (m)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
         axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DC_R

#combine and save
base_plot <-
  ((SWT_R / DO_R / chl_R) |
  (TD_R  / Hyp_R / DC_R)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

# ggsave(
#   filename = "Draft Paper Graphs/Recovery_Resilience_6_labels_newcolors_dg.png",
#   plot = combined_plot,
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

## Figure 8

-   Yearly resilience for structural and functional variables

```{r}
#Structural
#WT
WTV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable == 'TmpWtr', Depth == 1, Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Water Temperature",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(TmpWtr = "Water Temperature"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#452D7A'))
WTV_DRL
#DO
DOV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable == 'DOconc', Depth == 1, Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Dissolved Oxygen",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(DOconc = "Dissolved Oxygen"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#452D7A'))
DOV_DRL
#Chl
CHV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable == 'FlChlr', Depth == 1, Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(FlChlr = "Chlorophyll-a"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.title.x = element_text(color = '#452D7A'))
CHV_DRL

#Functional
#thermocline Depth
TDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'thermo.depth', Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#2E5EAA'))
TDV_DRL

#Hypoxic Depth
HDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'Anoxic_Depth', Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#2E5EAA'))
HDV_DRL

#Depth of chl peak
CDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'Depth_max_FlChlr', Year %in% c(2022, 2023, 2024, 2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.title.x = element_text(color = '#2E5EAA'))
CDV_DRL

#combine and save
base_plot <-
  ((WTV_DRL / DOV_DRL / CHV_DRL) |
  (TDV_DRL  / HDV_DRL / CDV_DRL)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

# ggsave(
#   filename = "Draft Paper Graphs/Recovery_Resilience_alltime_violin_nolimits_newcolors_nl_updated.png",
#   plot = combined_plot,
#   width = 12,
#   height = 8,
#   dpi = 300
# )
```

# Supplementary

## Figures

### Figure S1

-   Resistance for functional variables

```{r}
#colors depending on physical, chemical, or biological
#define order of variables
var_levels <- c(
  "schmidt.stability", "thermo.depth", "Anoxic_Depth", "Depth_max_FlChlr", "Depth_max_FlPhyc"
)

# Define variable types
var_type <- c(
  "schmidt.stability" = "Physical",
  "thermo.depth" = "Physical",
  "Anoxic_Depth" = "Chemical",
  "Depth_max_FlChlr" = "Biological",
  "Depth_max_FlPhyc" = "Biological"
)

# Combine with labels for axis text
var_labels <- c(
  # Physical
  "schmidt.stability" = "Schmidt\nStability\n(J/m²)",
  "thermo.depth" = "Thermocline\nDepth (m)",
  # Chemical
  "Anoxic_Depth" = "Hypoxic\nDepth (m)",
  # Biological
  "Depth_max_FlChlr" = "Peak\nChl-a\nDepth (m)",
  "Depth_max_FlPhyc" = "Peak\nPhycocyanin\nDepth (m)"
)

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)

#graphing - boxplot with one color
RS_heatmap <- Tutira_ND_WT_p1%>%
  filter(Variable %in% c('schmidt.stability', 'thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr', 'Depth_max_FlPhyc'))%>%
  mutate(
    Type = factor(var_type[as.character(Variable)], levels = c("Physical", "Chemical", "Biological")),
    Variable = factor(
      Variable,
      levels = var_levels,
      labels = var_labels[var_levels])
  )%>%
  ggplot(aes(x = Variable, y = RS, color = Type))+
  geom_point()+
  scale_color_manual(values = type_colors)+
  scale_y_continuous(limits = c(-1, 1))+
  labs(y = "Resistance", x = NULL, color = "")+
  theme_pubr()+
  theme(axis.text.x = element_text(color = '#2E5EAA'))
RS_heatmap

# ggsave(
#   filename = "Draft Paper Graphs/RS_F_point_colors_labels.png",
#   plot = RS_heatmap,
#   width = 9, #14
#   height = 4, #7
#   dpi = 300
# )
```

### Figure S2

-   Average thermocline depth

```{r}
#caluclates avg thermocline depth
Tutira_TD <- Tutira_ND_WT_p1 %>%
  dplyr::select(MD, thermo.depth_mean) %>%
  group_by(MD)%>%
  dplyr::summarise_at(vars(thermo.depth_mean),mean,na.rm=TRUE)%>%
  ungroup() %>%
  mutate(TD_avg = mean(thermo.depth_mean))

TD_avg_value <- Tutira_TD %>%
  filter(thermo.depth_mean <= 15) %>% # do not take into consideration when the lake is mixed
  mutate(TD_avg = mean(thermo.depth_mean))  # numeric value

TD <- ggplot(data = Tutira_TD, aes(x = MD, y = thermo.depth_mean))+
  geom_point()+
  scale_y_reverse(limits = c(0,40), breaks = seq(0, 40, 5))+
  geom_hline(yintercept = TD_avg_value$TD_avg)+
  labs(x = NULL, y = 'Avg Thermocline Depth (m)') +
  scale_x_datetime(breaks = "1 month", labels = date_format("%b")) +
  theme_pubr()
TD

# ggsave(
#   filename = "Draft Paper Graphs/Tutira_AvgTD.png",
#   plot = TD,
#   width = 5, #14
#   height = 3, #7
#   dpi = 300
# )
```

### Figure S3

-   heatmap of days till recovery for functional variables

```{r}
# ---- DEPTH-BASED ----
recovery_vars <- grep("^first_recovery_", colnames(Tutira_ND_WT_p1), value = TRUE)

func_df <- Tutira_ND_WT_p1 %>%
  dplyr::select(last_during_time, all_of(recovery_vars)) %>%
  pivot_longer(
    cols = all_of(recovery_vars),
    names_to = "variable",
    values_to = "recovery_date"
  ) %>%
  mutate(
    recovery_delay = as.numeric(difftime(recovery_date, last_during_time, units = "days")),
    variable = gsub("first_recovery_", "", variable),
    #Depth = as.numeric(as.character(Depth)),
    Type = "Functional",  # fixed assignment
    Property = case_when(
      variable %in% c("schmidt.stability", "thermo.depth") ~ "Physical",
      variable == 'Anoxic_Depth' ~ "Chemical",
      variable %in% c('Depth_max_FlChlr', 'Depth_max_FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    )
  ) %>%
  dplyr::select(variable, recovery_delay, Type, Property)%>%
  group_by(variable, Type, Property)%>%
  dplyr::summarise_at('recovery_delay', mean, na.rm=TRUE)%>%
  ungroup

# Define variable types
varible_order <- c(
#physical
  "schmidt.stability", "thermo.depth", 
  #chemical
  "Anoxic_Depth",
  #biological,
  "Depth_max_FlChlr", "Depth_max_FlPhyc"
)

# Combine with labels for axis text
var_labels <- c(
  # Physical
  "schmidt.stability" = "Schmidt\nStability\n(J/m²)",
  "thermo.depth" = "Thermocline\nDepth (m)",
  # Chemical
  "Anoxic_Depth" = "Hypoxic\nDepth (m)",
  # Biological
  "Depth_max_FlChlr" = "Peak\nChl-a\nDepth (m)",
  "Depth_max_FlPhyc" = "Peak\nPhycocyanin\nDepth (m)"
)

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)
func_df <- func_df %>%
  mutate(
    Property_colored = paste0(
      "<span style='color:",
      type_colors[Property],
      "'>",
      Property,
      "</span>"
    )
  )
ordered_levels <- paste0(
  "<span style='color:",
  type_colors[c("Physical","Chemical","Biological")],
  "'>",
  c("Physical","Chemical","Biological"),
  "</span>"
)

func_df <- func_df %>%
  mutate(Property_colored = factor(Property_colored, levels = ordered_levels))%>%
  mutate(dummy_x = "All")


RC<- ggplot(func_df%>% filter(Type == 'Functional', !variable %in% c('Buoyancy', 'Meta_Bottom', 'Meta_Top', 'lake.number')), aes(x = variable, y = dummy_x, fill = recovery_delay)) +
  geom_tile(color = "white") +
  #scale_fill_viridis_c(option = "B", na.value = "grey80", limits = c(0, 364)) +
  scale_fill_gradientn(
  colors = c("#66C2C7", "#7B9E4C", "#196F3D"),  # green → blue → green
  #colors = c('#A6262D', '#A626A6', '#4E2294'),
  na.value = "grey80",
  limits = c(0, 366)
)+
  #scale_x_discrete(labels = variable_order) +
  #scale_y_reverse(breaks = seq(37, 1, by = -2)) +
  scale_x_discrete(labels = var_labels) + 
  labs(x = NULL, y = NULL, fill = "Days till Recovered") +
  facet_wrap(~Property_colored, scales = "free_x", space = "free_x") +
  theme_pubr()+ 
  theme(
  #   #axis.text.x = element_markdown(size = 9, angle = 45, hjust = 1, lineheight = 1.1),
     panel.grid = element_blank(),
     axis.text.x = element_text(color = '#2E5EAA'),
     strip.text = element_markdown(),
     axis.text.y = element_blank())
  #   axis.ticks.length = unit(0.2, "cm"),
  #   axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x  = element_text(size = 8),
  #   axis.text.y  = element_text(size = 8),
  #   legend.text   = element_text(size = 8),
  #   legend.title  = element_text(size = 8),
  #   strip.text    = element_text(size = 8)
  # )
RC

#save
# ggsave(
#   filename = "Draft Paper Graphs/facet_heatmap_functional_newcolors.png",
#   plot = RC,
#   width = 5, #14
#   height = 3, #7
#   dpi = 300
# )
```

### Figure S4

-   Resilience and recovery for middle (10m) and bottom (35) structural variables

```{r}
#middle
#find longest recovery time - thermocline depth
Temp_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_TmpWtr[Tutira_D_WT_p1$Depth == 10]), na.rm = TRUE) 
DO_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_DOconc[Tutira_D_WT_p1$Depth == 10]), na.rm = TRUE) 
chl_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_FlChlr[Tutira_D_WT_p1$Depth == 10]), na.rm = TRUE) 
TD_rec_time   <- min(as.Date(Tutira_ND_WT_p1$first_recovery_thermo.depth), na.rm = TRUE) #2023-09-12

#picking out storm periods
start_time <- min(as.Date(Tutira_ND_WT_p1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_ND_WT_p1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp_10 <- Tutira_D_WT_p1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_temp <- min(df_Temp_10$TmpWtr_lower, na.rm = TRUE)
y_max_temp <- max(df_Temp_10$TmpWtr_upper, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R_10 <- ggplot(df_Temp_10, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'TmpWtr', Depth == 10, Date < Temp_rec_time, Date > end_time), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(10, y_max_temp),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = c(0.7,0.8), axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R_10

############################################ surface Dissolved Oxygen ########################################

df_DO_10 <- Tutira_D_WT_p1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_DO <- min(df_DO_10$DOconc_lower, na.rm = TRUE) 
y_max_DO <- max(df_DO_10$DOconc_upper, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R_10 <- ggplot(df_DO_10, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'DOconc', Depth == 10, Date < DO_rec_time, Date > end_time), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R_10

############################################ surface Chlorophyll-a ########################################

df_chl_10 <- Tutira_D_WT_p1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl_10$FlChlr_lower, na.rm = TRUE) 
y_max_chl <- max(df_chl_10$FlChlr_upper, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R_10 <- ggplot(df_chl_10, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'FlChlr', Depth == 10, Date < chl_rec_time, Date > end_time), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R_10

############################### bottom ##########################
#find longest recovery time - thermocline depth
Temp_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_TmpWtr[Tutira_D_WT_p1$Depth == 35]), na.rm = TRUE) 
DO_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_DOconc[Tutira_D_WT_p1$Depth == 35]), na.rm = TRUE) 
chl_rec_time <- min(as.Date(Tutira_D_WT_p1$first_recovery_FlChlr[Tutira_D_WT_p1$Depth == 35]), na.rm = TRUE) 

#picking out storm periods
start_time <- min(as.Date(Tutira_ND_WT_p1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_ND_WT_p1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp_35 <- Tutira_D_WT_p1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_temp <- min(df_Temp_35$TmpWtr_lower, na.rm = TRUE)
y_max_temp <- max(df_Temp_35$TmpWtr, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R_35 <- ggplot(df_Temp_35, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'TmpWtr', Depth == 35, Date < Temp_rec_time, Date > end_time), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(10, y_max_temp),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R_35

############################################ surface Dissolved Oxygen ########################################

df_DO_35 <- Tutira_D_WT_p1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_DO <- min(df_DO_35$DOconc_lower, na.rm = TRUE) 
y_max_DO <- max(df_DO_35$DOconc_upper, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R_35 <- ggplot(df_DO_35, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'DOconc', Depth == 35, Date < DO_rec_time, Date > end_time), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R_35

############################################ surface Chlorophyll-a ########################################

df_chl_35 <- Tutira_D_WT_p1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl_35$FlChlr_lower, na.rm = TRUE) 
y_max_chl <- max(df_chl_35$FlChlr_upper, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R_35 <- ggplot(df_chl_35, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_D_WT_RR_daily%>% filter(Variable == 'FlChlr', Depth == 35, Date < chl_rec_time, Date > end_time), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R_35

##################### combine and save ###############################
base_plot <-
  ((SWT_R_10 / DO_R_10 / chl_R_10) |
  (SWT_R_35  / DO_R_35 / chl_R_35)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

# ggsave(
#   filename = "Draft Paper Graphs/Recovery_Resilience_SS.png",
#   plot = base_plot,
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

### Figure S5

-   Bhattacharyya coefficient per year for structural and functional variables

```{r}
###################### calculate #########################
#structural
# Function to calculate Bhattacharyya coefficient using histograms
bhattacharyya_hist <- function(x, y, bins = 30) {
  
  # Define common breaks
  brks <- seq(min(c(x, y)), max(c(x, y)), length.out = bins + 1)
  
  # Histogram counts
  h1 <- hist(x, breaks = brks, plot = FALSE)$counts
  h2 <- hist(y, breaks = brks, plot = FALSE)$counts
  
  # Convert to probabilities
  p1 <- h1 / sum(h1)
  p2 <- h2 / sum(h2)
  
  # Bhattacharyya coefficient
  BC <- sum(sqrt(p1 * p2))
  return(BC)
}
Tutira_S6 <- Tutira_D_WT_RR_daily %>%
  filter(Variable %in% c('TmpWtr', 'DOconc','FlChlr')) %>%
  filter(Depth == 1) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

overlap_results <- list()
counter <- 1

variables <- unique(Tutira_S6$Variable)
years <- sort(unique(Tutira_S6$Year))

for (var in variables) {
  var_data <- Tutira_S6 %>% filter(Variable == var)
  
  for (i in 1:(length(years)-1)) {
    for (j in (i+1):length(years)) {
      
      x <- var_data$RL_daily[var_data$Year == years[i]] %>% na.omit()
      y <- var_data$RL_daily[var_data$Year == years[j]] %>% na.omit()
      
      if(length(x) < 5 | length(y) < 5) next  # smaller threshold
      
      bc <- bhattacharyya_hist(x, y, bins = 30)
      
      overlap_results[[counter]] <- data.frame(
        Variable = var,
        Year1 = years[i],
        Year2 = years[j],
        Bhattacharyya = bc
      )
      
      counter <- counter + 1
    }
  }
}

overlap_df <- bind_rows(overlap_results)

#functional
# Function to calculate Bhattacharyya coefficient using histograms
#functional
bhattacharyya_hist <- function(x, y, bins = 30) {
  
  # Define common breaks
  brks <- seq(min(c(x, y)), max(c(x, y)), length.out = bins + 1)
  
  # Histogram counts
  h1 <- hist(x, breaks = brks, plot = FALSE)$counts
  h2 <- hist(y, breaks = brks, plot = FALSE)$counts
  
  # Convert to probabilities
  p1 <- h1 / sum(h1)
  p2 <- h2 / sum(h2)
  
  # Bhattacharyya coefficient
  BC <- sum(sqrt(p1 * p2))
  return(BC)
}

Tutira_F6 <- Tutira_ND_WT_RR_daily %>%
  filter(Variable %in% c('thermo.depth', 'Anoxic_Depth','Depth_max_FlChlr')) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

overlap_results <- list()
counter <- 1

variables <- unique(Tutira_F6$Variable)
years <- sort(unique(Tutira_F6$Year))

for (var in variables) {
  var_data <- Tutira_F6 %>% filter(Variable == var)
  
  for (i in 1:(length(years)-1)) {
    for (j in (i+1):length(years)) {
      
      x <- var_data$RL_daily[var_data$Year == years[i]] %>% na.omit()
      y <- var_data$RL_daily[var_data$Year == years[j]] %>% na.omit()
      
      if(length(x) < 5 | length(y) < 5) next  # smaller threshold
      
      bc <- bhattacharyya_hist(x, y, bins = 30)
      
      overlap_results[[counter]] <- data.frame(
        Variable = var,
        Year1 = years[i],
        Year2 = years[j],
        Bhattacharyya = bc
      )
      
      counter <- counter + 1
    }
  }
}

overlap_df_F <- bind_rows(overlap_results)

######################## graph #######################
#Structural
ggplot(overlap_df, aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  facet_wrap(~ Variable, scales="free") +
  scale_fill_viridis_c(option="magma", direction=-1) +
  labs(
    x="Year 1", y="Year 2",
    fill="Bhattacharyya Coef"
  ) +
  theme_pubr()

#Functional
ggplot(overlap_df_F, aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  facet_wrap(~ Variable, scales="free") +
  scale_fill_viridis_c(option="magma", direction=-1) +
  labs(
    x="Year 1", y="Year 2",
    fill="Bhattacharyya Coef"
  ) +
  theme_pubr()

#structural
B_WT <- ggplot(overlap_df %>% filter(Variable == 'TmpWtr'), aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98), guide = guide_colorbar(
      direction = "horizontal",   # make legend horizontal
      title.position = "top",     # move title above the bar
      barwidth = 10,              # adjust width
      barheight = 0.5             # adjust height
    ))+
  labs(x=NULL, y=NULL,fill="Bhattacharyya Coef") +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Water\nTemperature",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = c(0.75, 0.18), axis.text.x = element_blank())
B_WT
B_DO <- ggplot(overlap_df %>% filter(Variable == 'DOconc'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Dissolved\noxygen",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_DO
B_C <- ggplot(overlap_df %>% filter(Variable == 'FlChlr'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Chlorophyll-a",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = 'none')
B_C
#Functional
B_TD <- ggplot(overlap_df_F %>% filter(Variable == 'thermo.depth'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Thermocline\nDepth",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_TD
B_HD <- ggplot(overlap_df_F %>% filter(Variable == 'Anoxic_Depth'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Hypoxic\nDepth",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_HD
B_CD <- ggplot(overlap_df_F %>% filter(Variable == 'Depth_max_FlChlr'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Depth of\nMaximum\nChlorophyll-a",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none')
B_CD

#combine and save
base_plot <-
  ((B_WT / B_DO / B_C) |
  (B_TD  / B_HD / B_CD)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

# ggsave(
#   filename = "Draft Paper Graphs/Bhattacharyya_Coef.png",
#   plot = combined_plot,
#   width = 12,
#   height = 8,
#   dpi = 300
# )
```

### Figure S6

-   Density curves of structural and functional variables

```{r}
Tutira_D_WT_RR_daily$Year <- factor(Tutira_D_WT_RR_daily$Year, levels = c(2022, 2024, 2025, 2023))
Tutira_D_WT_RR_daily$Variable <- factor(Tutira_D_WT_RR_daily$Variable, levels = c('TmpWtr', 'DOconc', 'FlChlr'))
Tutira_ND_WT_RR_daily$Year <- factor(Tutira_ND_WT_RR_daily$Year, levels = c(2022, 2024, 2025, 2023))
Tutira_ND_WT_RR_daily$Variable <- factor(Tutira_ND_WT_RR_daily$Variable, levels = c('thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr'))

# Combine with labels for axis text
var_labels <- c(
  "TmpWtr" = "Water\ntemperature\n(°C)",
  "DOconc" = "Dissolved\noxygen\n(mg/L)",
  "DOpsat" = "Dissolved\noxygen\n(%)",
  "pH"     = "pH",
  "FlChlr" = "Chlorophyll-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)",
  "Cond"   = "Conductivity\n(µS/cm)",
  "SpCond" = "Specific conductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)"
)

#structural
#WT
D_WT <- ggplot(data = Tutira_D_WT_RR_daily %>% filter(Variable == 'TmpWtr', Depth == 1), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3,       # y position (adjust based on density height)
    label = "Surface Water Temperature",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = c(0.2, 0.5))
D_WT
#DO
D_DO <- ggplot(data = Tutira_D_WT_RR_daily %>% filter(Variable == 'DOconc', Depth == 1), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3.5,       # y position (adjust based on density height)
    label = "Surface Dissolved oxygen",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_DO
#chla
D_chl <- ggplot(data = Tutira_D_WT_RR_daily %>% filter(Variable == 'FlChlr', Depth == 1), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = 'Daily Resilience')+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 11,       # y position (adjust based on density height)
    label = "Surface Chlorophyll-a",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(legend.position = 'none')
D_chl

#functional
#TD
D_TD <- ggplot(data = Tutira_ND_WT_RR_daily %>% filter(Variable == 'thermo.depth'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 1.8,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_TD
#DO
D_H <- ggplot(data = Tutira_ND_WT_RR_daily %>% filter(Variable == 'Anoxic_Depth'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3.5,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_H
#chla
D_mchl <- ggplot(data = Tutira_ND_WT_RR_daily %>% filter(Variable == 'Depth_max_FlChlr'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = 'Daily Resilience')+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 2,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(legend.position = 'none')
D_mchl

#combine and save
base_plot <-
  ((D_WT / D_DO / D_chl) |
  (D_TD  / D_H / D_mchl)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

# ggsave(
#   filename = "Draft Paper Graphs/Density_RL.png",
#   plot = combined_plot,
#   width = 12,
#   height = 8,
#   dpi = 300
# )
```

Figure S7

-   Violin plots of daily resilience for all depths of structural and functional variables

```{r}
#reordering years
Tutira_D_WT_RR_daily$Year <- factor(Tutira_D_WT_RR_daily$Year, levels = c(2022, 2023, 2024, 2025))
Tutira_ND_WT_RR_daily$Year <- factor(Tutira_ND_WT_RR_daily$Year, levels = c(2022, 2023, 2024, 2025))
#Structural
#WT
WTV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable == 'TmpWtr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Water Temperature",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(TmpWtr = "Water Temperature"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
WTV_DRL
#DO
DOV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable %in% 'DOconc', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Dissolved Oxygen",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(DOconc = "Dissolved Oxygen"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
DOV_DRL
#WT
CHV_DRL <- ggplot(Tutira_D_WT_RR_daily%>% filter(Variable == 'FlChlr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(FlChlr = "Chlorophyll-a"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none')
CHV_DRL

#Functional
#thermocline Depth
TDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'thermo.depth', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
TDV_DRL

#Hypoxic Depth
HDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'Anoxic_Depth', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
HDV_DRL

#Depth of chl peak
CDV_DRL <- ggplot(Tutira_ND_WT_RR_daily%>% filter(Variable == 'Depth_max_FlChlr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none')
CDV_DRL

#combine and save
base_plot <-
  ((WTV_DRL / DOV_DRL / CHV_DRL) |
  (TDV_DRL  / HDV_DRL / CDV_DRL)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  )

combined_plot

# ggsave(
#   filename = "Draft Paper Graphs/Recovery_Resilience_alltime_SS.png",
#   plot = combined_plot,
#   width = 12,
#   height = 8,
#   dpi = 300
# )
```

Figure S8

-   Relationship between days till recovery and resistance for all variables

```{r}
#Structural
Tutira_S4 <- Tutira_D_WT_p1%>%
  mutate(Type = case_when(
      Variable == 'TmpWtr' ~ "Physical",
      Variable %in% c('Cond', 'DOconc', 'DOpsat', 'pH', 'SpCond', 'TurbRT') ~ "Chemical",
      Variable %in% c('FlChlr', 'FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    ))%>%
  mutate(Property = 'Structural')
  

#Functional
Tutira_F4 <- Tutira_ND_WT_p1%>%
  mutate(Type = case_when(
      Variable %in% c('Buoyancy', "lake.number", "Meta_Top", "Meta_Bottom", "schmidt.stability", "thermo.depth") ~ "Physical",
      Variable == 'Anoxic_Depth' ~ "Chemical",
      Variable %in% c('Depth_max_FlChlr', 'Depth_max_FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    ))%>%
  mutate(Property = 'Functional')
    
dtr_RS <- ggplot(data = Tutira_S4, aes(x = RS, y = RTB, color = Type, shape = Property))+
  geom_point(size = 2)+
  geom_point(data = Tutira_F4, aes(x = RS, y = RTB, color = Type, shape = Property), size = 2)+
  scale_color_manual(breaks = c('Physical', 'Chemical', 'Biological'), values = c("#A6262D", "#A626A6", "#4E2294"), name = 'Process') +
  scale_shape_manual(breaks = c('Structural', 'Functional'), values = c(16, 17), name = 'Type', labels = c("<span style='color:#452D7A'>Structural</span>","<span style='color:#2E5EAA'>Functional</span>")) +
  xlim(-1,1)+
  labs(x = 'Resistance', y = 'Days till Recovery')+
  #guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_pubr()+
  theme(legend.position = 'right', legend.text = element_markdown())
dtr_RS

# ggsave(
#   filename = "Draft Paper Graphs/Recovery_daystillrecovery_newcolors.png",
#   plot = dtr_RS,
#   width = 6,
#   height = 4,
#   dpi = 300
# )
```

## Tables

### Table S1

-   values from Figure 5

```{r}
Tutira_Sbox <- Tutira_D_WT_p1%>%
  filter(!Variable %in% c("SpCond", "DOpsat", 'Cond','pH'))%>%
  dplyr::select(Variable, Depth, RS) %>%
  group_by(Variable, Depth)%>%
  distinct()

Tutira_summary <- Tutira_Sbox %>%
  group_by(Variable) %>%
  summarise(
    n       = sum(!is.na(RS)),
    mean    = mean(RS, na.rm = TRUE),
    sd      = sd(RS, na.rm = TRUE),
    median  = median(RS, na.rm = TRUE),
    Q1      = quantile(RS, 0.25, na.rm = TRUE),
    Q3      = quantile(RS, 0.75, na.rm = TRUE),
    IQR     = IQR(RS, na.rm = TRUE),
    min     = min(RS, na.rm = TRUE),
    max     = max(RS, na.rm = TRUE),
    .groups = "drop"
  )
```

### Table S2

-   values from Figure 8

```{r}
Tutira_S5 <- Tutira_D_WT_RR_daily%>%
  filter(Depth == 1)%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  distinct() %>%
  filter(Year %in% c(2022,2023,2024,2025))

Tutira_F5 <- Tutira_ND_WT_RR_daily%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  distinct() %>%
  # dplyr::summarise_at(vars(RL_daily),mean,na.rm=TRUE)%>%
  # ungroup()%>%
  filter(Year %in% c(2022,2023,2024,2025))

# 1 m data
Tutira_all <- bind_rows(
  Tutira_S5,
  Tutira_F5
) 

Tutira_summary <- Tutira_all %>%
  group_by(Variable, Year) %>%
  summarise(
    n       = sum(!is.na(RL_daily)),
    mean    = mean(RL_daily, na.rm = TRUE),
    sd      = sd(RL_daily, na.rm = TRUE),
    median  = median(RL_daily, na.rm = TRUE),
    Q1      = quantile(RL_daily, 0.25, na.rm = TRUE),
    Q3      = quantile(RL_daily, 0.75, na.rm = TRUE),
    IQR     = IQR(RL_daily, na.rm = TRUE),
    min     = min(RL_daily, na.rm = TRUE),
    max     = max(RL_daily, na.rm = TRUE),
    .groups = "drop"
  )

# all depths
Tutira_all_Depth <- bind_rows(
  Tutira_D_WT_RR_daily %>% dplyr::select(Variable, Year, Depth, RL_daily),
  Tutira_ND_WT_RR_daily %>% dplyr::select(Variable, Year, RL_daily)
) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

Tutira_summary_Depth <- Tutira_all_Depth %>%
  group_by(Variable, Year, Depth) %>%
  summarise(
    n       = sum(!is.na(RL_daily)),
    mean    = mean(RL_daily, na.rm = TRUE),
    sd      = sd(RL_daily, na.rm = TRUE),
    median  = median(RL_daily, na.rm = TRUE),
    Q1      = quantile(RL_daily, 0.25, na.rm = TRUE),
    Q3      = quantile(RL_daily, 0.75, na.rm = TRUE),
    IQR     = IQR(RL_daily, na.rm = TRUE),
    min     = min(RL_daily, na.rm = TRUE),
    max     = max(RL_daily, na.rm = TRUE),
    .groups = "drop"
  )
```
