---
title: "Tutira + Cyclone Gabrielle Paper Graphs Final"
format: html
editor: visual
---

# Libraries

```{r, message = FALSE}
library(sf)
library(ggplot2)
library(osmdata)
library(rnaturalearth)
library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(scales)
library(ggpubr)
library(rLakeAnalyzer) 
library(LakeMetabolizer)
library(purrr)
library(stringr)
library(cowplot)
library(zoo)
library(slider)
library(ggridges)
library(mgcv)
library(stats)
library(RColorBrewer)
library(rlang)
library(patchwork)
library(usethis)

usethis::use_git()
```

# Data

```{r}
#Structural with Recovery, RS, RL
Tutira_S <- read.csv(file = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/Tutira_D_WT_p1_2023.csv")

Tutira_S1<- Tutira_S
Tutira_S1$Date <- as.Date(Tutira_S1$Date)
Tutira_S1$Month <- months(Tutira_S1$Date)
Tutira_S1$Year <- format(as.POSIXct(Tutira_S1$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_S1$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_S1$Date), "%m-%d")))
Tutira_S1$first_recovery_Cond <- as.POSIXct(Tutira_S1$first_recovery_Cond, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_DOconc <- as.POSIXct(Tutira_S1$first_recovery_DOconc, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_pH <- as.POSIXct(Tutira_S1$first_recovery_pH, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_DOpsat <- as.POSIXct(Tutira_S1$first_recovery_DOpsat, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_SpCond<- as.POSIXct(Tutira_S1$first_recovery_SpCond, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_TmpWtr <- as.POSIXct(Tutira_S1$first_recovery_TmpWtr, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_TurbRT <- as.POSIXct(Tutira_S1$first_recovery_TurbRT, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_FlChlr <- as.POSIXct(Tutira_S1$first_recovery_FlChlr, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery_FlPhyc <- as.POSIXct(Tutira_S1$first_recovery_FlPhyc, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$first_recovery <- as.POSIXct(Tutira_S1$first_recovery, format = '%Y-%m-%d', tz = "UTC")
Tutira_S1$t0 <- as.POSIXct(Tutira_S1$t0, format = '%Y-%m-%d', tz = "UTC")

#Functional with Recovery, RR, RL
Tutira_F <- read.csv(file = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/Tutira_ND_WT_p1_2023.csv")

Tutira_F1<- Tutira_F
Tutira_F1$Date <- as.Date(Tutira_F1$Date)
Tutira_F1$Month <- months(Tutira_F1$Date)
Tutira_F1$Year <- format(as.POSIXct(Tutira_F1$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_F1$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_F1$Date), "%m-%d")))
Tutira_F1$first_recovery_Buoyancy <- as.POSIXct(Tutira_F1$first_recovery_Buoyancy, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_lake.number <- as.POSIXct(Tutira_F1$first_recovery_lake.number, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_Meta_Bottom <- as.POSIXct(Tutira_F1$first_recovery_Meta_Bottom, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_Meta_Top <- as.POSIXct(Tutira_F1$first_recovery_Meta_Top, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_schmidt.stability <- as.POSIXct(Tutira_F1$first_recovery_schmidt.stability, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_thermo.depth <- as.POSIXct(Tutira_F1$first_recovery_thermo.depth, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_Anoxic_Depth <- as.POSIXct(Tutira_F1$first_recovery_Anoxic_Depth, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_Depth_max_FlChlr <- as.POSIXct(Tutira_F1$first_recovery_Depth_max_FlChlr, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery_Depth_max_FlPhyc <- as.POSIXct(Tutira_F1$first_recovery_Depth_max_FlPhyc, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$first_recovery <- as.POSIXct(Tutira_F1$first_recovery, format = '%Y-%m-%d', tz = "UTC")
Tutira_F1$t0 <- as.POSIXct(Tutira_F1$t0, format = '%Y-%m-%d', tz = "UTC")

#Storm identification
Tutira_Storm <- read.csv(file = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/Tutira_storm_including2023.csv") 

Tutira_storm1<- Tutira_Storm
Tutira_storm1$DateTime <- ifelse(
  grepl("^\\d{4}-\\d{2}-\\d{2}$", Tutira_storm1$DateTime),  # if only date, no time
  paste0(Tutira_storm1$DateTime, " 00:00:00"),              # add time
  Tutira_storm1$DateTime                                     # leave as-is
)
Tutira_storm1$Date <- format(as.Date(Tutira_storm1$DateTime, '%Y-%m-%d', tz= "UTC"), format = '%Y-%m-%d')
Tutira_storm1$Date <- as.Date(Tutira_storm1$Date)
Tutira_storm1$Time <- format(as.POSIXct(Tutira_storm1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:%M')
Tutira_storm1$Hour <- format(as.POSIXct(Tutira_storm1$DateTime, '%Y-%m-%d %H:%M:%S',tz="UTC"), format = '%H:00')
Tutira_storm1$DateTime <- as.POSIXct(Tutira_storm1$DateTime, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
Tutira_storm1$Month <- months(Tutira_storm1$Date)
Tutira_storm1$Year <- format(as.POSIXct(Tutira_storm1$Date, '%Y-%m-%d',tz="UTC"), format = '%Y')
Tutira_storm1$datetime <- as.POSIXct(paste(Tutira_storm1$Date, Tutira_storm1$Hour),format='%Y-%m-%d %H:%M',tz = 'UTC')
Tutira_storm1$MD <- as.Date(paste0("2000-", format(as.Date(Tutira_storm1$Date), "%m-%d")))
Tutira_storm1$MDT <- as.POSIXct(paste0("2000-", format(as.POSIXct(Tutira_storm1$DateTime), "%m-%d %H:%M")),format = "%Y-%m-%d %H:%M",tz = "UTC")
Tutira_storm1$first_during_time <- as.POSIXct(Tutira_storm1$first_during_time, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
Tutira_storm1$last_during_time <- as.POSIXct(Tutira_storm1$last_during_time, format = '%Y-%m-%d %H:%M:%S', tz = "UTC")
```

# Graphs

## Map

```{r}
# Get country outline
nz <- ne_countries(scale = "large", country = "New Zealand", returnclass = "sf")

# Separate North and South Islands if needed
# Some datasets have an 'iso_a2' or island field; if not, you can crop using coordinates
# Approximate bounding box for North Island:
#north_island <- st_crop(nz, xmin=172.5, xmax=180, ymin=-41.5, ymax=-32)
both_islands <- st_crop(nz, xmin=166, xmax=180, ymin=-48, ymax=-32)

# -------------------------------
# 2. Function to get lake polygons
# -------------------------------
# Example: get lakes around North Island
#bbox <- st_bbox(c(xmin=172.5, xmax=180, ymin=-41.5, ymax=-32), crs=4326)
bbox <- st_bbox(c(xmin=166, xmax=180, ymin=-48, ymax=-32), crs=4326)

lakes_osm <- opq(bbox = bbox) %>%
  add_osm_feature(key = 'natural', value = 'water') %>%
  osmdata_sf()

# The lakes polygons
lakes <- lakes_osm$osm_multipolygons

# --- Helper function to get a lake polygon reliably (multipolygon OR polygon)
get_lake_polygon <- function(xmin, xmax, ymin, ymax) {
  bbox <- st_bbox(c(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), crs = 4326)
  
  lake_osm <- opq(bbox = bbox) %>%
    add_osm_feature(key = "natural", value = "water") %>%
    osmdata_sf()
  
  if (!is.null(lake_osm$osm_multipolygons) && nrow(lake_osm$osm_multipolygons) > 0) {
    return(st_make_valid(lake_osm$osm_multipolygons))
  } else if (!is.null(lake_osm$osm_polygons) && nrow(lake_osm$osm_polygons) > 0) {
    return(st_make_valid(lake_osm$osm_polygons))
  } else {
    stop("No water polygons found in this bounding box")
  }
}

# --- Scaling + shifting function (fixed to avoid interior artifacts)
scale_shift_sf <- function(lake_sf, scale = 5, offset = c(0,0)) {
  geom <- st_geometry(lake_sf)
  
  # Get centroid
  ctr <- st_centroid(geom)
  
  # Scale around centroid
  scaled_geom <- (geom - ctr) * scale + ctr
  
  # Apply offset
  scaled_geom <- scaled_geom + offset
  
  # Clean geometry
  scaled_geom <- st_make_valid(st_buffer(scaled_geom, 0))
  
  st_sfc(scaled_geom, crs = st_crs(lake_sf))
}

# --- 1. Get Okaro and Tutira using actual bounding boxes
tutira_lake <- get_lake_polygon(176.88, 176.90, -39.23, -39.21)

remove_holes_sfc <- function(sfc) {
  cleaned <- lapply(sfc, function(x) {
    if (inherits(x, "POLYGON")) {
      st_polygon(list(x[[1]]))           # keep only exterior ring
    } else if (inherits(x, "MULTIPOLYGON")) {
      st_multipolygon(lapply(x, function(p) list(p[[1]])))  # only exterior rings
    } else {
      x
    }
  })
  st_sfc(cleaned, crs = st_crs(sfc))
}

# --- 2. Scale + shift to create zoomed versions (no interior artifacts)

tutira_zoom <- scale_shift_sf(tutira_lake, scale = 100, offset = c(1.3, -1.5))
tutira_zoom <- remove_holes_sfc(tutira_zoom)

# --- 3. Centroids for labels
tutira_centroid <- st_centroid(tutira_zoom)

tutira_coords <- st_coordinates(tutira_centroid)

# Shift labels above/below the zoomed lakes
tutira_coords[1, "Y"] <- tutira_coords[1, "Y"] - 1.3 # shift south

tutira_label <- st_sf(label = "Lake Tūtira",
                      geometry = st_sfc(st_point(tutira_coords[1, ]), crs = st_crs(tutira_zoom)))

# --- 4. Connectors: centroid → zoomed centroid

tutira_line <- st_sfc(st_linestring(rbind(
  st_coordinates(st_centroid(tutira_lake)),
  st_coordinates(tutira_centroid)
)), crs = st_crs(tutira_lake))

#add bathymetry to tutuira - later
# Tutira_bathy <- "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/Tutira Original Data Files/Tutira_bathy.txt"
# Tutira_bathy <- read.table(Tutira_bathy, header = TRUE)

# --- 5. Plot
OT_Map <- ggplot() +
  geom_sf(data = both_islands, fill = "lightgreen", color = "black") +
  geom_sf(data = lakes, fill = "lightblue", color = "blue", alpha = 0.5) +   # hydrology background
  geom_sf(data = st_centroid(tutira_lake), color = "black", size = 3) +
  geom_sf(data = tutira_line, color = "black", linetype = "dashed", size = 1) +
  geom_sf(data = tutira_zoom, fill = "blue", color = "black") +
  geom_sf_text(data = tutira_label, aes(label = label), color = "black", size = 6, fontface = "bold") +
  # annotate( #adding in white box to remove the south island
  #   "rect",
  #   xmin = 172.5, xmax = 174.4,   # adjust these
  #   ymin = -42.5, ymax = -40,   # adjust these
  #   fill = "white", color = "white", alpha = 1
  # ) +
  coord_sf(xlim = c(166, 180.2), ylim = c(-48, -34), expand = FALSE) +
  theme_void()
OT_Map

ggsave("C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Random Graphs/NZFSS 2025 Conference Poster/Turira_Map_new.png", OT_Map, width = 4, height = 6, dpi = 300, bg = "white")
```

map from Tadhg code

```{r}
install.packages(c("remotes", "tmap"))
remotes::install_github("limnotrack/aemetools", ref = "dev") # Dev version of aemetools with new lake shape function
remotes::install_github("limnotrack/bathytools")

# Tutira Lake, New Zealand
tutira_lid <- 36981
max_depth <- 42
api_key <- "lernzmp_lakes"

# Get lake shoreline
shoreline <- aemetools::get_lake_shape(id = tutira_lid, api_key = api_key)

library(tmap)
tmap_mode("plot")

tm_shape(shoreline) +
  tm_polygons(fill = "blue", fill_alpha = 0.5)

bathy <- bathytools::estimate_bathymetry(shoreline = shoreline,
                                         max_depth = max_depth,
                                         res = 4) # resolution of the bathymetry raster in meters

tutira_map <- tm_shape(bathy) +
  tm_raster(col.legend = tm_legend(title = "Depth (m)"),
            col.scale = tm_scale_continuous(values = "-brewer.blues")) +
  tm_shape(shoreline) +
  tm_borders(col = "black") +
  tm_layout(legend.outside = TRUE, frame = FALSE)

# Save the map
tmap_save(tutira_map, 
          filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Graphs/tutira_bathy_map.png",
          width = 2400, height = 2400, units = "px")

# Write bathymetry raster to file-
#terra::writeRaster(bathy, "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/tutira_bathy.tif", overwrite = TRUE)

bathy_df <- as.data.frame(bathy, xy = TRUE)
colnames(bathy_df) <- c("x", "y", "depth")

library(terra)
library(sf)

# Convert bathy to SpatRaster
bathy_raster <- rast(bathy)

# Get shoreline bounding box
shore_bbox <- st_bbox(shoreline)

# Assign extent to the raster
ext(bathy_raster) <- c(shore_bbox$xmin, shore_bbox$xmax,
                        shore_bbox$ymin, shore_bbox$ymax)

# Assign CRS (match shoreline)
crs(bathy_raster) <- st_crs(shoreline)$proj4string

# Step 2: Convert to data frame for ggplot
bathy_df <- as.data.frame(bathy_raster, xy = TRUE)
colnames(bathy_df) <- c("x", "y", "depth")
```

combining bathy map with original map

```{r}
remotes::install_github("ropensci/rnaturalearthhires")
library(rnaturalearthhires)
# Get country outline
nz <- ne_countries(scale = "large", country = "New Zealand", returnclass = "sf")

# Separate North and South Islands if needed
# Some datasets have an 'iso_a2' or island field; if not, you can crop using coordinates
# Approximate bounding box for North Island:
#north_island <- st_crop(nz, xmin=172.5, xmax=180, ymin=-41.5, ymax=-32)
both_islands <- st_crop(nz, xmin=166, xmax=180, ymin=-48, ymax=-32)

# -------------------------------
# 2. Function to get lake polygons
# -------------------------------
# Example: get lakes around North Island
#bbox <- st_bbox(c(xmin=172.5, xmax=180, ymin=-41.5, ymax=-32), crs=4326)
bbox <- st_bbox(c(xmin=166, xmax=180, ymin=-48, ymax=-32), crs=4326)

lakes_osm <- opq(bbox = bbox) %>%
  add_osm_feature(key = 'natural', value = 'water') %>%
  osmdata_sf()

# The lakes polygons
lakes <- lakes_osm$osm_multipolygons

# --- Helper function to get a lake polygon reliably (multipolygon OR polygon)
get_lake_polygon <- function(xmin, xmax, ymin, ymax) {
  bbox <- st_bbox(c(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), crs = 4326)
  
  lake_osm <- opq(bbox = bbox) %>%
    add_osm_feature(key = "natural", value = "water") %>%
    osmdata_sf()
  
  if (!is.null(lake_osm$osm_multipolygons) && nrow(lake_osm$osm_multipolygons) > 0) {
    return(st_make_valid(lake_osm$osm_multipolygons))
  } else if (!is.null(lake_osm$osm_polygons) && nrow(lake_osm$osm_polygons) > 0) {
    return(st_make_valid(lake_osm$osm_polygons))
  } else {
    stop("No water polygons found in this bounding box")
  }
}

# --- Scaling + shifting function (fixed to avoid interior artifacts)
scale_shift_sf <- function(lake_sf, scale = 5, offset = c(0,0)) {
  geom <- st_geometry(lake_sf)
  
  # Get centroid
  ctr <- st_centroid(geom)
  
  # Scale around centroid
  scaled_geom <- (geom - ctr) * scale + ctr
  
  # Apply offset
  scaled_geom <- scaled_geom + offset
  
  # Clean geometry
  scaled_geom <- st_make_valid(st_buffer(scaled_geom, 0))
  
  st_sfc(scaled_geom, crs = st_crs(lake_sf))
}

# --- 1. Get Okaro and Tutira using actual bounding boxes
tutira_lake <- get_lake_polygon(176.88, 176.90, -39.23, -39.21)

remove_holes_sfc <- function(sfc) {
  cleaned <- lapply(sfc, function(x) {
    if (inherits(x, "POLYGON")) {
      st_polygon(list(x[[1]]))           # keep only exterior ring
    } else if (inherits(x, "MULTIPOLYGON")) {
      st_multipolygon(lapply(x, function(p) list(p[[1]])))  # only exterior rings
    } else {
      x
    }
  })
  st_sfc(cleaned, crs = st_crs(sfc))
}

# --- 2. Scale + shift to create zoomed versions (no interior artifacts)

tutira_zoom <- scale_shift_sf(tutira_lake, scale = 100, offset = c(1.3, -1.5))
tutira_zoom <- remove_holes_sfc(tutira_zoom)

# --- 3. Centroids for labels
tutira_centroid <- st_centroid(tutira_zoom)

tutira_coords <- st_coordinates(tutira_centroid)

# Shift labels above/below the zoomed lakes
tutira_coords[1, "Y"] <- tutira_coords[1, "Y"] - 1.3 # shift south

tutira_label <- st_sf(label = "Lake Tūtira",
                      geometry = st_sfc(st_point(tutira_coords[1, ]), crs = st_crs(tutira_zoom)))

# --- 4. Connectors: centroid → zoomed centroid

tutira_line <- st_sfc(st_linestring(rbind(
  st_coordinates(st_centroid(tutira_lake)),
  st_coordinates(tutira_centroid)
)), crs = st_crs(tutira_lake))

#add bathymetry to tutuira - later
# Tutira_bathy <- "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Data/Tutira Original Data Files/Tutira_bathy.txt"
# Tutira_bathy <- read.table(Tutira_bathy, header = TRUE)

# --- 5. Plot
OT_Map <- ggplot() +
  # Background islands
  geom_sf(data = both_islands, fill = "lightgreen", color = "black") +
  # Other lakes
  geom_sf(data = lakes, fill = "lightblue", color = "blue", alpha = 0.5) +
  # Bathymetry raster for Tutira
  geom_raster(data = bathy_df, aes(x = x, y = y, fill = depth)) +
  scale_fill_gradientn(
    colors = rev(RColorBrewer::brewer.pal(9, "Blues")),
    name = "Depth (m)"
  ) +
  # Tutira shoreline outline
  geom_sf(data = shoreline, fill = NA, color = "black", size = 0.8) +
  # Other map features
  geom_sf(data = st_centroid(tutira_lake), color = "black", size = 3) +
  geom_sf(data = tutira_line, color = "black", linetype = "dashed", size = 1) +
  geom_sf_text(data = tutira_label, aes(label = label), color = "black", size = 6, fontface = "bold") +
  coord_sf(xlim = c(166, 180.2), ylim = c(-48, -34), expand = FALSE) +
  theme_void()

OT_Map

ggsave("C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Random Graphs/NZFSS 2025 Conference Poster/Turira_Map_bathy.png", OT_Map, width = 4, height = 6, dpi = 300, bg = "white")
```

Importing image

```{r}
library(ggplot2)
library(png)
library(grid)

# Load the PNG image
bathy_img <- png::readPNG("C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Graphs/Tutira_Map_PP.png")

# Convert to a grid object for ggplot
bathy_grob <- grid::rasterGrob(bathy_img, interpolate = TRUE)

# Shift labels above/below the zoomed lakes
tutira_coords[1, "Y"] <- tutira_coords[1, "Y"] - 3 # shift south

tutira_label <- st_sf(label = "Lake Tūtira",
                      geometry = st_sfc(st_point(tutira_coords[1, ]), crs = st_crs(tutira_zoom)))

# --- 4. Connectors: centroid → zoomed centroid

tutira_line <- st_sfc(st_linestring(rbind(
  st_coordinates(st_centroid(tutira_lake)),
  st_coordinates(tutira_centroid)
)), crs = st_crs(tutira_lake))

OT_Map <- ggplot() +
  # Main NZ map
  geom_sf(data = both_islands, fill = "lightgreen", color = "black") +
  #geom_sf(data = lakes, fill = "lightblue", color = "blue", alpha = 0.5) +
  
  # Tutira bathymetry inset
  # annotation_custom(
  #   grob = bathy_grob,
  #   xmin = 176, xmax = 180.5,  # approximate longitude range for inset
  #   ymin = -47, ymax = -40  # approximate latitude range for inset
  # ) +
  
  # Tutira shoreline outline (optional, for overlay)
  #geom_sf(data = shoreline, fill = NA, color = "black", size = 0.8) +
  
  # Other map features
  geom_sf(data = st_centroid(tutira_lake), color = "black", size = 3) +
  #geom_sf(data = tutira_line, color = "black", linetype = "dashed", size = 1) +
  #geom_sf_text(data = tutira_label, aes(label = label), color = "black", size = 6, fontface = "bold") +
  
  coord_sf(xlim = c(166, 181), ylim = c(-48, -34), expand = FALSE) +
  theme_void()

OT_Map

ggsave("C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Graphs/New_Zealand_Outline.png", OT_Map, width = 4, height = 6, dpi = 300, bg = "white")
```

World Map

```{r}
library(rnaturalearthdata)
# Get world data
world <- ne_countries(scale = "medium", returnclass = "sf")

# Create a flag for New Zealand
world <- world %>%
  mutate(highlight = ifelse(admin == "New Zealand", "NZ", "Other"))

# Plot
# Split data
nz <- world %>% filter(admin == "New Zealand")
rest <- world %>% filter(admin != "New Zealand")

WM <- ggplot() +
  # Other countries
  geom_sf(data = rest, fill = "grey80", color = "black", size = 0.1) +
  
  # New Zealand (highlighted)
  geom_sf(data = nz, fill = "lightgreen", color = "darkgreen", size = 0.3) +
  
  theme_pubr() +
  theme(
    legend.position = "none"
  )
WM
ggsave("C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Graphs/World_Map.png", WM, width = 4, height = 6, dpi = 300, bg = "white")
```

Map from Jamie's files

```{r}
library(sf)

bathy_sf <- st_read("C:/Users/mah92/Downloads/NIWA_Lake_Tutira_shapefile/Tut_bathLines.shp")

edge <- bathy_sf %>% filter(Comment == "Lake Edge")
contours <- bathy_sf %>% filter(is.na(Comment))

ggplot() +
  geom_sf(data = contours, aes(color = Depth), size = 0.6) +
  geom_sf(data = edge, color = "black", size = 1.2) +
  scale_color_viridis_c(direction = -1) +
  theme_minimal()

#filling in circles
# Separate edge and contours
# Separate edge and contours
edge <- bathy_sf %>% filter(Comment == "Lake Edge")
contours <- bathy_sf %>% filter(is.na(Comment))

# Lake polygon
lake_poly <- st_union(edge)

# Sort contours from deepest to shallowest
contours <- contours %>% arrange(desc(Depth))

# Initialize list to store buffered polygons
poly_list <- list()

# Loop over each contour line to create a thick “band”
for (i in seq_len(nrow(contours))) {
  cont <- contours[i, ]
  
  # Buffer slightly to make a polygon
  poly_geom <- st_buffer(cont, dist = 10)  # adjust 10 as needed
  
  # Wrap geometry in st_sfc to create proper geometry column
  poly_sfc <- st_sfc(poly_geom$geometry, crs = st_crs(cont))
  
  # Create sf object
  poly_sf <- st_sf(Depth = cont$Depth, geometry = poly_sfc)
  
  # Store
  poly_list[[i]] <- poly_sf
}

# Combine all polygons
contours_poly <- do.call(rbind, poly_list)

# Clip polygons to lake
contours_poly <- st_intersection(contours_poly, lake_poly)

# Plot
ggplot() +
  geom_sf(data = contours_poly, aes(fill = Depth), color = NA) +
  geom_sf(data = edge, color = "black", size = 1) +
  geom_sf(data = contours, aes(color = Depth), size = 0.6) +
  scale_fill_viridis_c(direction = -1) +
  scale_color_viridis_c(direction = -1) +
  theme_minimal()
```

## Storm Identification

```{r}
# pull start/end into simple scalars
Tutira_first_time <- Tutira_storm1$first_during_time
Tutira_last_time  <- Tutira_storm1$last_during_time

#barometric pressure
BP <- ggplot(data = Tutira_storm1, aes(x = datetime, y = PrBaro))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  #geom_line(color = "#7B9E4C")+
  geom_line(color = "black")+
  ylab('Barometric Pressure\n(hPa)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  #geom_hline(yintercept = unique(Tutira_storm$PrBaro_10th), linetype = 'solid', color = 'black') +
  #scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  scale_x_datetime(breaks = "1 week", labels = NULL) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
BP

#wind speed
WS<-ggplot(data = Tutira_storm1, aes(x = datetime, y = WndSpd))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  geom_line(color = "black")+
  ylab('Wind Speed\n(m/s)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  #geom_hline(yintercept = unique(Tutira_storm$WS_90th), linetype = 'solid', color = 'black') +
  #scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  scale_x_datetime(breaks = "1 week", labels = NULL) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
WS

#rainfall
R<-ggplot(data = Tutira_storm1, aes(x = datetime, y = PpRain))+
  geom_rect(aes(xmin = Tutira_first_time, xmax = Tutira_last_time, ymin = -Inf, ymax = Inf),
            fill = "#BDBDBD", alpha = 0.2) +
  geom_col(color = "black") +
  ylab('Precipitation\n(mm)')+
  xlab(NULL)+
  geom_vline(xintercept = as.numeric(Tutira_first_time), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.numeric(Tutira_last_time), linetype = "dashed", color = "black") +
  scale_x_datetime(breaks = "1 week", labels = date_format("%b %d")) +
  theme_pubr()
  # theme(
  #   axis.title.x = element_text(face = "bold"),
  #   axis.title.y = element_text(face = "bold"),
  #   axis.text.x  = element_text(face = "bold"),
  #   axis.text.y  = element_text(face = "bold")
  # )
R

Tutira_Cyclone_patch <-
  (BP / WS / R) +
  plot_layout(heights = c(1, 1, 1)) &
  theme(
    plot.margin = margin(0, 0, 0, 0),
    panel.spacing = unit(0, "lines")
  )&
  plot_annotation(
     tag_levels = "A")#&
  # theme(
  #   plot.tag.position = c(0.13, 0.95)#,
  #   #plot.tag = element_text(face = "bold")
  # )
Tutira_Cyclone_patch

#saving
ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Tutira_Cyclone_Gabrielle.png",
  plot = Tutira_Cyclone_patch,
  width = 5, #14
  height = 6, #7
  dpi = 300
)
```

## Thermocline Depth

```{r}
Tutira_TD <- Tutira_F1 %>%
  dplyr::select(MD, thermo.depth_mean) %>%
  group_by(MD)%>%
  dplyr::summarise_at(vars(thermo.depth_mean),mean,na.rm=TRUE)%>%
  ungroup() %>%
  mutate(TD_avg = mean(thermo.depth_mean))

TD_avg_value <- Tutira_TD %>%
  filter(thermo.depth_mean <= 15) %>%
  mutate(TD_avg = mean(thermo.depth_mean))  # numeric value

TD <- ggplot(data = Tutira_TD, aes(x = MD, y = thermo.depth_mean))+
  geom_point()+
  scale_y_reverse(limits = c(0,40), breaks = seq(0, 40, 5))+
  geom_hline(yintercept = TD_avg_value$TD_avg)+
  labs(x = NULL, y = 'Avg Thermocline Depth (m)') +
  scale_x_datetime(breaks = "1 month", labels = date_format("%b")) +
  theme_pubr()
TD

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Tutira_AvgTD.png",
  plot = TD,
  width = 5, #14
  height = 3, #7
  dpi = 300
)
```

## Resistance

### Structural

```{r}
# #editing names and orders
# var_levels <- c(
#   "TmpWtr", "Cond", "DOconc", "DOpsat", "pH", "TurbRT",
#   "FlChlr", "FlPhyc"
# )
# 
# var_labels <- c(
#   "TmpWtr"  = "Water\ntemperature\n(°C)",
#   "DOconc"  = "Dissolved\noxygen\n(mg/L)",
#   "DOpsat"  = "Dissolved\noxygen\n(%)",
#   "pH"      = "pH",
#   "FlChlr"  = "Chlorophyll-a\n(RFU)",
#   "FlPhyc"  = "Phycocyanin\n(RFU)",
#   "Cond"    = "Conductivity\n(µS/cm)",
#   "TurbRT"  = "Turbidity\n(NTU)"
# )
# 
# #graphing - boxplot with one color
# RS_Box <- Tutira_S1%>%
#   filter(Variable != "SpCond")%>%
#   mutate(
#     Variable = factor(
#       Variable,
#       levels = var_levels,
#       labels = var_labels[var_levels]
#     )
#   )%>%
#   ggplot(aes(x = Variable, y = RS))+
#   geom_boxplot(fill = '#389480')+
#   scale_y_continuous(limits = c(-1, 1))+
#   labs(y = "Resistance", x = NULL)+
#   theme_pubr()
# RS_Box
# 
# ggsave(
#   filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/RS_S_Box.png",
#   plot = RS_Box,
#   width = 9, #14
#   height = 4, #7
#   dpi = 300
# )

#colors depending on physical, chemical, or biological
# variable levels
var_levels <- c(
  "TmpWtr", "Cond", "DOconc", "pH", "TurbRT",
  "FlChlr", "FlPhyc"
)
# Define variable types
var_type <- c(
  "TmpWtr" = "Physical",
  "DOconc" = "Chemical",
  "DOpsat" = "Chemical",
  "pH"     = "Chemical",
  "FlChlr" = "Biological",
  "FlPhyc" = "Biological",
  "Cond"   = "Chemical",
  "SpCond" = "Chemical",
  "TurbRT" = "Chemical"
)

# Combine with labels for axis text
var_labels <- c(
  "TmpWtr" = "Water\ntemperature\n(°C)",
  "DOconc" = "Dissolved\noxygen\n(mg/L)",
  "DOpsat" = "Dissolved\noxygen\n(%)",
  "pH"     = "pH",
  "FlChlr" = "Chlorophyll-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)",
  "Cond"   = "Conductivity\n(µS/cm)",
  "SpCond" = "Specific conductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)"
)

# Define colors for each type
# type_colors <- c(
#   "Physical" = "#66C2C7",
#   "Chemical" = "#7B9E4C",
#   "Biological" = "#196F3D"
# )

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)

#graphing - boxplot with one color
RS_Box <- Tutira_S1%>%
  filter(!Variable %in% c("SpCond", "DOpsat", 'Cond','pH'))%>%
  mutate(
    Type = factor(var_type[as.character(Variable)], levels = c("Physical", "Chemical", "Biological")),
    Variable = factor(
      Variable,
      levels = var_levels,
      labels = var_labels[var_levels])
  )%>%
  ggplot(aes(x = Variable, y = RS, fill = Type))+
  geom_boxplot()+
  scale_fill_manual(values = type_colors)+
  scale_y_continuous(limits = c(-1, 1))+
  labs(y = "Resistance", x = NULL, fill = "")+
  theme_pubr()+
  theme(axis.text.x = element_text(color = '#452D7A'))
RS_Box

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/RS_S_Box_colors_updated_colors.png",
  plot = RS_Box,
  width = 8, #14
  height = 4, #7
  dpi = 300
)
```

#### Stats - edit

```{r}
Tutira_Sbox <- Tutira_S1%>%
  filter(!Variable %in% c("SpCond", "DOpsat", 'Cond','pH'))%>%
  dplyr::select( Variable, Depth, RS)%>%
  group_by(Variable, Depth)%>%
  dplyr::summarise_at(vars(RS),mean,na.rm=TRUE)%>%
  ungroup()
  #filter(Year %in% c(2022,2023,2024,2025))

Tutira_summary <- Tutira_Sbox %>%
  group_by(Variable) %>%
  summarise(
    n       = sum(!is.na(RS)),
    mean    = mean(RS, na.rm = TRUE),
    sd      = sd(RS, na.rm = TRUE),
    median  = median(RS, na.rm = TRUE),
    Q1      = quantile(RS, 0.25, na.rm = TRUE),
    Q3      = quantile(RS, 0.75, na.rm = TRUE),
    IQR     = IQR(RS, na.rm = TRUE),
    min     = min(RS, na.rm = TRUE),
    max     = max(RS, na.rm = TRUE),
    .groups = "drop"
  )

```

### Functional

```{r}
#colors depending on physical, chemical, or biological
#define order of variables
var_levels <- c(
  #"Buoyancy", "lake.number", "Meta_Top", "Meta_Bottom", 
  "schmidt.stability", "thermo.depth", "Anoxic_Depth", "Depth_max_FlChlr", "Depth_max_FlPhyc"
)

# Define variable types
var_type <- c(
  #"Buoyancy" = "Physical",
  #"lake.number" = "Physical",
  #"Meta_Top" = "Physical",
  #"Meta_Bottom" = "Physical",
  "schmidt.stability" = "Physical",
  "thermo.depth" = "Physical",
  "Anoxic_Depth" = "Chemical",
  "Depth_max_FlChlr" = "Biological",
  "Depth_max_FlPhyc" = "Biological"
)

# Combine with labels for axis text
var_labels <- c(
  # Physical
  #"Buoyancy" = "Buoyancy\nFrequency\n(s⁻¹)",
  #"Meta_Bottom" = "Metalimnion\nBottom\n(m)",
  #"Meta_Top" = "Metalimnion\nTop (m)",
  #"lake.number" = "Lake\nNumber",
  "schmidt.stability" = "Schmidt\nStability\n(J/m²)",
  "thermo.depth" = "Thermocline\nDepth (m)",
  # Chemical
  "Anoxic_Depth" = "Hypoxic\nDepth (m)",
  # Biological
  "Depth_max_FlChlr" = "Peak\nChl-a\nDepth (m)",
  "Depth_max_FlPhyc" = "Peak\nPhycocyanin\nDepth (m)"
)

# Define colors for each type
# type_colors <- c(
#   "Physical" = "#66C2C7",
#   "Chemical" = "#7B9E4C",
#   "Biological" = "#196F3D"
# )

type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)

#graphing - boxplot with one color
RS_heatmap <- Tutira_F1%>%
  filter(Variable %in% c('schmidt.stability', 'thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr', 'Depth_max_FlPhyc'))%>%
  mutate(
    Type = factor(var_type[as.character(Variable)], levels = c("Physical", "Chemical", "Biological")),
    Variable = factor(
      Variable,
      levels = var_levels,
      labels = var_labels[var_levels])
  )%>%
  ggplot(aes(x = Variable, y = RS, color = Type))+
  geom_point()+
  scale_color_manual(values = type_colors)+
  scale_y_continuous(limits = c(-1, 1))+
  labs(y = "Resistance", x = NULL, color = "")+
  theme_pubr()+
  theme(axis.text.x = element_text(color = '#2E5EAA'))
RS_heatmap

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/RS_F_point_colors_labels.png",
  plot = RS_heatmap,
  width = 9, #14
  height = 4, #7
  dpi = 300
)
```

## Recovery - Daily Resilience

```{r}
Tutira_S1$t0 <- as.Date(Tutira_S1$t0)
Tutira_F1$t0 <- as.Date(Tutira_F1$t0)
#structural
vars <- c("TmpWtr", "DOconc", "DOpsat", "pH", "FlChlr", "FlPhyc", "Cond", "SpCond", "TurbRT")

# daily rate of resilience for each variable and depth
Tutira_S2 <- Tutira_S1%>%
  filter(Date >= last_during_time &
             Date <= first_recovery + hours(72)) %>%     # recovery window
  dplyr::select(Date, Depth, all_of(vars), all_of(paste0(vars, "_mean")), first_recovery) %>%
  pivot_longer(
    cols = all_of(vars),
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  mutate(
    MeanValue = case_when(
      Variable == "TmpWtr"  ~ TmpWtr_mean,
      Variable == "DOconc"  ~ DOconc_mean,
      Variable == "DOpsat"  ~ DOpsat_mean,
      Variable == "pH"      ~ pH_mean,
      Variable == "FlChlr"  ~ FlChlr_mean,
      Variable == "FlPhyc"  ~ FlPhyc_mean,
      Variable == "Cond"    ~ Cond_mean,
      Variable == "SpCond"  ~ SpCond_mean,
      Variable == "TurbRT"  ~ TurbRT_mean),
      Dd = Value - MeanValue        # daily deviation
      ) %>%
      merge(Tutira_S1, by = c("Variable", 'Date', all_of(paste0(vars, "_mean")), 'first_recovery', 'Depth'))%>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )

#functional
vars <- c("Buoyancy", "lake.number", "Meta_Top", "Meta_Bottom", "schmidt.stability", "thermo.depth", "Anoxic_Depth", "Depth_max_FlChlr", "Depth_max_FlPhyc")

# daily rate of resilience for each variable and depth
Tutira_F2 <- Tutira_F1%>%
  filter(Date >= last_during_time &
             Date <= first_recovery + hours(72)) %>%     # recovery window
  dplyr::select(Date, all_of(vars), all_of(paste0(vars, "_mean")), first_recovery) %>%
  pivot_longer(
    cols = all_of(vars),
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  mutate(
    MeanValue = case_when(
      Variable == "Buoyancy"  ~ Buoyancy_mean,
      Variable == "lake.number"  ~ lake.number_mean,
      Variable == "Meta_Top"  ~ Meta_Top_mean,
      Variable == "Meta_Bottom"      ~ Meta_Bottom_mean,
      Variable == "schmidt.stability"  ~ schmidt.stability_mean,
      Variable == "thermo.depth"  ~ thermo.depth_mean,
      Variable == "Anoxic_Depth"    ~ Anoxic_Depth_mean,
      Variable == "Depth_max_FlChlr"  ~ Depth_max_FlChlr_mean,
      Variable == "Depth_max_FlPhyc"  ~ Depth_max_FlPhyc_mean),
      Dd = Value - MeanValue        # daily deviation
      ) %>%
      merge(Tutira_F1, by = c("Variable", 'Date', all_of(paste0(vars, "_mean")), 'first_recovery'))%>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )
```

### Structural vs function daily Resilience

-   Structural: Water Temperature, dissolved Oxygen, Chlorophyll

-   Functional: Thermocline Depth, Hypoxic Depth, Depth of peak

```{r}
#find longest recovery time - thermocline depth
TD_rec_time   <- min(as.Date(Tutira_F1$first_recovery_thermo.depth), na.rm = TRUE) #2023-09-12
Temp_rec_time <- min(as.Date(Tutira_S1$first_recovery_TmpWtr[Tutira_S1$Depth == 1]), na.rm = TRUE) #2023-04-21
#Turb_rec_time <- min(as.Date(Tutira_S1$first_recovery_TurbRT[Tutira_S1$Depth == 1]), na.rm = TRUE)
DO_rec_time <- min(as.Date(Tutira_S1$first_recovery_DOconc[Tutira_S1$Depth == 1]), na.rm = TRUE) #2023-03-21
chl_rec_time <- min(as.Date(Tutira_S1$first_recovery_FlChlr[Tutira_S1$Depth == 1]), na.rm = TRUE) #2023-02-17
Hyp_rec_time <- min(as.Date(Tutira_F1$first_recovery_Anoxic_Depth), na.rm = TRUE) #2023-02-22
DC_rec_time <- min(as.Date(Tutira_F1$first_recovery_Depth_max_FlChlr), na.rm = TRUE) #2023-08-29

#picking out storm periods
start_time <- min(as.Date(Tutira_F1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_F1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_temp <- 10 #min(df_Temp$TmpWtr, na.rm = TRUE)
y_max_temp <- max(df_Temp$TmpWtr, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R <- ggplot(df_Temp, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'TmpWtr', Depth == 1), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(10, y_max_temp),
  breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = c(0.7,0.8), axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R

############################################ surface Dissolved Oxygen ########################################

df_DO <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_DO <- 4 #min(df_DO$DOconc, na.rm = TRUE) 
y_max_DO <- max(df_DO$DOconc, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R <- ggplot(df_DO, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'DOconc', Depth == 1), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R

############################################ surface Chlorophyll-a ########################################

df_chl <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl$FlChlr, na.rm = TRUE) 
y_max_chl <- 3.4 #max(df_chl$FlChlr, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R <- ggplot(df_chl, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'FlChlr', Depth == 1), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R

############################################ Thermocline Depth ########################################

#for secondary axis
# ranges
y1_min <- min(Tutira_F1$thermo.depth, na.rm = TRUE)
y1_max <- max(Tutira_F1$thermo.depth, na.rm = TRUE)

y2_min <- -1
y2_max <- 1

# scale RL_Daily to thermo.depth range
scale_fun_TD <- function(x) {
  y1_max - (x - y2_min) / (y2_max - y2_min) * (y1_max - y1_min)
}

inv_scale_fun_TD <- function(x) {
  y2_min + (y1_max - x) / (y1_max - y1_min) * (y2_max - y2_min)
}

#limiting time on graph
df_TD <- Tutira_F1 %>%
  filter(Date >= x_min & Date <= x_max)

#setting y limits
y_min_TD <- min(df_TD$thermo.depth, na.rm = TRUE)
y_max_TD <- max(df_TD$thermo.depth, na.rm = TRUE)

#creating boxes for storm and recovery
storm_window_TD <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_TD, ymax = y_max_TD)
recovery_window_TD <- data.frame(xmin = end_time, xmax = TD_rec_time, ymin = y_min_TD, ymax = y_max_TD)

#graph
TD_R <- ggplot(df_TD, aes(x = Date, y = thermo.depth)) +
  geom_rect(data = storm_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  #geom_rect(data = recovery_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            #inherit.aes = FALSE, fill = '#27AE15', alpha = 0.2) +
  geom_rect(data = recovery_window_TD, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = thermo.depth_lower, ymax = thermo.depth_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = thermo.depth_mean), colour = 'black', size = 1) +
  geom_line(color = '#7B9E4C', size = 1) +
  geom_line(data = Tutira_F2%>% filter(Variable == 'thermo.depth'), aes(x = Date, y = scale_fun_TD(RL_daily)), color = '#FF7B9C', size = 1, linetype = 'dashed')+
  geom_vline(xintercept = c(start_time, end_time, TD_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  #scale_y_reverse(name = 'Thermocline Depth\n(m)', sec.axis = sec_axis(~inv_scale_fun(.), name = "RL Daily")) +
  scale_y_reverse(
  name = 'Thermocline Depth\n(m)',
  limits = c(39, 0),
  sec.axis = sec_axis(
    ~inv_scale_fun_TD(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  labs(x = NULL) +
  theme_pubr()+
  theme(axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
  # theme(axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x   = element_text(size = 8),
  #   axis.text.y   = element_text(size = 8))

TD_R

############################################ Hypoxic Depth ########################################

df_Hyp <- Tutira_F1 %>%
  filter(Date >= x_min & Date <= x_max)

y_min_Hyp <- min(df_Hyp$Anoxic_Depth, na.rm = TRUE) 
y_max_Hyp <- max(df_Hyp$Anoxic_Depth, na.rm = TRUE)

scale_fun_Hyp <- function(x) {
  y_max_Hyp - (x - y2_min) / (y2_max - y2_min) * (y_max_Hyp - y_min_Hyp)
}

inv_scale_fun_Hyp <- function(x) {
  y2_min + (y_max_Hyp - x) / (y_max_Hyp - y_min_Hyp) * (y2_max - y2_min)
}

storm_window_Hyp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_Hyp, ymax = y_max_Hyp)
recovery_window_Hyp <- data.frame(xmin = end_time, xmax = Hyp_rec_time, ymin = y_min_Hyp, ymax = y_max_Hyp)

Hyp_R <- ggplot(df_Hyp, aes(x = Date, y = Anoxic_Depth)) +
  geom_rect(data = storm_window_Hyp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_Hyp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = Anoxic_Depth_lower, ymax = Anoxic_Depth_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = Anoxic_Depth_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = Anoxic_Depth, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Hyp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_F2%>% filter(Variable == 'Anoxic_Depth'), aes(x = Date, y = scale_fun_Hyp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_reverse(
  name = 'Hypoxic Depth\n(m)',
  limits = c(39, y_min_Hyp),
  sec.axis = sec_axis(
    ~inv_scale_fun_Hyp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Hypoxic Depth\n(m)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
         axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
Hyp_R

############################################ Depth of maximum Chlorophyll-a ########################################

df_DC <- Tutira_F1 %>%
  filter(Date >= x_min & Date <= x_max)

y_min_DC <- min(df_DC$Depth_max_FlChlr, na.rm = TRUE) 
y_max_DC <- max(df_DC$Depth_max_FlChlr, na.rm = TRUE)

scale_fun_DC <- function(x) {
  y_max_DC - (x - y2_min) / (y2_max - y2_min) * (y_max_DC - y_min_DC)
}

inv_scale_fun_DC <- function(x) {
  y2_min + (y_max_DC - x) / (y_max_DC - y_min_DC) * (y2_max - y2_min)
}

storm_window_DC <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DC, ymax = y_max_DC)
recovery_window_DC <- data.frame(xmin = end_time, xmax = DC_rec_time, ymin = y_min_DC, ymax = y_max_DC)

DC_R <- ggplot(df_DC, aes(x = Date, y = Depth_max_FlChlr)) +
  geom_rect(data = storm_window_DC, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DC, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = Depth_max_FlChlr_lower, ymax = Depth_max_FlChlr_upper), fill = '#909497', alpha = 0.5) +
  geom_line(aes(y = Depth_max_FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = Depth_max_FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DC_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_F2%>% filter(Variable == 'Depth_max_FlChlr'), aes(x = Date, y = scale_fun_DC(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_reverse(
  name = 'Depth of Maximum\nChlorophyll-a (m)',
  limits = c(y_max_DC, y_min_DC),
  sec.axis = sec_axis(
    ~inv_scale_fun_DC(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Depth of Maximum\nChlorophyll-a (m)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
         axis.title.y = element_text(color = '#2E5EAA'), axis.title.y.right  = element_text(color = '#2E5EAA'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DC_R

#combine and save
base_plot <-
  ((SWT_R / DO_R / chl_R) |
  (TD_R  / Hyp_R / DC_R)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Resilience_6_labels_newcolors_dg.png",
  plot = combined_plot,
  width = 10,
  height = 6,
  dpi = 300
)
```

Surface for hui

```{r}
#find longest recovery time - thermocline depth
#TD_rec_time   <- min(as.Date(Tutira_F1$first_recovery_thermo.depth), na.rm = TRUE) #2023-09-12
Temp_rec_time <- min(as.Date(Tutira_S1$first_recovery_TmpWtr[Tutira_S1$Depth == 1]), na.rm = TRUE) #2023-04-21
Turb_rec_time <- min(as.Date(Tutira_S1$first_recovery_TurbRT[Tutira_S1$Depth == 1]), na.rm = TRUE)
DO_rec_time <- min(as.Date(Tutira_S1$first_recovery_DOconc[Tutira_S1$Depth == 1]), na.rm = TRUE) #2023-03-21

#picking out storm periods
start_time <- min(as.Date(Tutira_F1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_F1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- Turb_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_temp <- 10 #min(df_Temp$TmpWtr, na.rm = TRUE)
y_max_temp <- max(df_Temp$TmpWtr, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R <- ggplot(df_Temp, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  #geom_line(data = Tutira_S2%>% filter(Variable == 'TmpWtr', Depth == 1), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C")) +
  scale_y_continuous(
  limits = c(10, y_max_temp),
  breaks = seq(10, 25, by = 5),
  # sec.axis = sec_axis(
  #   ~inv_scale_fun_temp(.),
  #   name   = "Daily Resilience",
  #   breaks = seq(-1, 1, by = 0.5),
  #   labels = scales::number_format(accuracy = 0.1)
  # )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = c(0.7,0.8), axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R

############################################ surface Dissolved Oxygen ########################################

df_DO <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_DO <- 4 #min(df_DO$DOconc, na.rm = TRUE) 
y_max_DO <- max(df_DO$DOconc, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R <- ggplot(df_DO, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  #geom_line(data = Tutira_S2%>% filter(Variable == 'DOconc', Depth == 1), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C")) +
  scale_y_continuous(
  limits = c(y_min_DO, y_max_DO)
  #breaks = seq(10, 25, by = 5),
  # sec.axis = sec_axis(
  #   ~inv_scale_fun_DO(.),
  #   name   = "Daily Resilience",
  #   breaks = seq(-1, 1, by = 0.5),
  #   labels = scales::number_format(accuracy = 0.1)
  # )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R

############################################ surface Turbidity ########################################

df_T <- Tutira_S1 %>%
  filter(Depth == 1, Date >= x_min & Date <= x_max)

y_min_T <- 0#min(df_T$TurbRT, na.rm = TRUE) 
y_max_T <- max(df_T$TurbRT, na.rm = TRUE)

scale_fun_T <- function(x) {
  y_min_T + (x - y2_min) / (y2_max - y2_min) * (y_max_T - y_min_T)
}

inv_scale_fun_T <- function(x) {
  y2_min + (x - y_min_T) / (y_max_T - y_min_T) * (y2_max - y2_min)
}

storm_window_T <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_T, ymax = y_max_T)
recovery_window_T <- data.frame(xmin = end_time, xmax = Turb_rec_time, ymin = y_min_T, ymax = y_max_T)

T_R <- ggplot(df_T, aes(x = Date, y = TurbRT)) +
  geom_rect(data = storm_window_T, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_T, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TurbRT_lower, ymax = TurbRT_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TurbRT_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TurbRT, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Turb_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  #geom_line(data = Tutira_S2%>% filter(Variable == 'TurbRT', Depth == 1), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C")) +
  scale_y_continuous(
  limits = c(y_min_T, y_max_T),
  breaks = seq(0, 125, by = 25))+
#   sec.axis = sec_axis(
#     ~inv_scale_fun_DO(.),
#     name   = "Daily Resilience",
#     breaks = seq(-1, 1, by = 0.5),
#     labels = scales::number_format(accuracy = 0.1)
#   )
# )+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Surface Turbidity\n(NTU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', 
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
T_R

#combine and save
base_plot <-
  (SWT_R / DO_R / T_R)+
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

# combined_plot <-
#   ggdraw(base_plot) +
#   draw_label(
#     "Structural",
#     x = 0.25, y = 0.98,
#     hjust = 0.5, vjust = 1, color = '#452D7A'
#     #fontface = "bold", size = 14
#   ) +
#   draw_label(
#     "Functional",
#     x = 0.75, y = 0.98,
#     hjust = 0.5, vjust = 1, color = '#2E5EAA'
#     #fontface = "bold", size = 14
#   )
# 
# combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Hui.png",
  plot = base_plot,
  width = 6,
  height = 6,
  dpi = 300
)
```

#### Middle

-   10 m (avg depth of thermocline)

```{r}
#find longest recovery time - thermocline depth
Temp_rec_time <- min(as.Date(Tutira_S1$first_recovery_TmpWtr[Tutira_S1$Depth == 10]), na.rm = TRUE) 
DO_rec_time <- min(as.Date(Tutira_S1$first_recovery_DOconc[Tutira_S1$Depth == 10]), na.rm = TRUE) 
chl_rec_time <- min(as.Date(Tutira_S1$first_recovery_FlChlr[Tutira_S1$Depth == 10]), na.rm = TRUE) 
TD_rec_time   <- min(as.Date(Tutira_F1$first_recovery_thermo.depth), na.rm = TRUE) #2023-09-12

#picking out storm periods
start_time <- min(as.Date(Tutira_F1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_F1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp_10 <- Tutira_S1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_temp <- min(df_Temp_10$TmpWtr_lower, na.rm = TRUE)
y_max_temp <- max(df_Temp_10$TmpWtr_upper, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R_10 <- ggplot(df_Temp_10, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'TmpWtr', Depth == 10), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(10, y_max_temp),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = c(0.7,0.8), axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R_10

############################################ surface Dissolved Oxygen ########################################

df_DO_10 <- Tutira_S1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_DO <- min(df_DO_10$DOconc_lower, na.rm = TRUE) 
y_max_DO <- max(df_DO_10$DOconc_upper, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R_10 <- ggplot(df_DO_10, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'DOconc', Depth == 10), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R_10

############################################ surface Chlorophyll-a ########################################

df_chl_10 <- Tutira_S1 %>%
  filter(Depth == 10, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl_10$FlChlr_lower, na.rm = TRUE) 
y_max_chl <- max(df_chl_10$FlChlr_upper, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R_10 <- ggplot(df_chl_10, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'FlChlr', Depth == 10), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Middle Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R_10
```

#### Bottom

-   35 m

```{r}
#find longest recovery time - thermocline depth
Temp_rec_time <- min(as.Date(Tutira_S1$first_recovery_TmpWtr[Tutira_S1$Depth == 35]), na.rm = TRUE) 
DO_rec_time <- min(as.Date(Tutira_S1$first_recovery_DOconc[Tutira_S1$Depth == 35]), na.rm = TRUE) 
chl_rec_time <- min(as.Date(Tutira_S1$first_recovery_FlChlr[Tutira_S1$Depth == 35]), na.rm = TRUE) 

#picking out storm periods
start_time <- min(as.Date(Tutira_F1$first_during_time), na.rm = TRUE)
end_time   <- min(as.Date(Tutira_F1$last_during_time), na.rm = TRUE)

# Overall x-axis range: extend to latest recovery + 1 month
x_min <- start_time - months(1)
x_max <- TD_rec_time + months(1)

y2_min <- -1
y2_max <- 1

############################################ surface water temp ########################################
df_Temp_35 <- Tutira_S1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_temp <- min(df_Temp_35$TmpWtr_lower, na.rm = TRUE)
y_max_temp <- max(df_Temp_35$TmpWtr, na.rm = TRUE)

scale_fun_temp <- function(x) {
  y_min_temp + (x - y2_min) / (y2_max - y2_min) * (y_max_temp - y_min_temp)
}

inv_scale_fun_temp <- function(x) {
  y2_min + (x - y_min_temp) / (y_max_temp - y_min_temp) * (y2_max - y2_min)
}

storm_window_temp <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_temp, ymax = y_max_temp)
recovery_window_temp <- data.frame(xmin = end_time, xmax = Temp_rec_time, ymin = y_min_temp, ymax = y_max_temp)

SWT_R_35 <- ggplot(df_Temp_35, aes(x = Date, y = TmpWtr)) +
  geom_rect(data = storm_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_temp, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = TmpWtr_lower, ymax = TmpWtr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = TmpWtr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = TmpWtr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, Temp_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'TmpWtr', Depth == 35), aes(x = Date, y = scale_fun_temp(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(10, y_max_temp),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_temp(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Water\nTemperature (°C)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
SWT_R_35

############################################ surface Dissolved Oxygen ########################################

df_DO_35 <- Tutira_S1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_DO <- min(df_DO_35$DOconc_lower, na.rm = TRUE) 
y_max_DO <- max(df_DO_35$DOconc_upper, na.rm = TRUE)

scale_fun_DO <- function(x) {
  y_min_DO + (x - y2_min) / (y2_max - y2_min) * (y_max_DO - y_min_DO)
}

inv_scale_fun_DO <- function(x) {
  y2_min + (x - y_min_DO) / (y_max_DO - y_min_DO) * (y2_max - y2_min)
}

storm_window_DO <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_DO, ymax = y_max_DO)
recovery_window_DO <- data.frame(xmin = end_time, xmax = DO_rec_time, ymin = y_min_DO, ymax = y_max_DO)

DO_R_35 <- ggplot(df_DO_35, aes(x = Date, y = DOconc)) +
  geom_rect(data = storm_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_DO, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = DOconc_lower, ymax = DOconc_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = DOconc_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = DOconc, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, DO_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'DOconc', Depth == 35), aes(x = Date, y = scale_fun_DO(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_DO, y_max_DO),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_DO(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Dissolved\nOxygen (mg/L)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x  = element_blank(),
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
DO_R_35

############################################ surface Chlorophyll-a ########################################

df_chl_35 <- Tutira_S1 %>%
  filter(Depth == 35, Date >= x_min & Date <= x_max)

y_min_chl <- min(df_chl_35$FlChlr_lower, na.rm = TRUE) 
y_max_chl <- max(df_chl_35$FlChlr_upper, na.rm = TRUE)

scale_fun_chl <- function(x) {
  y_min_chl + (x - y2_min) / (y2_max - y2_min) * (y_max_chl - y_min_chl)
}

inv_scale_fun_chl <- function(x) {
  y2_min + (x - y_min_chl) / (y_max_chl - y_min_chl) * (y2_max - y2_min)
}

storm_window_chl <- data.frame(xmin = start_time, xmax = end_time, ymin = y_min_chl, ymax = y_max_chl)
recovery_window_chl <- data.frame(xmin = end_time, xmax = chl_rec_time, ymin = y_min_chl, ymax = y_max_chl)

chl_R_35 <- ggplot(df_chl_35, aes(x = Date, y = FlChlr)) +
  geom_rect(data = storm_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#66C2C7', alpha = 0.3) +
  geom_rect(data = recovery_window_chl, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
            inherit.aes = FALSE, fill = '#196F3D', alpha = 0.2) +
  geom_ribbon(aes(ymin = FlChlr_lower, ymax = FlChlr_upper), fill = '#BDC3C7', alpha = 0.5) +
  geom_line(aes(y = FlChlr_mean, color = "Mean"), size = 1) +
  geom_line(aes(y = FlChlr, color = "2023"), size = 1) +
  #scale_y_continuous(limits = c(10, 25), breaks = seq(10, 25, by = 5)) +  # force axis limits and breaks
  geom_vline(xintercept = c(start_time, end_time, chl_rec_time), linetype = "dashed",
             color = c("black","black","#196F3D")) +
  #scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  geom_line(data = Tutira_S2%>% filter(Variable == 'FlChlr', Depth == 35), aes(x = Date, y = scale_fun_chl(RL_daily), color = 'Resilience'), size = 1, linetype = 'dashed')+
  scale_color_manual(values = c("Mean" = "black", "2023" = "#7B9E4C", 'Resilience' = '#FF7B9C')) +
  scale_y_continuous(
  #limits = c(y_min_chl, y_max_chl),
  #breaks = seq(10, 25, by = 5),
  sec.axis = sec_axis(
    ~inv_scale_fun_chl(.),
    name   = "Daily Resilience",
    breaks = seq(-1, 1, by = 0.5),
    labels = scales::number_format(accuracy = 0.1)
  )
)+
  scale_x_date(limits = c(x_min, x_max), date_labels = "%b", date_breaks = "1 month") +
  labs(x = NULL, y = 'Bottom Chlorophyll-a\n(RFU)', color = NULL) +
  theme_pubr()+
  theme(legend.position = 'none',
        axis.title.y = element_text(color = '#452D7A'), axis.title.y.right  = element_text(color = '#452D7A'))
    # axis.title.x  = element_text(size = 8),
    # axis.title.y  = element_text(size = 8),
    # axis.text.x   = element_text(size = 8),
    # axis.text.y   = element_text(size = 8),
    # legend.text   = element_text(size = 8))
chl_R_35
```

Combining

```{r}
#combine and save
base_plot <-
  ((SWT_R_10 / DO_R_10 / chl_R_10) |
  (SWT_R_35  / DO_R_35 / chl_R_35)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

# combined_plot <-
#   ggdraw(base_plot) +
#   draw_label(
#     "Structural",
#     x = 0.25, y = 0.98,
#     hjust = 0.5, vjust = 1, color = '#452D7A'
#     #fontface = "bold", size = 14
#   ) +
#   draw_label(
#     "Functional",
#     x = 0.75, y = 0.98,
#     hjust = 0.5, vjust = 1, color = '#2E5EAA'
#     #fontface = "bold", size = 14
#   )

#combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Resilience_SS.png",
  plot = base_plot,
  width = 10,
  height = 6,
  dpi = 300
)
```

## Recovery with Depth

### Structural

```{r}
# ---- DEPTH-BASED ----
recovery_vars_depth <- grep("^first_recovery_", colnames(Tutira_S1), value = TRUE)

depth_df <- Tutira_S1 %>%
  dplyr::select(Depth, last_during_time, all_of(recovery_vars_depth)) %>%
  pivot_longer(
    cols = all_of(recovery_vars_depth),
    names_to = "variable",
    values_to = "recovery_date"
  ) %>%
  mutate(
    recovery_delay = as.numeric(difftime(recovery_date, last_during_time, units = "days")),
    variable = gsub("first_recovery_", "", variable),
    Depth = as.numeric(as.character(Depth)),
    Type = "Structural",  # fixed assignment
    Property = case_when(
      variable == 'TmpWtr' ~ "Physical",
      variable %in% c('Cond', 'DOconc', 'DOpsat', 'pH', 'SpCond', 'TurbRT') ~ "Chemical",
      variable %in% c('FlChlr', 'FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    )
  ) %>%
  dplyr::select(variable, Depth, recovery_delay, Type, Property)%>%
  group_by(variable, Depth, Type, Property)%>%
  dplyr::summarise_at('recovery_delay', mean, na.rm=TRUE)%>%
  ungroup

#graphing
variable_order <- c(
  # Physical
  "TmpWtr",
  # Chemical
  "Cond", "DOconc", "DOpsat", "pH", "SpCond", "TurbRT", 
  # Biological
  "FlChlr", "FlPhyc"
)
library(ggforce)

depth_df <- depth_df %>%
  mutate(Property = factor(Property, levels = c("Physical", "Chemical", "Biological")))
filtered_vars <- unique(depth_df$variable[!depth_df$variable %in% c('SpCond', 'pH', 'DOpsat', 'Cond')])

var_labels <- c(
  # Physical
  "TmpWtr" = "Water\nTemperature\n(°C)",
  #chemical
  #"Cond" = "Conductivity\n(µS/cm)",
  "DOconc" = "Dissolved\nOxygen\n(mg/L)",
  #"DOpsat" = "Oxygen\nSaturation\n(%)",
  #"pH" = "pH",
  #"SpCond" = "Specific\nConductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)",
  # Biological
  "FlChlr" = "Chl-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)"
)

library(ggtext)
type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)
depth_df <- depth_df %>%
  mutate(
    Property_colored = paste0(
      "<span style='color:",
      type_colors[Property],
      "'>",
      Property,
      "</span>"
    )
  )
ordered_levels <- paste0(
  "<span style='color:",
  type_colors[c("Physical","Chemical","Biological")],
  "'>",
  c("Physical","Chemical","Biological"),
  "</span>"
)

depth_df <- depth_df %>%
  mutate(Property_colored = factor(Property_colored,
                                   levels = ordered_levels))

depth_df <- depth_df %>%
  mutate(variable = factor(variable, levels = names(var_labels), labels = var_labels[names(var_labels)]))

RC<- ggplot(depth_df%>% filter(Type == 'Structural', variable != 'NA'), aes(x = variable, y = Depth, fill = recovery_delay)) +
  geom_tile(color = "white") +
  #scale_fill_viridis_c(option = "B", na.value = "grey80", limits = c(0, 364)) +
  scale_fill_gradientn(
  colors = c("#66C2C7", "#7B9E4C", "#196F3D"),  # green → blue → green
  #colors = c('#A6262D', '#A626A6', '#4E2294'),
  na.value = "grey80",
  limits = c(0, 366)
)+
  #scale_x_discrete(labels = variable_order) +
  scale_y_reverse(breaks = seq(37, 1, by = -2)) +
  #scale_x_discrete(labels = var_labels) + 
  labs(x = NULL, y = "Depth (m)", fill = "Days till Recovered") +
  facet_wrap(~Property_colored, scales = "free_x", space = "free_x") +
  theme_pubr()+ 
  theme(
  #   #axis.text.x = element_markdown(size = 9, angle = 45, hjust = 1, lineheight = 1.1),
     panel.grid = element_blank(),
     axis.text.x = element_text(color = '#452D7A'),
     strip.text = element_markdown())
  #   axis.ticks.length = unit(0.2, "cm"),
  #   axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x  = element_text(size = 8),
  #   axis.text.y  = element_text(size = 8),
  #   legend.text   = element_text(size = 8),
  #   legend.title  = element_text(size = 8),
  #   strip.text    = element_text(size = 8)
  # )
RC
ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/facet_heatmap_newcolors.png",
  plot = RC,
  width = 5, #14
  height = 6, #7
  dpi = 300
)
```

Days

```{r}
depth_df_WTTop <- depth_df %>%
  filter(variable == 'TmpWtr' & Depth %in% c(1:14)) %>%
  mutate(WT_mean = mean(recovery_delay))

depth_df_WTBottom <- depth_df %>%
  filter(variable == 'TmpWtr' & Depth %in% c(14:39)) %>%
  mutate(WT_mean = mean(recovery_delay))

#turb
depth_df_TTop <- depth_df %>%
  filter(variable == 'TurbRT' & Depth %in% c(1:13)) %>%
  mutate(WT_mean = mean(recovery_delay))

depth_df_TBottom <- depth_df %>%
  filter(variable == 'TurbRT' & Depth %in% c(13:39)) %>%
  mutate(WT_mean = mean(recovery_delay))

#DO
depth_df_DOTop <- depth_df %>%
  filter(variable == 'DOconc' & Depth %in% c(5:8)) %>%
  mutate(WT_mean = mean(recovery_delay))

depth_df_DOBottom <- depth_df %>%
  filter(variable == 'DOconc' & Depth %in% c(1:4, 9:39)) %>%
  mutate(WT_mean = mean(recovery_delay))

#chl
depth_df_chl <- depth_df %>%
  filter(variable == 'FlChlr') %>%
  mutate(WT_mean = mean(recovery_delay))

#phyco
depth_df_phyco <- depth_df %>%
  filter(variable == 'FlPhyc') %>%
  mutate(WT_mean = mean(recovery_delay))

#physical & Chemical
#phyco
depth_df_pc <- depth_df %>%
  filter(variable %in% c('TmpWtr', 'DOconc', 'TurbRT')) %>%
  mutate(mean = mean(recovery_delay))

depth_df_all <- depth_df %>%
  filter(variable %in% c('TmpWtr', 'DOconc', 'TurbRT', 'FlChlr', 'FlPhyc')) %>%
  mutate(mean = mean(recovery_delay))

func_df_all <- func_df %>%
  filter(variable %in% c('schmidt.stability', 'thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr', 'Depth_max_FlPhyc')) %>%
  mutate(mean = mean(recovery_delay))

#difference between DO after recovery and mean
DO_changes <- Tutira_S1 %>%
  dplyr::select(Date, Year, Month, Depth, DOconc, DOconc_mean, DOconc_lower, DOconc_upper) %>%
  filter(Year == '2023' & Month == 'May' & Depth == '1')
```

### Functional

```{r}
# ---- DEPTH-BASED ----
recovery_vars <- grep("^first_recovery_", colnames(Tutira_F1), value = TRUE)

func_df <- Tutira_F1 %>%
  dplyr::select(last_during_time, all_of(recovery_vars)) %>%
  pivot_longer(
    cols = all_of(recovery_vars),
    names_to = "variable",
    values_to = "recovery_date"
  ) %>%
  mutate(
    recovery_delay = as.numeric(difftime(recovery_date, last_during_time, units = "days")),
    variable = gsub("first_recovery_", "", variable),
    #Depth = as.numeric(as.character(Depth)),
    Type = "Functional",  # fixed assignment
    Property = case_when(
      variable %in% c("schmidt.stability", "thermo.depth") ~ "Physical",
      variable == 'Anoxic_Depth' ~ "Chemical",
      variable %in% c('Depth_max_FlChlr', 'Depth_max_FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    )
  ) %>%
  dplyr::select(variable, recovery_delay, Type, Property)%>%
  group_by(variable, Type, Property)%>%
  dplyr::summarise_at('recovery_delay', mean, na.rm=TRUE)%>%
  ungroup

# Define variable types
varible_order <- c(
#physical
  "schmidt.stability", "thermo.depth", 
  #chemical
  "Anoxic_Depth",
  #biological,
  "Depth_max_FlChlr", "Depth_max_FlPhyc"
)

# Combine with labels for axis text
var_labels <- c(
  # Physical
  #"Buoyancy" = "Buoyancy\nFrequency\n(s⁻¹)",
  #"Meta_Bottom" = "Metalimnion\nBottom\n(m)",
  #"Meta_Top" = "Metalimnion\nTop (m)",
  #"lake.number" = "Lake\nNumber",
  "schmidt.stability" = "Schmidt\nStability\n(J/m²)",
  "thermo.depth" = "Thermocline\nDepth (m)",
  # Chemical
  "Anoxic_Depth" = "Hypoxic\nDepth (m)",
  # Biological
  "Depth_max_FlChlr" = "Peak\nChl-a\nDepth (m)",
  "Depth_max_FlPhyc" = "Peak\nPhycocyanin\nDepth (m)"
)

library(ggforce)

# func_df <- func_df %>%
#   mutate(Property = factor(Property, levels = c("Physical", "Chemical", "Biological")))

library(ggtext)
type_colors <- c(
  "Physical" = "#A6262D",
  "Chemical" = "#A626A6",
  "Biological" = "#4E2294"
)
func_df <- func_df %>%
  mutate(
    Property_colored = paste0(
      "<span style='color:",
      type_colors[Property],
      "'>",
      Property,
      "</span>"
    )
  )
ordered_levels <- paste0(
  "<span style='color:",
  type_colors[c("Physical","Chemical","Biological")],
  "'>",
  c("Physical","Chemical","Biological"),
  "</span>"
)

func_df <- func_df %>%
  mutate(Property_colored = factor(Property_colored, levels = ordered_levels))%>%
  mutate(dummy_x = "All")


RC<- ggplot(func_df%>% filter(Type == 'Functional', !variable %in% c('Buoyancy', 'Meta_Bottom', 'Meta_Top', 'lake.number')), aes(x = variable, y = dummy_x, fill = recovery_delay)) +
  geom_tile(color = "white") +
  #scale_fill_viridis_c(option = "B", na.value = "grey80", limits = c(0, 364)) +
  scale_fill_gradientn(
  colors = c("#66C2C7", "#7B9E4C", "#196F3D"),  # green → blue → green
  #colors = c('#A6262D', '#A626A6', '#4E2294'),
  na.value = "grey80",
  limits = c(0, 366)
)+
  #scale_x_discrete(labels = variable_order) +
  #scale_y_reverse(breaks = seq(37, 1, by = -2)) +
  scale_x_discrete(labels = var_labels) + 
  labs(x = NULL, y = NULL, fill = "Days till Recovered") +
  facet_wrap(~Property_colored, scales = "free_x", space = "free_x") +
  theme_pubr()+ 
  theme(
  #   #axis.text.x = element_markdown(size = 9, angle = 45, hjust = 1, lineheight = 1.1),
     panel.grid = element_blank(),
     axis.text.x = element_text(color = '#2E5EAA'),
     strip.text = element_markdown(),
     axis.text.y = element_blank())
  #   axis.ticks.length = unit(0.2, "cm"),
  #   axis.title.x  = element_text(size = 8),
  #   axis.title.y  = element_text(size = 8),
  #   axis.text.x  = element_text(size = 8),
  #   axis.text.y  = element_text(size = 8),
  #   legend.text   = element_text(size = 8),
  #   legend.title  = element_text(size = 8),
  #   strip.text    = element_text(size = 8)
  # )
RC
ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/facet_heatmap_functional_newcolors_n23.png",
  plot = RC,
  width = 5, #14
  height = 3, #7
  dpi = 300
)
```

## Daily Resilience All Time

```{r}
Tutira_S1$t0 <- as.Date(Tutira_S1$t0)
Tutira_F1$t0 <- as.Date(Tutira_F1$t0)
#structural
vars <- c("TmpWtr", "DOconc", "DOpsat", "pH", "FlChlr", "FlPhyc", "Cond", "SpCond", "TurbRT")

# daily rate of resilience for each variable and depth
Tutira_S3 <- Tutira_S1%>%
  #filter(Date >= last_during_time) %>% #& Date <= first_recovery + hours(72)) %>%     # recovery window
  dplyr::select(Date, Depth, all_of(vars), all_of(paste0(vars, "_mean")), first_recovery) %>%
  pivot_longer(
    cols = all_of(vars),
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  mutate(
    MeanValue = case_when(
      Variable == "TmpWtr"  ~ TmpWtr_mean,
      Variable == "DOconc"  ~ DOconc_mean,
      Variable == "DOpsat"  ~ DOpsat_mean,
      Variable == "pH"      ~ pH_mean,
      Variable == "FlChlr"  ~ FlChlr_mean,
      Variable == "FlPhyc"  ~ FlPhyc_mean,
      Variable == "Cond"    ~ Cond_mean,
      Variable == "SpCond"  ~ SpCond_mean,
      Variable == "TurbRT"  ~ TurbRT_mean),
      Dd = Value - MeanValue        # daily deviation
      ) %>%
      merge(Tutira_S1, by = c("Variable", 'Date', all_of(paste0(vars, "_mean")), 'first_recovery', 'Depth'))%>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )

#functional
vars <- c("Buoyancy", "lake.number", "Meta_Top", "Meta_Bottom", "schmidt.stability", "thermo.depth", "Anoxic_Depth", "Depth_max_FlChlr", "Depth_max_FlPhyc")

# daily rate of resilience for each variable and depth
Tutira_F3 <- Tutira_F1%>%
  #filter(Date >= last_during_time) %>% # & Date <= first_recovery + hours(72)) %>%     # recovery window
  dplyr::select(Date, all_of(vars), all_of(paste0(vars, "_mean")), first_recovery) %>%
  pivot_longer(
    cols = all_of(vars),
    names_to = "Variable",
    values_to = "Value"
  ) %>%
  mutate(
    MeanValue = case_when(
      Variable == "Buoyancy"  ~ Buoyancy_mean,
      Variable == "lake.number"  ~ lake.number_mean,
      Variable == "Meta_Top"  ~ Meta_Top_mean,
      Variable == "Meta_Bottom"      ~ Meta_Bottom_mean,
      Variable == "schmidt.stability"  ~ schmidt.stability_mean,
      Variable == "thermo.depth"  ~ thermo.depth_mean,
      Variable == "Anoxic_Depth"    ~ Anoxic_Depth_mean,
      Variable == "Depth_max_FlChlr"  ~ Depth_max_FlChlr_mean,
      Variable == "Depth_max_FlPhyc"  ~ Depth_max_FlPhyc_mean),
      Dd = Value - MeanValue        # daily deviation
      ) %>%
      merge(Tutira_F1, by = c("Variable", 'Date', all_of(paste0(vars, "_mean")), 'first_recovery'))%>%
      mutate(
        RL_daily = ((2 * abs(D0)) / (abs(Dd) + abs(D0))) - 1,
        day_since_disturbance = as.numeric(Date - t0, units = "days")
      )
```

### Graphing

One Variable

```{r}
out_dir <- "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Graphs/RSRL/Structural"

#thermocline depth
TD_R <- ggplot(Tutira_F3%>% filter(Variable == 'thermo.depth'), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  labs(x = NULL, y = 'Daily Resilience for\nThermocline Depth') +
  theme_pubr()
TD_R

vars <- c("TmpWtr", "DOconc", "DOpsat", "pH", "FlChlr", "FlPhyc", "Cond", "SpCond", "TurbRT")
Depths <- 1:38

S3_plots <- list()

for (var in vars) {
  S3_plots[[var]] <- list()
  for (d in Depths){
    S3_plots[[var]][[as.character(d)]] <- Tutira_S3 %>%
      filter(Variable == var, Depth == d) %>%
      ggplot(aes(x = MD, y = RL_daily, group = Year, color = Year)) +
      geom_line(size = 1) + 
      scale_x_date(date_labels = "%b", date_breaks = "1 month") +
      scale_y_continuous(limits = c(-1,1))+
      labs(x = NULL, y = 'Daily Resilience for\nThermocline Depth') +
      theme_pubr()
  }
}

for (var in vars) {
  for (d in Depths){
    print(S3_plots[[var]][[as.character(d)]])
  }
}

for (var in vars) {
  for (d in Depths){
  ggsave(
    filename = paste0("S3_depth_profile_", var, "_", d, "_n23.png"),
    plot     = S3_plots[[var]],
    path     = out_dir,
    width    = 5,
    height   = 7,
    dpi      = 300
  )
  }
}

# S3_plots <- Tutira_S3 %>%
#   filter(Variable %in% vars, Depth %in% Depths) %>%
#   group_split(Variable, Depth) %>%
#   purrr::map(~ 
#     ggplot(.x, aes(MD, RL_daily, group = Year, color = Year)) +
#       geom_line(linewidth = 1) +
#       scale_x_date(date_labels = "%b", date_breaks = "1 month") +
#       scale_y_continuous(limits = c(-1, 1)) +
#       labs(x = NULL, y = 'Daily Resilience for\nThermocline Depth') +
#       theme_pubr()
#   )
# S3_plots
```

Part 2

```{r}
#Structural
#Surface Water Temperature
WT_DRL <- ggplot(Tutira_S3%>% filter(Variable == 'TmpWtr', Depth == 1, Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nSurface\nWater Temperature') +
  theme_pubr()+
  theme(legend.position = c(0.5, 0.4), axis.x.text = element_blank())
WT_DRL

#Surface Dissolved Oxygen Concentration
DO_DRL <- ggplot(Tutira_S3%>% filter(Variable == 'DOconc', Depth == 1, Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nSurface\nDissolved Oxygen') +
  theme_pubr()+
  theme(legend.position = 'none', axis.x.text = element_blank())
DO_DRL

#Surface Chlorophyll-a
chl_DRL <- ggplot(Tutira_S3%>% filter(Variable == 'FlChlr', Depth == 1, Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nSurface\nChlorophyll-a') +
  theme_pubr()+
  theme(legend.position = 'none')
chl_DRL

#functional
#thermocline Depth
TD_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'thermo.depth', Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nThermocline Depth') +
  theme_pubr()+
  theme(legend.position = 'none', axis.x.text = element_blank())
TD_DRL

#Hypoxic Depth
HD_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'Anoxic_Depth', Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nHypoxic Depth') +
  theme_pubr()+
  theme(legend.position = 'none', axis.x.text = element_blank())
HD_DRL

#Depth of chl peak
CD_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'Depth_max_FlChlr', Year %in% c(2022,2023,2024,2025)), aes(x = MD, y = RL_daily, group = Year, color = Year)) +
  geom_line(size = 1) + 
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience for\nDepth of Maximum\nChlorophyll-a Peak') +
  theme_pubr()+
  theme(legend.position = 'none')
CD_DRL

#combine and save
base_plot <-
  ((WT_DRL / DO_DRL / chl_DRL) |
  (TD_DRL  / HD_DRL / CD_DRL)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Resilience_alltime.png",
  plot = combined_plot,
  width = 12,
  height = 8,
  dpi = 300
)
```

#### Violin Plots

```{r}
Tutira_S5 <- Tutira_S3%>%
  filter(Depth == 1)%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  dplyr::summarise_at(vars(RL_daily),mean,na.rm=TRUE)%>%
  ungroup()%>%
  filter(Year %in% c(2022,2023,2024,2025))

Tutira_F5 <- Tutira_F3%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  dplyr::summarise_at(vars(RL_daily),mean,na.rm=TRUE)%>%
  ungroup()%>%
  filter(Year %in% c(2022,2023,2024,2025))


#Structural
#WT
WTV_DRL <- ggplot(Tutira_S5%>% filter(Variable == 'TmpWtr'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Water Temperature",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(TmpWtr = "Water Temperature"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#452D7A'))
WTV_DRL
#DO
DOV_DRL <- ggplot(Tutira_S5%>% filter(Variable %in% 'DOconc'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Dissolved Oxygen",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(DOconc = "Dissolved Oxygen"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#452D7A'))
DOV_DRL
#Chl
CHV_DRL <- ggplot(Tutira_S5%>% filter(Variable == 'FlChlr'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(FlChlr = "Chlorophyll-a"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.title.x = element_text(color = '#452D7A'))
CHV_DRL

#Functional
#thermocline Depth
TDV_DRL <- ggplot(Tutira_F5%>% filter(Variable == 'thermo.depth'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#2E5EAA'))
TDV_DRL

#Hypoxic Depth
HDV_DRL <- ggplot(Tutira_F5%>% filter(Variable == 'Anoxic_Depth'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank(), axis.title.x = element_text(color = '#2E5EAA'))
HDV_DRL

#Depth of chl peak
CDV_DRL <- ggplot(Tutira_F5%>% filter(Variable == 'Depth_max_FlChlr'), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.title.x = element_text(color = '#2E5EAA'))
CDV_DRL

#combine and save
base_plot <-
  ((WTV_DRL / DOV_DRL / CHV_DRL) |
  (TDV_DRL  / HDV_DRL / CDV_DRL)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Resilience_alltime_violin_nolimits_newcolors_nl.png",
  plot = combined_plot,
  width = 12,
  height = 8,
  dpi = 300
)
```

#### All Depths

```{r}
#Structural
#WT
WTV_DRL <- ggplot(Tutira_S3%>% filter(Variable == 'TmpWtr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Water Temperature",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(TmpWtr = "Water Temperature"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
WTV_DRL
#DO
DOV_DRL <- ggplot(Tutira_S3%>% filter(Variable %in% 'DOconc', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Dissolved Oxygen",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(DOconc = "Dissolved Oxygen"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
DOV_DRL
#WT
CHV_DRL <- ggplot(Tutira_S3%>% filter(Variable == 'FlChlr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +

  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  #scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  #scale_x_discrete(labels = c(FlChlr = "Chlorophyll-a"))+
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none')
CHV_DRL

#Functional
#thermocline Depth
TDV_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'thermo.depth', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
TDV_DRL

#Hypoxic Depth
HDV_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'Anoxic_Depth', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
HDV_DRL

#Depth of chl peak
CDV_DRL <- ggplot(Tutira_F3%>% filter(Variable == 'Depth_max_FlChlr', Year %in% c(2022,2023,2024,2025)), aes(x = Year, y = RL_daily, color = Year, fill = Year)) +
  geom_violin(position = position_dodge(width = 0.9),
              trim = FALSE,
              alpha = 0.4) +
  geom_boxplot(position = position_dodge(width = 0.9),
               width = 0.15,
               outlier.shape = 16,
               outlier.size = 1.5,
               alpha = 0.8, color = 'black') +
  annotate(
    "text",
    x = '2022',       # x position (adjust based on your RL_daily range)
    y = -0.98,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # right align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  scale_y_continuous(limits = c(-1,1.2), breaks = c(-1, -0.5, 0, 0.5, 1))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL, y = 'Daily Resilience') +
  theme_pubr()+
  theme(legend.position = 'none')
CDV_DRL

#combine and save
base_plot <-
  ((WTV_DRL / DOV_DRL / CHV_DRL) |
  (TDV_DRL  / HDV_DRL / CDV_DRL)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_Resilience_alltime_SS.png",
  plot = combined_plot,
  width = 12,
  height = 8,
  dpi = 300
)
```

##### Table for box plots

```{r}
Tutira_S5 <- Tutira_S3%>%
  filter(Depth == 1)%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  dplyr::summarise_at(vars(RL_daily),mean,na.rm=TRUE)%>%
  ungroup()%>%
  filter(Year %in% c(2022,2023,2024,2025))

Tutira_F5 <- Tutira_F3%>%
  dplyr::select(Date, Variable,Year, RL_daily)%>%
  group_by(Date, Variable, Year)%>%
  dplyr::summarise_at(vars(RL_daily),mean,na.rm=TRUE)%>%
  ungroup()%>%
  filter(Year %in% c(2022,2023,2024,2025))

# 1 m data
Tutira_all <- bind_rows(
  Tutira_S5,
  Tutira_F5
) 

Tutira_summary <- Tutira_all %>%
  group_by(Variable, Year) %>%
  summarise(
    n       = sum(!is.na(RL_daily)),
    mean    = mean(RL_daily, na.rm = TRUE),
    sd      = sd(RL_daily, na.rm = TRUE),
    median  = median(RL_daily, na.rm = TRUE),
    Q1      = quantile(RL_daily, 0.25, na.rm = TRUE),
    Q3      = quantile(RL_daily, 0.75, na.rm = TRUE),
    IQR     = IQR(RL_daily, na.rm = TRUE),
    min     = min(RL_daily, na.rm = TRUE),
    max     = max(RL_daily, na.rm = TRUE),
    .groups = "drop"
  )

# all depths
Tutira_all_Depth <- bind_rows(
  Tutira_S3 %>% dplyr::select(Variable, Year, Depth, RL_daily),
  Tutira_F3 %>% dplyr::select(Variable, Year, RL_daily)
) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

Tutira_summary_Depth <- Tutira_all_Depth %>%
  group_by(Variable, Year, Depth) %>%
  summarise(
    n       = sum(!is.na(RL_daily)),
    mean    = mean(RL_daily, na.rm = TRUE),
    sd      = sd(RL_daily, na.rm = TRUE),
    median  = median(RL_daily, na.rm = TRUE),
    Q1      = quantile(RL_daily, 0.25, na.rm = TRUE),
    Q3      = quantile(RL_daily, 0.75, na.rm = TRUE),
    IQR     = IQR(RL_daily, na.rm = TRUE),
    min     = min(RL_daily, na.rm = TRUE),
    max     = max(RL_daily, na.rm = TRUE),
    .groups = "drop"
  )
```

##### Stats

```{r}
#structural
#one-way anova
# Make sure Year is a factor
Tutira_S5$Year <- as.factor(Tutira_S5$Year)

# Run ANOVA
model_S <- aov(RL_daily ~ Year, data = Tutira_S5)

summary(model_S)

#if significant - do post-hoc comparisons
TukeyHSD(model_S)

#check normality
library(lme4)

Tutira_S5$Year <- as.factor(Tutira_S5$Year)
Tutira_S5$DOY <- as.numeric(format(Tutira_S5$Date, "%j"))

model_LS <- lmer(RL_daily ~ Year + (1|DOY), data = Tutira_S5)

summary(model_LS)
anova(model_LS)

Tutira_S5$Month <- format(Tutira_S5$Date, "%m")

monthly_means <- Tutira_S5 %>%
  group_by(Year, Month) %>%
  summarise(mean_RL = mean(RL_daily, na.rm = TRUE))

aov(mean_RL ~ Year, data = monthly_means)
summary(aov(mean_RL ~ Year, data = monthly_means))

TukeyHSD(aov(mean_RL ~ Year, data = monthly_means))

ggplot(monthly_means, aes(x = Year, y = mean_RL)) +
  stat_summary(fun = mean, geom = "point", size = 3) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  ylab("Monthly mean RL") +
  theme_minimal()
```

Take two

```{r}
#removing variables that aren't necessary
Tutira_S6 <- Tutira_S5 %>%
  filter(Variable %in% c('TmpWtr', 'DOconc', 'FlChlr'))
#check for normality - shapiro.test
shapiro_results <- Tutira_S6 %>%
  group_by(Variable, Year) %>%
  summarise(
    n = n(),
    shapiro_p = shapiro.test(RL_daily)$p.value,
    .groups = "drop"
  )
#shows non-normality for all variables

#histograms to check skewness
ggplot(data = Tutira_S6, aes(x = RL_daily)) +
  geom_histogram(bins = 30) +
  facet_grid(Variable~Year) +
  theme_pubr()

#density plot to check skewness
ggplot(data = Tutira_S6, aes(x = RL_daily)) +
  geom_density() +
  facet_grid(Variable~Year) +
  theme_pubr()

#checking inference for chla
Tutira_chla <- Tutira_S6%>%
  filter(Variable == 'FlChlr')
model <- gls(RL_daily ~ factor(Year),
             data = Tutira_chla,
             correlation = corAR1(form = ~ Date))

qqnorm(residuals(model))
qqline(residuals(model))
#is not linear

model_raw <- gls(RL_daily ~ factor(Year),
                 data = Tutira_chla,
                 correlation = corAR1(form = ~ Date))

model_squared <- gls(RL_daily^2 ~ factor(Year),
                     data = Tutira_chla,
                     correlation = corAR1(form = ~ Date))

AIC(model_raw, model_squared) #raw better
qqnorm(residuals(model_raw))
qqline(residuals(model_raw))
acf(residuals(model_raw))

#generalized least squares (GLS) - models non-independence
library(nlme)

#chl
# Fit GLS with AR(1) to account for daily autocorrelation
model_chlr <- gls(
  RL_daily ~ factor(Year),   # DOY optional if you want to account for seasonality
  data = Tutira_chla,
  correlation = corAR1(form = ~ Date),
  method = "REML"
)

summary(model_chlr)

anova(model_chlr) #tests difference between years

library(emmeans)
emmeans(model_chlr, pairwise ~ Year) #looks at individual years

#WT
Tutira_WT <- Tutira_S6%>%
  filter(Variable == 'TmpWtr')
# Fit GLS with AR(1) to account for daily autocorrelation
model_WT <- gls(
  RL_daily ~ factor(Year),   # DOY optional if you want to account for seasonality
  data = Tutira_WT,
  correlation = corAR1(form = ~ Date),
  method = "REML"
)

summary(model_WT)

anova(model_WT) #tests difference between years
emmeans(model_WT, pairwise ~ Year) #looks at individual years

#automatic
# Optional: create day-of-year to account for seasonality
Tutira_S6 <- Tutira_S6 %>%
  mutate(DOY = as.numeric(format(Date, "%j")))

variables <- unique(Tutira_S6$Variable)

# Initialize lists to store results
results_summary <- list()
pairwise_summary <- list()

for (var in variables) {
  
  # Filter data for the variable
  data_var <- Tutira_S6 %>% filter(Variable == var)
  
  # Fit GLS with AR(1)
  model <- gls(
    RL_daily ~ factor(Year),       # + DOY if you want to model seasonal cycle
    data = data_var,
    correlation = corAR1(form = ~ Date),
    method = "REML"
  )
  
  # Store ANOVA summary for Year effect
  anova_res <- anova(model)
  results_summary[[var]] <- anova_res
  
  # Store pairwise Year comparisons
  emm <- emmeans(model, pairwise ~ Year, adjust = "tukey")
  pairwise_summary[[var]] <- emm$contrasts
  
  # Optional: QQ plot of residuals for each variable
  qq <- ggplot(data = data.frame(resid = residuals(model)), aes(sample = resid)) +
    stat_qq() +
    stat_qq_line() +
    ggtitle(paste("QQ Plot of residuals:", var))
  
  print(qq)
}

# -------------------------------
# Example: Viewing Results
# -------------------------------

# ANOVA for a variable
results_summary[["TmpWtr"]]
results_summary[["DOconc"]]
results_summary[["FlChlr"]]

# Pairwise comparisons for a variable
pairwise_summary[["TmpWtr"]]
pairwise_summary[["DOconc"]]
pairwise_summary[["FlChlr"]]

# -------------------------------
# Optional: Combine into a Table
# -------------------------------

library(purrr)
library(tibble)

# Function to tidy contrasts
tidy_contrasts <- function(x, variable_name){
  df <- as.data.frame(x)
  df$Variable <- variable_name
  df <- df %>% select(Variable, contrast, estimate, SE, df, t.ratio, p.value)
  return(df)
}

pairwise_table <- map2_dfr(pairwise_summary, names(pairwise_summary), tidy_contrasts)


#functional
Tutira_F6 <- Tutira_F5 %>%
  filter(Variable %in% c('thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr'))
#automatic
# Optional: create day-of-year to account for seasonality
Tutira_F6 <- Tutira_F6 %>%
  mutate(DOY = as.numeric(format(Date, "%j")))

variables <- unique(Tutira_F6$Variable)

# Initialize lists to store results
results_summary <- list()
pairwise_summary <- list()

for (var in variables) {
  
  # Filter data for the variable
  data_var <- Tutira_F6 %>% filter(Variable == var)
  
  # Fit GLS with AR(1)
  model <- gls(
    RL_daily ~ factor(Year),       # + DOY if you want to model seasonal cycle
    data = data_var,
    correlation = corAR1(form = ~ Date),
    method = "REML"
  )
  
  # Store ANOVA summary for Year effect
  anova_res <- anova(model)
  results_summary[[var]] <- anova_res
  
  # Store pairwise Year comparisons
  emm <- emmeans(model, pairwise ~ Year, adjust = "tukey")
  pairwise_summary[[var]] <- emm$contrasts
  
  # Optional: QQ plot of residuals for each variable
  qq <- ggplot(data = data.frame(resid = residuals(model)), aes(sample = resid)) +
    stat_qq() +
    stat_qq_line() +
    ggtitle(paste("QQ Plot of residuals:", var))
  
  print(qq)
}

# -------------------------------
# Example: Viewing Results
# -------------------------------

# ANOVA for a variable
results_summary[["thermo.depth"]]
results_summary[["Anoxic_Depth"]]
results_summary[["Depth_max_FlChlr"]]

# Pairwise comparisons for a variable
pairwise_summary[["thermo.depth"]]
pairwise_summary[["Anoxic_Depth"]]
pairwise_summary[["Depth_max_FlChlr"]]

# -------------------------------
# Optional: Combine into a Table
# -------------------------------


# Function to tidy contrasts
tidy_contrasts <- function(x, variable_name){
  df <- as.data.frame(x)
  df$Variable <- variable_name
  df <- df %>% dplyr::select(Variable, contrast, estimate, SE, df, t.ratio, p.value)
  return(df)
}

pairwise_table_functional <- map2_dfr(pairwise_summary, names(pairwise_summary), tidy_contrasts)


################################################### bootstraping for density changes #######################################################33
library(boot)

# Function to compute a summary statistic
# Can change to mean, sd, quantile, skewness, etc.
stat_fun <- function(data, indices) {
  return(mean(data[indices]))
}

# Function for block bootstrap
block_bootstrap <- function(x, block_size = 7, R = 1000, stat_fun) {
  
  n <- length(x)
  num_blocks <- ceiling(n / block_size)
  boot_stats <- numeric(R)
  
  for (r in 1:R) {
    block_starts <- sample(1:(n - block_size + 1), num_blocks, replace = TRUE)
    sample_idx <- unlist(lapply(block_starts, function(s) s:(s + block_size - 1)))
    sample_idx <- sample_idx[sample_idx <= n]
    
    boot_stats[r] <- stat_fun(x, sample_idx)
  }
  
  return(boot_stats)
}

# Example: Compare TmpWtr between 2022 and 2025
data_tmp <- Tutira_S6 %>% filter(Variable == "TmpWtr")

tmp_2022 <- data_tmp %>% filter(Year == 2022) %>% pull(RL_daily)
tmp_2025 <- data_tmp %>% filter(Year == 2025) %>% pull(RL_daily)

# Run block bootstrap
set.seed(123)
boot_2022 <- block_bootstrap(tmp_2022, block_size = 7, R = 2000, stat_fun = stat_fun)
boot_2025 <- block_bootstrap(tmp_2025, block_size = 7, R = 2000, stat_fun = stat_fun)

# Compute difference in statistic for each bootstrap
boot_diff <- boot_2025 - boot_2022

# 95% confidence interval
ci <- quantile(boot_diff, c(0.025, 0.975))
mean_diff <- mean(boot_diff)

mean_diff
ci
```

#### Density Plots

```{r}
Tutira_S5$Year <- factor(Tutira_S5$Year, levels = c(2022, 2024, 2025, 2023))
Tutira_S5$Variable <- factor(Tutira_S5$Variable, levels = c('TmpWtr', 'DOconc', 'FlChlr'))
Tutira_F5$Year <- factor(Tutira_F5$Year, levels = c(2022, 2024, 2025, 2023))
Tutira_F5$Variable <- factor(Tutira_F5$Variable, levels = c('thermo.depth', 'Anoxic_Depth', 'Depth_max_FlChlr'))

# Combine with labels for axis text
var_labels <- c(
  "TmpWtr" = "Water\ntemperature\n(°C)",
  "DOconc" = "Dissolved\noxygen\n(mg/L)",
  "DOpsat" = "Dissolved\noxygen\n(%)",
  "pH"     = "pH",
  "FlChlr" = "Chlorophyll-a\n(RFU)",
  "FlPhyc" = "Phycocyanin\n(RFU)",
  "Cond"   = "Conductivity\n(µS/cm)",
  "SpCond" = "Specific conductivity\n(µS/cm)",
  "TurbRT" = "Turbidity\n(NTU)"
)
#testing
ggplot(data = Tutira_S5 %>% filter(Variable %in% c('TmpWtr', 'DOconc', 'FlChlr')), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  facet_wrap(~Variable, scales = 'free_y', labeller = labeller(Variable = var_labels))+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = 'Daily Resilience')+
  theme_pubr()

#structural
#WT
D_WT <- ggplot(data = Tutira_S5 %>% filter(Variable == 'TmpWtr'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3,       # y position (adjust based on density height)
    label = "Surface Water Temperature",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = c(0.2, 0.5))
D_WT
#DO
D_DO <- ggplot(data = Tutira_S5 %>% filter(Variable == 'DOconc'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3.5,       # y position (adjust based on density height)
    label = "Surface Dissolved oxygen",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_DO
#chla
D_chl <- ggplot(data = Tutira_S5 %>% filter(Variable == 'FlChlr'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = 'Daily Resilience')+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 11,       # y position (adjust based on density height)
    label = "Surface Chlorophyll-a",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#452D7A'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(legend.position = 'none')
D_chl

#functional
#TD
D_TD <- ggplot(data = Tutira_F5 %>% filter(Variable == 'thermo.depth'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 1.8,       # y position (adjust based on density height)
    label = "Thermocline Depth",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_TD
#DO
D_H <- ggplot(data = Tutira_F5 %>% filter(Variable == 'Anoxic_Depth'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = NULL)+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 3.5,       # y position (adjust based on density height)
    label = "Hypoxic Depth",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(axis.text.x = element_blank(), legend.position = 'none')
D_H
#chla
D_mchl <- ggplot(data = Tutira_F5 %>% filter(Variable == 'Depth_max_FlChlr'), aes(x = RL_daily, group = Year, fill = Year, color = Year)) +
  geom_density(alpha = 0.5)+
  scale_color_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  scale_fill_manual(breaks = c(2022, 2023, 2024, 2025), values = c("#F4989C", "#7B9E4C", "#7AE5F8",  "#9F74D8")) +
  labs(x = 'Daily Resilience')+
  annotate(
    "text",
    x = -0.95,       # x position (adjust based on your RL_daily range)
    y = 2,       # y position (adjust based on density height)
    label = "Depth of Maximum Chlorophyll-a",
    hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  xlim(c(-1,1))+
  theme_pubr()+
  theme(legend.position = 'none')
D_mchl

#combine and save
base_plot <-
  ((D_WT / D_DO / D_chl) |
  (D_TD  / D_H / D_mchl)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Density_RL.png",
  plot = combined_plot,
  width = 12,
  height = 8,
  dpi = 300
)
```

#### Bhattacharyya

```{r}
#structural
# Function to calculate Bhattacharyya coefficient using histograms
bhattacharyya_hist <- function(x, y, bins = 30) {
  
  # Define common breaks
  brks <- seq(min(c(x, y)), max(c(x, y)), length.out = bins + 1)
  
  # Histogram counts
  h1 <- hist(x, breaks = brks, plot = FALSE)$counts
  h2 <- hist(y, breaks = brks, plot = FALSE)$counts
  
  # Convert to probabilities
  p1 <- h1 / sum(h1)
  p2 <- h2 / sum(h2)
  
  # Bhattacharyya coefficient
  BC <- sum(sqrt(p1 * p2))
  return(BC)
}
Tutira_S6 <- Tutira_S5 %>%
  filter(Variable %in% c('TmpWtr', 'DOconc','FlChlr')) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

overlap_results <- list()
counter <- 1

variables <- unique(Tutira_S6$Variable)
years <- sort(unique(Tutira_S6$Year))

for (var in variables) {
  var_data <- Tutira_S6 %>% filter(Variable == var)
  
  for (i in 1:(length(years)-1)) {
    for (j in (i+1):length(years)) {
      
      x <- var_data$RL_daily[var_data$Year == years[i]] %>% na.omit()
      y <- var_data$RL_daily[var_data$Year == years[j]] %>% na.omit()
      
      if(length(x) < 5 | length(y) < 5) next  # smaller threshold
      
      bc <- bhattacharyya_hist(x, y, bins = 30)
      
      overlap_results[[counter]] <- data.frame(
        Variable = var,
        Year1 = years[i],
        Year2 = years[j],
        Bhattacharyya = bc
      )
      
      counter <- counter + 1
    }
  }
}

overlap_df <- bind_rows(overlap_results)

#functional
# Function to calculate Bhattacharyya coefficient using histograms
#functional
bhattacharyya_hist <- function(x, y, bins = 30) {
  
  # Define common breaks
  brks <- seq(min(c(x, y)), max(c(x, y)), length.out = bins + 1)
  
  # Histogram counts
  h1 <- hist(x, breaks = brks, plot = FALSE)$counts
  h2 <- hist(y, breaks = brks, plot = FALSE)$counts
  
  # Convert to probabilities
  p1 <- h1 / sum(h1)
  p2 <- h2 / sum(h2)
  
  # Bhattacharyya coefficient
  BC <- sum(sqrt(p1 * p2))
  return(BC)
}

Tutira_F6 <- Tutira_F5 %>%
  filter(Variable %in% c('thermo.depth', 'Anoxic_Depth','Depth_max_FlChlr')) %>%
  filter(Year %in% c(2022, 2023, 2024, 2025))

overlap_results <- list()
counter <- 1

variables <- unique(Tutira_F6$Variable)
years <- sort(unique(Tutira_F6$Year))

for (var in variables) {
  var_data <- Tutira_F6 %>% filter(Variable == var)
  
  for (i in 1:(length(years)-1)) {
    for (j in (i+1):length(years)) {
      
      x <- var_data$RL_daily[var_data$Year == years[i]] %>% na.omit()
      y <- var_data$RL_daily[var_data$Year == years[j]] %>% na.omit()
      
      if(length(x) < 5 | length(y) < 5) next  # smaller threshold
      
      bc <- bhattacharyya_hist(x, y, bins = 30)
      
      overlap_results[[counter]] <- data.frame(
        Variable = var,
        Year1 = years[i],
        Year2 = years[j],
        Bhattacharyya = bc
      )
      
      counter <- counter + 1
    }
  }
}

overlap_df_F <- bind_rows(overlap_results)
```

Graphing

```{r}
#Structural
ggplot(overlap_df, aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  facet_wrap(~ Variable, scales="free") +
  scale_fill_viridis_c(option="magma", direction=-1) +
  labs(
    x="Year 1", y="Year 2",
    fill="Bhattacharyya Coef"
  ) +
  theme_pubr()

#Functional
ggplot(overlap_df_F, aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  facet_wrap(~ Variable, scales="free") +
  scale_fill_viridis_c(option="magma", direction=-1) +
  labs(
    x="Year 1", y="Year 2",
    fill="Bhattacharyya Coef"
  ) +
  theme_pubr()

#structural
B_WT <- ggplot(overlap_df %>% filter(Variable == 'TmpWtr'), aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98), guide = guide_colorbar(
      direction = "horizontal",   # make legend horizontal
      title.position = "top",     # move title above the bar
      barwidth = 10,              # adjust width
      barheight = 0.5             # adjust height
    ))+
  labs(x=NULL, y=NULL,fill="Bhattacharyya Coef") +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Water\nTemperature",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = c(0.75, 0.18), axis.text.x = element_blank())
B_WT
B_DO <- ggplot(overlap_df %>% filter(Variable == 'DOconc'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Dissolved\noxygen",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_DO
B_C <- ggplot(overlap_df %>% filter(Variable == 'FlChlr'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Surface Chlorophyll-a",
    #hjust = 0,     # right align
    size = 4,      # text size
    color = '#452D7A'
  )+
  theme_pubr()+
  theme(legend.position = 'none')
B_C
#Functional
B_TD <- ggplot(overlap_df_F %>% filter(Variable == 'thermo.depth'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Thermocline\nDepth",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_TD
B_HD <- ggplot(overlap_df_F %>% filter(Variable == 'Anoxic_Depth'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Hypoxic\nDepth",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none', axis.text.x = element_blank())
B_HD
B_CD <- ggplot(overlap_df_F %>% filter(Variable == 'Depth_max_FlChlr'),
               aes(x=factor(Year1), y=factor(Year2), fill=Bhattacharyya)) +
  geom_tile(color="white") +
  geom_text(aes(label = round(Bhattacharyya, 2)), size = 3) +  # add values
  scale_fill_distiller(palette = "YlGnBu", direction = 1, limits=c(0.86,0.98))+
  labs(x=NULL, y=NULL, fill=NULL) +
  annotate(
    "text",
    x = '2024',       # x position (adjust based on your RL_daily range)
    y = '2024',       # y position (adjust based on density height)
    label = "Depth of\nMaximum\nChlorophyll-a",
    #hjust = 0,     # left align
    size = 4,      # text size
    color = '#2E5EAA'
  )+
  theme_pubr()+
  theme(legend.position = 'none')
B_CD

#combine and save
base_plot <-
  ((B_WT / B_DO / B_C) |
  (B_TD  / B_HD / B_CD)) +
  plot_annotation(
    tag_levels = "A"   # A, B, C
  )

base_plot

combined_plot <-
  ggdraw(base_plot) +
  draw_label(
    "Structural",
    x = 0.25, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#452D7A'
    #fontface = "bold", size = 14
  ) +
  draw_label(
    "Functional",
    x = 0.75, y = 0.98,
    hjust = 0.5, vjust = 1, color = '#2E5EAA'
    #fontface = "bold", size = 14
  )

combined_plot

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Bhattacharyya_Coef.png",
  plot = combined_plot,
  width = 12,
  height = 8,
  dpi = 300
)
```

## Recovery Days vs Resistance

```{r}
#Structural
Tutira_S4 <- Tutira_S1%>%
  mutate(Type = case_when(
      Variable == 'TmpWtr' ~ "Physical",
      Variable %in% c('Cond', 'DOconc', 'DOpsat', 'pH', 'SpCond', 'TurbRT') ~ "Chemical",
      Variable %in% c('FlChlr', 'FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    ))%>%
  mutate(Property = 'Structural')
  

#Functional
Tutira_F4 <- Tutira_F1%>%
  mutate(Type = case_when(
      Variable %in% c('Buoyancy', "lake.number", "Meta_Top", "Meta_Bottom", "schmidt.stability", "thermo.depth") ~ "Physical",
      Variable == 'Anoxic_Depth' ~ "Chemical",
      Variable %in% c('Depth_max_FlChlr', 'Depth_max_FlPhyc') ~ "Biological",
      TRUE ~ NA_character_  # for any other variables
    ))%>%
  mutate(Property = 'Functional')
    
dtr_RS <- ggplot(data = Tutira_S4, aes(x = RS, y = RTB, color = Type, shape = Property))+
  geom_point(size = 2)+
  geom_point(data = Tutira_F4, aes(x = RS, y = RTB, color = Type, shape = Property), size = 2)+
  scale_color_manual(breaks = c('Physical', 'Chemical', 'Biological'), values = c("#A6262D", "#A626A6", "#4E2294"), name = 'Process') +
  scale_shape_manual(breaks = c('Structural', 'Functional'), values = c(16, 17), name = 'Type', labels = c("<span style='color:#452D7A'>Structural</span>","<span style='color:#2E5EAA'>Functional</span>")) +
  xlim(-1,1)+
  labs(x = 'Resistance', y = 'Days till Recovery')+
  #guides(color = guide_legend(order = 1), shape = guide_legend(order = 2)) +
  theme_pubr()+
  theme(legend.position = 'right', legend.text = element_markdown())
dtr_RS

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Recovery_daystillrecovery_newcolors_n23.png",
  plot = dtr_RS,
  width = 6,
  height = 4,
  dpi = 300
)
```

## Conceptual Figure

```{r}
concept_ts <- data.frame(
  time = 1:27,
  value = c(
    rep(1, 5),          # baseline
    1.6, 1.8, 1.95, 2.0, 1.98,     # storm impact
    1.8, 1.5,           # early recovery
    1.3, 1.15, 1.05, 1.03,   # recovery
    rep(1, 4),           # recovered
    1.03, 1.15, 1.30, 1.27, 1.15, 1.05, 1
  )
)

storm_start <- 5
storm_end   <- 10
recovery_end <- 16
recovery_end_2 <- 27
baseline <- 1
ci_width  <- 0.1  # half-width of 95% CI
x_arrow <- 9
y_start <- 1.05
y_end   <- 1.9
y_mid   <- (y_start + y_end) / 2  # middle point

#center points of boxes
mid_x_S<- storm_start + (storm_end - storm_start) / 2
mid_x_R <- storm_end + (recovery_end - storm_end) / 2
mid_x_R2 <- recovery_end + (recovery_end_2 - recovery_end) / 2
mid_x_RL <- storm_end + (recovery_end_2 - storm_end) / 2

conceptual <- ggplot(concept_ts, aes(time, value)) +

  # Storm period shading
  annotate(
    "rect",
    xmin = storm_start,
    xmax = storm_end,
    ymin = -Inf,
    ymax = Inf,
    fill = '#66C2C7',
    alpha = 0.2
  ) +
  
  # Recovery shading
  annotate(
    "rect",
    xmin = storm_end,
    xmax = recovery_end,
    ymin = -Inf,
    ymax = Inf,
    fill = '#196F3D',
    alpha = 0.2
  ) +
  
  #Long-term Recovery
  annotate(
    "rect",
    xmin = recovery_end,
    xmax = recovery_end_2,
    ymin = -Inf,
    ymax = Inf,
    fill = '#003B19',
    alpha = 0.2
  ) +
  
   # 95% CI ribbon
  geom_ribbon(
    aes(ymin = baseline - ci_width, ymax = baseline + ci_width),
    fill = '#BDC3C7',
    alpha = 0.5
  ) +

  # Baseline
  geom_hline(
    yintercept = 1,
    linetype = "dashed",
    color = "black"
  ) +

  # System response line
  geom_line(linewidth = 1, color = "#7B9E4C") +
  #geom_point(size = 2) +

  # Resistance arrow
  # annotate(
  #   "segment",
  #   x = 9, xend = 9,
  #   y = 1, yend = 1.95,
  #   arrow = arrow(length = unit(0.2, "cm"))
  # ) +
  annotate(
    "segment",
    x = x_arrow, xend = x_arrow,
    yend = y_start + 0.02, y = y_mid - 0.1,  # leave small gap for text
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  # Second half of arrow
  annotate(
    "segment",
    x = x_arrow, xend = x_arrow,
    y = y_mid + 0.1, yend = y_end,
    arrow = arrow(length = unit(0.2, "cm"))
  ) +
  # Text in the middle
  annotate(
    "text",
    x = x_arrow,
    y = y_mid,
    label =  "D[0]",
    parse = TRUE,
    fontface = "bold",
    vjust = 0.5, size = 3.5
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.8,
    label = "Resistance",
    color = '#842A11'
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.55,
    label = "D[0] == V[0] - B[0]",
    parse = TRUE,
    color = '#842A11'
  ) +
  geom_point(aes(x = 9, y = 2), color = "black", size = 2)+
  # Dashed rectangle around point + arrow + text
annotate(
  "rect",
  xmin = 8.5, xmax = 9.5,   # horizontal span
  ymin = 0.65, ymax = 2.4,   # vertical span
  color = "#842A11",           # border color
  linetype = "dashed",       # dashed border
  fill = NA,                 # no fill
  linewidth = 0.7
)+
  annotate(
    "text",
    x = 9,
    y = 0.8,
    label =  "B[0]",
    parse = TRUE, size = 3.5
  ) +
  annotate(
    "text",
    x = 9,
    y = 2.2,
    label =  "V[0]",
    parse = TRUE, size = 3.5
  ) +

  # Recovery arrow
  # annotate(
  #   "segment",
  #   x = storm_end,
  #   xend = recovery_end,
  #   y = 0.9,
  #   yend = 0.9,
  #   arrow = arrow(length = unit(0.2, "cm"))
  # ) +
  annotate(
    "text",
    x = mid_x_R,
    y = 3.2,
    label = "Recovery \nPeriod",
    fontface = "bold"
  ) +
  annotate(
    "text",
    x = mid_x_R2,
    y = 3.2,
    label = "Long - Term\nRecovery Period",
    fontface = "bold"
  ) +
  geom_point(aes(x = 16, y = 1.03), color = "#674A84", size = 3)+
  annotate(
    "text",
    x = 16,
    y = 1.8,
    label = "Initial\nRecovery",
    color = '#674A84'
  ) +

  # Labels
  annotate(
    "text",
    x = mid_x_S,
    #y = max(concept_ts$value) + 0.1,
    y = 3.2,
    label = "Storm\nPeriod",
    fontface = "bold"
  ) +
  #resilience
  #points
  geom_point(aes(x = 10, y = 1.98), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 11, y = 1.8), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 12, y = 1.5), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 13, y = 1.3), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 14, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 15, y = 1.05), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 16, y = 1.03), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 17, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 18, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 19, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 20, y = 1), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 21, y = 1.03), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 22, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 23, y = 1.30), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 24, y = 1.27), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 25, y = 1.15), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 26, y = 1.05), shape = 1, size = 2, color = '#594F3B') +
  geom_point(aes(x = 27, y = 1), shape = 1, size = 2, color = '#594F3B') +
  #baseline labels
  annotate("text", x = 10, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  # annotate("text", x = 11, y = 0.95, label =  "C[2]", parse = TRUE) +
  # annotate("text", x = 12, y = 0.95, label =  "C[3]", parse = TRUE) +
  # annotate("text", x = 13, y = 0.95, label =  "C[4]", parse = TRUE) +
  # annotate("text", x = 14, y = 0.95, label =  "C[5]", parse = TRUE) +
  # annotate("text", x = 15, y = 0.95, label =  "C[6]", parse = TRUE) +
  annotate("text", x = 16, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate("text", x = 27, y = 0.8, label =  "B[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  #actual value labels
  annotate("text", x = 10, y = 2.16, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  # annotate("text", x = 11, y = 1.86, label =  "P[2]", parse = TRUE, hjust = 0.3) +
  # annotate("text", x = 12, y = 1.56, label =  "P[3]", parse = TRUE, hjust = 0) +
  # annotate("text", x = 13, y = 1.36, label =  "P[4]", parse = TRUE, hjust = 0.2) +
  # annotate("text", x = 14, y = 1.21, label =  "P[5]", parse = TRUE, hjust = 0.5) +
  # annotate("text", x = 15, y = 1.11, label =  "P[6]", parse = TRUE) +
  annotate("text", x = 16, y = 1.23, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate("text", x = 27, y = 1.2, label =  "V[t]", parse = TRUE, color = '#594F3B', size = 3.5) +
  annotate(
    "text",
    x = mid_x_RL,
    y = 2.8,
    label = "Resilience",
   # hjust = 0,
    color = '#D57124'
  ) +
  annotate(
    "text",
    x = mid_x_RL,
    y = 2.55,
    label = "D[t] == V[t] - B[t]",
    #hjust = 0,
    parse = TRUE,
    color = '#D57124'
  ) +
  geom_point(aes(x = 9, y = 2), color = "black", size = 3)+
  # Dashed rectangle around point + arrow + text
annotate(
  "rect",
  xmin = 9.5, xmax = 27.8,   # horizontal span
  ymin = 0.65, ymax = 2.4,   # vertical span
  color = '#D57124',           # border color
  linetype = "dashed",       # dashed border
  fill = NA,                 # no fill
  linewidth = 0.7            # optional border thickness
)+
  
  labs(
    x = "Day",
    y = "Lake Value"
  ) +
  scale_x_continuous(breaks = c(0,2,4,6,8,10,12,14,16,18,20,22,24,26))+
  scale_y_continuous(limits = c(0.5, 3.5), breaks = c(1, 2, 3))+

  theme_pubr() +
  theme(
    panel.grid = element_blank()
  )
conceptual

ggsave(
  filename = "C:/Users/mah92/OneDrive - The University of Waikato/Desktop/Project 1/Draft Paper Graphs/Conceptual_new.png",
  plot = conceptual,
  width = 6, #14
  height = 3, #7
  dpi = 300
)
```

Density Plot for LTR

```{r}
ggplot(data = Tutira_S5, aes(x = RL_daily, color = factor(Year))+
  geom_density(na.rm = TRUE, linewidth = 1)+
  theme_pubr()
```
